### 2024-10-24 PaperSections.Rmd
After model change 23/10/24

# Setup Env

```{r include=FALSE}
library(tidyverse)
library(ggpubr)
library(cowplot)
```

# Abundance Section

## Acoustic

### Campelen

```{r}
# acc_surv <- read.csv("./Data/Capelin_AccSurv.csv") %>% filter(Year > 1980) %>% rename(acsurv_bm = names(Capelin_AccSurv)[2])
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv") %>% 
  filter(Year > 1994) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

## Survey year proper
p1 <- ggplot(data = acc_surv) +
  geom_line(aes(x = Year, y = acsurv_bm), colour = "#BB2D05", linewidth = 1) +
  geom_point(aes(x = Year, y = acsurv_bm), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1995, 2020.9), breaks = c(seq(1995, 2020, 5))) + 
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.009,0), limits = c(0, 1100)) +
  ggtitle("Campelen\na) Spring") +
  theme_classic() +
  theme(legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.line.x = element_line(size = 0.7), axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))
```

### Engel

```{r}
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv") %>% 
  filter(Year > 1980 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

## Survey year proper
p2 <- ggplot(data = acc_surv) +
  geom_line(aes(x = Year, y = acsurv_bm), colour = "#BB2D05", linewidth = 1) +
  geom_point(aes(x = Year, y = acsurv_bm), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1981,1995.1), breaks = c(seq(1981,1995, 3))) + 
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.009,0), limits = c(0,6000)) +
  ggtitle("Engel\nb) Spring") +
  theme_classic() +
  theme(legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.line.x = element_line(size = 0.7), axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))
```

## Campelen

### Spring

```{r}
load(file = "./ModelSaves/AP-SprCamp_Length.RData")
load(file = "./ModelSaves/GH-SprCamp_Length.RData")

# Set up index df - GH
gh_data <- gh_fishy_dat
gh_uni_names <- unique(gh_data$names)
gh_dat_names <- c("Index", gh_uni_names)

gh_new_list <- list()
for(i in 1:length(gh_uni_names)){
  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
}

gh_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  gh_new_list
)

# Set up index df - AC
ap_data <- ap_fishy_dat
ap_uni_names <- unique(ap_data$names)
ap_dat_names <- c("Index", ap_uni_names)

ap_new_list <- list()
for(i in 1:length(ap_uni_names)){
  ap_one_dex <- subset(ap_data, names == ap_uni_names[i])
  ap_new_list[[i]] <- aggregate(ap_one_dex$pa, by = list(ap_one_dex$year), FUN = mean, na.rm = TRUE)
}

ap_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  ap_new_list
)

gh_low_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] - qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
gh_high_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] + qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
gh_ts_df <- data.frame(ts = gh_rep$iye, time = gh_multi_inner[,1], low_sd = gh_low_rho, high_sd = gh_high_rho)

ap_low_rho = ap_sdrep$value[names(ap_sdrep$value) == "iye"] - qnorm(0.975)*ap_sdrep$sd[names(ap_sdrep$value) == "iye"]
ap_high_rho = ap_sdrep$value[names(ap_sdrep$value) == "iye"] + qnorm(0.975)*ap_sdrep$sd[names(ap_sdrep$value) == "iye"]
ap_ts_df <- data.frame(ts = ap_rep$iye, time = ap_multi_inner[,1], low_sd = ap_low_rho, high_sd = ap_high_rho)

p3 <- ggplot() +
  geom_line(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
  geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +

  geom_line(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
  geom_point(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +

  geom_ribbon(data = gh_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_line(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
  geom_point(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +

  geom_ribbon(data = ap_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_line(data = ap_ts_df, aes(x = time, y = ts, colour = "ap"), size = 1.5) +
  geom_point(data = ap_ts_df, aes(x = time, y = ts, colour = "ap"), size = 1.5) +

  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1995,2021), breaks = c(seq(1995, 2021, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.6,2.4)) +
  scale_color_manual(name = "Species Model", values = c(all = "black", surv = "#BB2D05", ap = "#FF7733", gh = "#048BA8"),
                     labels = c(all = "All species", surv = "Acoustic survey", ap = "Plaice", gh = "Greenland halibut")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  ggtitle("c) Spring") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
        plot.title = element_text(size = 16, face = "bold"))
```

### Fall

```{r}
load(file = "./ModelSaves/FallCamp_Length.RData")

data <- fishy_dat
uni_names <- unique(data$names)
dat_names <- c("Index", uni_names)

new_list <- list()
for(i in 1:length(uni_names)){
  one_dex <- subset(data, names == uni_names[i])
  new_list[[i]] <- aggregate(one_dex$pa, by = list(one_dex$year), FUN = mean, na.rm = TRUE)
}

multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  new_list)

# Confidence intervals
low_rho = sdrep$value[names(sdrep$value) == "iye"] - qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
high_rho = sdrep$value[names(sdrep$value) == "iye"] + qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
ts_df <- data.frame(ts = rep$iye, year = multi_inner[,1], low_sd = low_rho, high_sd = high_rho) %>% mutate(acc_year = multi_inner[,1]+1)

p4 <- ggplot() +
  geom_ribbon(data = ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_point(data = ts_df, aes(x = acc_year, y = ts, colour = "all")) +
  geom_line(data = ts_df, aes(x = acc_year, y = ts, colour = "all" ), size = 1.5) +

  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1995,2022), breaks = c(seq(1995, 2022, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.45, 1.08)) +
  scale_color_manual(name = "Species Model", values = c(all = "black", ac = "#BC8DA0", gh = "#048BA8"),
                     labels = c(all = "All species", ac = "Cod/ Plaice", gh = "Greenland halibut")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  ggtitle("e) Fall") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
        plot.title = element_text(size = 16, face = "bold"))
```

## Engel

### Spring

```{r}
load(file = "./ModelSaves/ACAP-SprEng_Length.RData")
load(file = "./ModelSaves/GH-SprEng_Length.RData")

# Set up index df - GH
gh_data <- gh_fishy_dat
gh_uni_names <- unique(gh_data$names)
gh_dat_names <- c("Index", gh_uni_names)

gh_new_list <- list()
for(i in 1:length(gh_uni_names)){
  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
}

gh_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  gh_new_list
)

# Set up index df - AC
ac_data <- ac_fishy_dat
ac_uni_names <- unique(ac_data$names)
ac_dat_names <- c("Index", ac_uni_names)

ac_new_list <- list()
for(i in 1:length(ac_uni_names)){
  ac_one_dex <- subset(ac_data, names == ac_uni_names[i])
  ac_new_list[[i]] <- aggregate(ac_one_dex$pa, by = list(ac_one_dex$year), FUN = mean, na.rm = TRUE)
}

ac_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  ac_new_list
)

gh_low_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] - qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
gh_high_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] + qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
gh_ts_df <- data.frame(ts = gh_rep$iye, time = gh_multi_inner[,1], low_sd = gh_low_rho, high_sd = gh_high_rho)

ac_low_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] - qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
ac_high_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] + qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
ac_ts_df <- data.frame(ts = ac_rep$iye, time = ac_multi_inner[,1], low_sd = ac_low_rho, high_sd = ac_high_rho)

p5 <- ggplot() +
  geom_line(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
  geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +

  geom_line(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
  geom_point(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +

  geom_ribbon(data = gh_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_line(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
  geom_point(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +

  geom_ribbon(data = ac_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_line(data = ac_ts_df, aes(x = time, y = ts, colour = "ac"), size = 1.5) +
  geom_point(data = ac_ts_df, aes(x = time, y = ts, colour = "ac"), size = 1.5) +

  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1981,1995), breaks = c(seq(1981, 1995, 3))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.3,2.0)) +
  scale_color_manual(name = "Species Model", values = c(all = "black", surv = "#BB2D05", ac = "#BC8DA0", gh = "#048BA8"),
                     labels = c(all = "All species", surv = "Acoustic survey", ac = "Cod/ Plaice", gh = "Greenland halibut")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  ggtitle("c) Spring") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
        plot.title = element_text(size = 16, face = "bold"))
```

### Fall

```{r}
load(file = "./ModelSaves/ACAP-FallEng_Length.RData")
load(file = "./ModelSaves/GH-FallEng_Length.RData")

# Set up index df - GH
gh_data <- gh_fishy_dat
gh_uni_names <- unique(gh_data$names)
gh_dat_names <- c("Index", gh_uni_names)

gh_new_list <- list()
for(i in 1:length(gh_uni_names)){
  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
}

gh_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  gh_new_list
)

# Set up index df - AC
ac_data <- ac_fishy_dat
ac_uni_names <- unique(ac_data$names)
ac_dat_names <- c("Index", ac_uni_names)

ac_new_list <- list()
for(i in 1:length(ac_uni_names)){
  ac_one_dex <- subset(ac_data, names == ac_uni_names[i])
  ac_new_list[[i]] <- aggregate(ac_one_dex$pa, by = list(ac_one_dex$year), FUN = mean, na.rm = TRUE)
}

ac_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  ac_new_list
)

gh_low_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] - qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
gh_high_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] + qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
gh_ts_df <- data.frame(ts = gh_rep$iye, time = gh_multi_inner[,1], low_sd = gh_low_rho, high_sd = gh_high_rho) %>% 
  mutate(acc_year = gh_multi_inner[,1]+1)

ac_low_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] - qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
ac_high_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] + qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
ac_ts_df <- data.frame(ts = ac_rep$iye, time = ac_multi_inner[,1], low_sd = ac_low_rho, high_sd = ac_high_rho) %>% 
  mutate(acc_year = ac_multi_inner[,1]+1)

p6 <- ggplot() +
  geom_line(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
  geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +

  geom_line(aes(x = 0, y = 0, colour = "ap"), size = 1.5) +
  geom_point(aes(x = 0, y = 0, colour = "ap"), size = 1.5) +

  geom_ribbon(data = gh_ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_line(data = gh_ts_df, aes(x = acc_year, y = ts, colour = "gh"), size = 1.5) +
  geom_point(data = gh_ts_df, aes(x = acc_year, y = ts, colour = "gh"), size = 1.5) +

  geom_ribbon(data = ac_ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_line(data = ac_ts_df, aes(x = acc_year, y = ts, colour = "ac"), size = 1.5) +
  geom_point(data = ac_ts_df, aes(x = acc_year, y = ts, colour = "ac"), size = 1.5) +

  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1981,1995), breaks = c(seq(1981, 1995, 3))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.21,0.75)) +
  scale_color_manual(name = "Species Model", values = c(all = "black", ac = "#BC8DA0", gh = "#048BA8", ap = "#FF7733"),
                     labels = c(all = "All species", ac = "Cod/ Plaice", gh = "Greenland halibut", ap = "American plaice")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  ggtitle("f) Fall") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
        plot.title = element_text(size = 16, face = "bold"))
```

## - Figure 2

```{r, fig.width = 16, fig.height=13}

p7 <- ggarrange(p1+theme(axis.title.x = element_blank()),
          p2+theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
          p3+theme(),
          p5+theme(axis.title.y = element_blank()),
          p4,
          p6+theme(axis.title.y = element_blank()),
          nrow = 3, ncol = 2,
          align = "v", legend = "right", legend.grob = ggpubr::get_legend(p6+theme(legend.position = "right")))

ggsave(filename = "abundancefull.tiff", device = "tiff", plot = p7, path = "./Figures",
       dpi = 300, width = 16, height = 13, units = "in")
```

# Survey Comparison

## Campelen

### Fall

```{r}
load(file = "./ModelSaves/FallCamp_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1994) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

# Set up relationship data frame
lr_dat <- data.frame(year = acc_surv[2:28,1], acc_bm = acc_surv[2:28,2], NLFPM_bm = rep$iye) #have to go y+1

# Linear relationship 
fit <- lm(acc_bm~NLFPM_bm, data = lr_dat)
cor.test(x = lr_dat$NLFPM_bm, y = lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated

lr_dat <- na.omit(lr_dat)

p8 <- ggplot(data = lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
  geom_point(aes(colour = year), size = 1.5) +

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle("Campelen\na) Fall 2J3KL All Speices") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = "none",
    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

```

### Spring

```{r}
load(file = "./ModelSaves/AP-SprCamp_Length.RData")
load(file = "./ModelSaves/GH-SprCamp_Length.RData")

acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1994) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

# Set up relationship data frame - ACAP
ap_lr_dat <- data.frame(year = acc_surv[2:25,1], acc_bm = acc_surv[2:25,2], NLFPM_bm = ap_rep$iye)

# This doesnt change corelation coefficient 
ap_lr_dat <- data.frame(year = c(acc_surv[2:18,1], acc_surv[21:25,1]), acc_bm = c(acc_surv[2:18,2], acc_surv[21:25,2]), 
                        NLFPM_bm = c(ap_rep$iye[2:18],ap_rep$iye[21:25]))

# Linear relationship 
fit <- lm(acc_bm~NLFPM_bm, data = ap_lr_dat) # thought is: can NLFPM predict acoustic survey accurately
cor.test(x = ap_lr_dat$NLFPM_bm, y = ap_lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated

ap_lr_dat <- na.omit(ap_lr_dat)

p9 <- ggplot(data = ap_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
  geom_point(aes(colour = year), size = 1.5) +

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle(" \nb) Spring 3L Plaice") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

# Set up relationship data frame - GH
gh_lr_dat <- data.frame(year = acc_surv[2:25,1], acc_bm = acc_surv[2:25,2], NLFPM_bm = gh_rep$iye)

# This does change the correlation coefficient
gh_lr_dat <- data.frame(year = c(acc_surv[2:18,1], acc_surv[21:25,1]), acc_bm = c(acc_surv[2:18,2], acc_surv[21:25,2]), 
                        NLFPM_bm = c(gh_rep$iye[2:18],gh_rep$iye[21:25]))

# Linear relationship 
fit <- lm(acc_bm~NLFPM_bm, data = gh_lr_dat) # thought is: can NLFPM predict acoustic survey accurately
cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated

gh_lr_dat <- na.omit(gh_lr_dat)

p10 <- ggplot(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
  geom_point(aes(colour = year), size = 1.5) +

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
  theme_classic() +
  ggtitle(" \nc) Spring 3L Halibut") +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
        legend.position = 'none',
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
        axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

```

## Engel

### Fall

```{r}
load(file = "./ModelSaves/ACAP-FallEng_Length.RData")
load(file = "./ModelSaves/GH-FallEng_Length.RData")

acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1980 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

# Set up relationship data frame - ACAP
ac_lr_dat <- data.frame(year = acc_surv[2:15,1], acc_bm = acc_surv[2:15,2], NLFPM_bm = ac_rep$iye) #have to y+1

# Linear relationship 
fit <- lm(acc_bm~NLFPM_bm, data = ac_lr_dat) # thought is: can NLFPM predict acoustic survey accurately
cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated

ac_lr_dat <- na.omit(ac_lr_dat)

p11 <- ggplot(data = ac_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
  geom_point(aes(colour = year), size = 1.5) +

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1981,1995), midpoint = 1987,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle("Engel\nd) Fall 2J3KL Cod/Plaice") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

# Set up relationship data frame - GH
gh_lr_dat <- data.frame(year = acc_surv[2:15,1], acc_bm = acc_surv[2:15,2], NLFPM_bm = gh_rep$iye)

# Linear relationship 
fit <- lm(acc_bm~NLFPM_bm, data = gh_lr_dat) # thought is: can NLFPM predict acoustic survey accurately
cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated

gh_lr_dat <- na.omit(gh_lr_dat)

p12 <- ggplot(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
  geom_point(aes(colour = year), size = 1.5) +

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1981,1995), midpoint = 1987,  low = "blue", mid = "#FFAEFF", high = "red") +
  theme_classic() +
  ggtitle(" \ne) Fall 2J3KL Halibut") +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

```

### Spring

```{r}
load(file = "./ModelSaves/ACAP-SprEng_Length.RData")
load(file = "./ModelSaves/GH-SprEng_Length.RData")

acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1983 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

# Set up relationship data frame - ACAP
ac_lr_dat <- data.frame(year = acc_surv[2:13,1], acc_bm = acc_surv[2:13,2], NLFPM_bm = c(ac_rep$iye[12], ac_rep$iye[1:11])) #have to y+1

# Linear relationship 
fit <- lm(acc_bm~NLFPM_bm, data = ac_lr_dat) # thought is: can NLFPM predict acoustic survey accurately
cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated

ac_lr_dat <- na.omit(ac_lr_dat)

p13 <- ggplot(data = ac_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
  geom_point(aes(colour = year), size = 1.5) +

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle("\nf) Spring 2J3KL Cod/Plaice") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

# Set up relationship data frame - GH
gh_lr_dat <- data.frame(year = acc_surv[2:13,1], acc_bm = acc_surv[2:13,2], NLFPM_bm = c(gh_rep$iye[12], gh_rep$iye[1:11]))

# Linear relationship 
fit <- lm(acc_bm~NLFPM_bm, data = gh_lr_dat) # thought is: can NLFPM predict acoustic survey accurately
cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated

gh_lr_dat <- na.omit(gh_lr_dat)

p14 <- ggplot(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
  geom_point(aes(colour = year), size = 1.5) +

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
  theme_classic() +
  ggtitle(" \ng) Spring 2J3KL Halibut") +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))
```

## - Figure 3

```{r, fig.width=14, fig.height=8}
p0 <- ggplot() +
  geom_point(aes(x = 0, y = 0, colour = "white"), size = 1.5)+
  scale_x_continuous(limits = c(0.1,1))+
  theme_classic()

p15 <- ggarrange(p8+theme(axis.title.x = element_blank()),
          p9+theme(axis.title.x = element_blank(),axis.title.y = element_blank()),
          p10+theme(axis.title.x = element_blank(),axis.title.y = element_blank()),
          p0+theme(text = element_blank(), title = element_blank(), line = element_blank()),
          nrow = 1, ncol = 4,
          align = "v", legend = "right", common.legend = T)

p16 <- ggarrange(p11,
          p12+theme(axis.title.y = element_blank()),
          p13+theme(axis.title.y = element_blank()),
          p14+theme(axis.title.y = element_blank()),
          nrow = 1, ncol = 4,
          align = "hv", legend = "right", common.legend = T)

p17 <- ggarrange(p15,p16,
          nrow = 2, ncol = 1, align = "h")

ggsave(filename = "survcomp.tiff", device = "tiff", plot = p17, path = "./Figures",
       dpi = 300, width = 16, height = 8, units = "in")
```

# Spatial Comparison

## Fall 2J3KL

```{r}
load(file = "./ModelSaves/FallCamp_Length.RData")

# Set up relationship data frame
lr_dat <- data.frame(year = unique(fishy_dat$year)[1:26], jkl_NLFPM_bm = rep$iye[1:26])

load(file = "./ModelSaves/3LFallCamp_Length.RData")

lr_dat$l_NLFPM_bm <- rep$iye

# Linear relationship 
fit <- lm(jkl_NLFPM_bm~l_NLFPM_bm, data = lr_dat)
cor.test(x = lr_dat$jkl_NLFPM_bm, y = lr_dat$l_NLFPM_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated

car::influencePlot.lm(fit)

```

## - Figure 4

```{r}
p18 <- ggplot(data = lr_dat, aes(x = l_NLFPM_bm, y = jkl_NLFPM_bm)) +
  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
  geom_point(aes(colour = year), size = 1.5) +

  scale_x_continuous(name = "3L NLFPM Abundance Index", expand = c(0.005,0)) +
  scale_y_continuous(name = "2J3KL NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_colour_gradient2(name = "Year", limits = c(1995,2021), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
        legend.position = 'right', legend.direction = "vertical",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
        axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"))

ggsave(filename = "spatialcomp.tiff", device = "tiff", plot = p18, path = "./Figures",
       dpi = 300, width = 5, height = 4.5, units = "in")
```

### 2024-10-24 Analysis/Campelen/Fall/3L/3LFallCamp-SetUp.R

@@ -1,0 +1,170 @@
+# Set up data
+library(tidyverse)
+library(TMB)
+dyn.load("./TMBcode/SclNLFPM")
+
+# load rstrap set data
+load(file = "./Data/setdet.rda") 
+setdet <- setdet %>% mutate(v.t.s = paste(vessel,trip,set, sep = ".")) %>% 
+  filter(spec == "889"|spec == "438"|spec == "892") %>%
+  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)),
+         long_dd = as.numeric(format(trimws(long.start), digits = 5)))
+
+
+# load and format trawl and stomach contents data
+camp_fall <- read.csv("./Data/dfo_camp_dat.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = ".")) %>%
+  rename(year = YEAR, trawl_pa = Capelin_PA)
+camp_fall <- left_join(camp_fall, 
+                       setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
+camp_fall <- camp_fall %>% filter(data.series == "Campelen" & season == "FALL"& is.na(bot.temp) == FALSE) %>%
+  mutate(lat_dd = as.numeric(trimws(lat_dd)),
+         long_dd = as.numeric(trimws(long_dd)))
+
+
+call_fall <- read.csv("./Data/dfo_call_dat.csv")
+call_fall <- left_join(call_fall, 
+                       camp_fall %>% select(v.t.s, lat_dd, long_dd, set.depth.max, bot.temp), by = c("v.t.s"))
+call_fall <- call_fall %>% filter(data.series == "Campelen" & season == "fall" & is.na(bot.temp) == FALSE)%>% 
+  mutate(content = rep("called", length(data.series))) %>%
+  select(year, month, content, alt.name, pa, NAFOdiv, length, bot.temp, lat_dd, long_dd)
+call_fall <- call_fall  %>%
+  filter((alt.name == "Atlantic cod" & length > 17)|(alt.name == "Greenland halibut" & length > 19)|(alt.name == "American plaice" & length > 29))
+
+
+full_fall <- read.csv("./Data/NAFC_diet_capelin_COD_TURBOT_PLAICE_2J3KL.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."))
+full_fall <- left_join(full_fall, 
[…]

### 2024-10-24 Analysis/Campelen/Fall/3L/3LFallCamp_Length.R

@@ -1,0 +1,60 @@
+# Set up data
+source("./Analysis/Campelen/Fall/3L/3LFallCamp-SetUp.R")
+
+
+
+model <- 0
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
+                 idmod = fishy_dat$idmod,
+                 ndex = length(unique(fishy_dat$idex)),
+                 idex = fishy_dat$idex,
+                 omega = omega$value,
+                 Omin = unique(omega$min)[2:length(n)],
+                 Omax = unique(omega$max)[2:length(n)]
+)
+
+param_list <- list(
+  iye = seq(from = log(10), to = log(20), length.out = tmb_data$nyrs),
+  logrw_var = log(1),
+  lchi = c(rep(log(0.5), (length(n)-1))),
+  lbeta = c(rep(log(0.5), (length(n)-1))),
+  lscl = c(rep(log(0.75), (length(n)-1)))
+)
+
+
+
+
+map <- list(lscl = as.factor(c(rep(NA, length(param_list$lscl)))))
+
+obj <- MakeADFun(data = tmb_data, map=map,
+                 parameters = param_list,
+                 DLL = "SclNLFPM", 
+                 random = c("iye"))
+
+opt <- nlminb(obj$par, obj$fn, obj$gr, control = list(trace = 10, eval.max = 2000, iter.max = 1000), silent = TRUE)
+
+
[…]

### 2024-10-24 Analysis/Campelen/Fall/FallCamp-SetUp.R

@@ -1,0 +1,170 @@
+# Set up data
+library(tidyverse)
+library(TMB)
+dyn.load("./TMBcode/SclNLFPM")
+
+# load rstrap set data
+load(file = "./Data/setdet.rda") 
+setdet <- setdet %>% mutate(v.t.s = paste(vessel,trip,set, sep = ".")) %>% 
+  filter(spec == "889"|spec == "438"|spec == "892") %>%
+  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)),
+         long_dd = as.numeric(format(trimws(long.start), digits = 5)))
+
+
+# load and format trawl and stomach contents data
+camp_fall <- read.csv("./Data/dfo_camp_dat.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = ".")) %>%
+  rename(year = YEAR, trawl_pa = Capelin_PA)
+camp_fall <- left_join(camp_fall, 
+                       setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
+camp_fall <- camp_fall %>% filter(data.series == "Campelen" & season == "FALL"& is.na(bot.temp) == FALSE) %>%
+  mutate(lat_dd = as.numeric(trimws(lat_dd)),
+         long_dd = as.numeric(trimws(long_dd)))
+
+
+call_fall <- read.csv("./Data/dfo_call_dat.csv")
+call_fall <- left_join(call_fall, 
+                       camp_fall %>% select(v.t.s, lat_dd, long_dd, set.depth.max, bot.temp), by = c("v.t.s"))
+call_fall <- call_fall %>% filter(data.series == "Campelen" & season == "fall" & is.na(bot.temp) == FALSE)%>% 
+  mutate(content = rep("called", length(data.series))) %>%
+  select(year, month, content, alt.name, pa, NAFOdiv, length, bot.temp, lat_dd, long_dd)
+call_fall <- call_fall  %>%
+  filter((alt.name == "Atlantic cod" & length > 17)|(alt.name == "Greenland halibut" & length > 19)|(alt.name == "American plaice" & length > 29))
+
+
+full_fall <- read.csv("./Data/NAFC_diet_capelin_COD_TURBOT_PLAICE_2J3KL.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."))
+full_fall <- left_join(full_fall, 
[…]

### 2024-10-24 Analysis/Campelen/Fall/FallCamp_Base.R

@@ -1,0 +1,86 @@
+# Set up data
+source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")
+
+
+
+## Set up for model
+n <- c(length(trawlf$year), length(AC_stof$year), length(GH_stof$year), length(AP_stof$year))
+pa <- c(trawlf$pa, AC_stof$pa, GH_stof$pa, AP_stof$pa)
+year <- c(trawlf$year, AC_stof$year, GH_stof$year, AP_stof$year)
+names <- c("Trawl", "Atlantic cod", "Greenland halibut", "American plaice")
+id = c(0,1,2,3)
+model <- 0
+
+sd_temp <- c(sd(trawlf$bot.temp), 
+             sd(AC_stof$bot.temp), 
+             sd(GH_stof$bot.temp), 
+             sd(AP_stof$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(AC_stof$bot.temp), 
+          median(GH_stof$bot.temp), 
+          median(AP_stof$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          AC_stof$bot.temp, 
+          GH_stof$bot.temp, 
+          AP_stof$bot.temp)
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n), 
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
+                 idmod = fishy_dat$idmod,
[…]

### 2024-10-24 Analysis/Campelen/Fall/FallCamp_Length.R

@@ -1,0 +1,64 @@
+# Set up data
+source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")
+
+
+
+model <- 0
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
+                 idmod = fishy_dat$idmod,
+                 ndex = length(unique(fishy_dat$idex)),
+                 idex = fishy_dat$idex,
+                 omega = omega$value,
+                 Omin = unique(omega$min)[2:length(n)],
+                 Omax = unique(omega$max)[2:length(n)]
+)
+
+param_list <- list(
+  iye = seq(from = log(10), to = log(20), length.out = tmb_data$nyrs),
+  logrw_var = log(1),
+  lchi = c(rep(log(0.5), (length(n)-1))),
+  lbeta = c(rep(log(0.5), (length(n)-1))),
+  lscl = c(rep(log(0.75), (length(n)-1)))
+)
+
+
+library(TMB)
+# dyn.unload("./TMBcode/SclNLFPM")
+# compile("./TMBcode/SclNLFPM.cpp")
+dyn.load("./TMBcode/SclNLFPM")
+
+
+map <- list(lscl = as.factor(c(rep(NA, length(param_list$lscl)))))
+
+obj <- MakeADFun(data = tmb_data, map=map,
+                 parameters = param_list,
+                 DLL = "SclNLFPM", 
[…]

### 2024-10-24 Analysis/Campelen/Fall/FallCamp_Temp.R

@@ -1,0 +1,85 @@
+# Set up data
+source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")
+
+
+
+## Set up for model
+n <- c(length(trawlf$year), length(AC_stof$year), length(GH_stof$year), length(AP_stof$year))
+pa <- c(trawlf$pa, AC_stof$pa, GH_stof$pa, AP_stof$pa)
+year <- c(trawlf$year, AC_stof$year, GH_stof$year, AP_stof$year)
+names <- c("Trawl", "Atlantic cod", "Greenland halibut", "American plaice")
+id = c(0,1,2,3)
+model <- 5
+
+sd_temp <- c(sd(trawlf$bot.temp), 
+             sd(AC_stof$bot.temp), 
+             sd(GH_stof$bot.temp), 
+             sd(AP_stof$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(AC_stof$bot.temp), 
+          median(GH_stof$bot.temp), 
+          median(AP_stof$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          AC_stof$bot.temp, 
+          GH_stof$bot.temp, 
+          AP_stof$bot.temp)
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
+                 idmod = fishy_dat$idmod,
[…]

### 2024-10-24 Analysis/Campelen/Fall/FallCamp_TempLength.R

@@ -1,0 +1,63 @@
+# Set up data
+source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")
+
+
+
+model <- 5
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
+                 idmod = fishy_dat$idmod,
+                 ndex = length(unique(fishy_dat$idex)),
+                 idex = fishy_dat$idex,
+                 omega = omega$value,
+                 Omin = unique(omega$min)[2:length(n)],
+                 Omax = unique(omega$max)[2:length(n)]
+)
+
+param_list <- list(
+  iye = seq(from = log(10), to = log(20), length.out = tmb_data$nyrs),
+  logrw_var = log(1),
+  lchi = c(rep(log(0.5), (length(n)-1))),
+  lbeta = c(rep(log(0.5), (length(n)-1))),
+  lscl = c(rep(log(0.75), (length(n)-1)))
+)
+
+
+library(TMB)
+# dyn.unload("./TMBcode/SclNLFPM")
+# compile("./TMBcode/SclNLFPM.cpp")
+dyn.load("./TMBcode/SclNLFPM")
+
+
+obj <- MakeADFun(data = tmb_data,
+                 parameters = param_list,
+                 DLL = "SclNLFPM", 
+                 random = c("iye"))
+
[…]

### 2024-10-24 Analysis/Campelen/Spring/AC-SprCamp_Length.R

@@ -1,0 +1,79 @@
+# Set up data
+source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")
+
+# Set up model env
+n <- c(length(trawlf$year),
+       length(ac1$year),length(ac2$year))
+pa <- c(trawlf$pa, 
+        ac1$pa, ac2$pa)
+year <- c(trawlf$year, 
+          ac1$year, ac2$year)
+names <- c("Trawl", "ac1","ac2")
+id <- c(seq(0,(length(names)-1)))
+
+
+sd_temp <- c(sd(trawlf$bot.temp),
+             sd(ac1$bot.temp),sd(ac2$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(ac1$bot.temp), median(ac2$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          ac1$bot.temp, ac2$bot.temp)
+
+
+spp_n <- c(length(trawlf$year), 
+           sum(length(ac1$year),length(ac2$year)))
+spp_id <- c(0,1)
+
+model <- 0
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
+                 idmod = fishy_dat$idmod,
+                 ndex = length(unique(fishy_dat$idex)),
+                 idex = fishy_dat$idex,
+                 omega = omega$value,
[…]

### 2024-10-24 Analysis/Campelen/Spring/ACAP-SprCamp_Length.R

@@ -1,0 +1,86 @@
+# Set up data
+source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")
+
+# Set up model env
+n <- c(length(trawlf$year),
+       length(ac1$year),length(ac2$year),
+       length(ap1$year))
+pa <- c(trawlf$pa, 
+        ac1$pa, ac2$pa, 
+        ap1$pa)
+year <- c(trawlf$year, 
+          ac1$year, ac2$year,
+          ap1$year)
+names <- c("Trawl", "ac1","ac2", "ap1")
+id <- c(seq(0,(length(names)-1)))
+
+
+sd_temp <- c(sd(trawlf$bot.temp),
+             sd(ac1$bot.temp),sd(ac2$bot.temp),
+             sd(ap1$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(ac1$bot.temp), median(ac2$bot.temp),  
+          median(ap1$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          ac1$bot.temp, ac2$bot.temp,
+          ap1$bot.temp)
+
+
+spp_n <- c(length(trawlf$year), 
+           sum(length(ac1$year),length(ac2$year)), 
+           sum(length(ap1$year)))
+spp_id <- c(0,1,2)
+
+model <- 0
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
[…]

### 2024-10-24 Analysis/Campelen/Spring/AP-SprCamp_Length.R

@@ -1,0 +1,82 @@
+# Set up data
+source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")
+
+# Set up model env
+n <- c(length(trawlf$year),
+       length(ap1$year))
+pa <- c(trawlf$pa, 
+        ap1$pa)
+year <- c(trawlf$year, 
+          ap1$year)
+names <- c("Trawl", "ap1")
+id <- c(seq(0,(length(names)-1)))
+
+
+sd_temp <- c(sd(trawlf$bot.temp),
+             sd(ap1$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(ap1$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          ap1$bot.temp)
+
+
+spp_n <- c(length(trawlf$year), 
+           sum(length(ap1$year)))
+spp_id <- c(0,1)
+
+model <- 0
+
+ap_fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = ap_fishy_dat$names, value = rep(NA, length(ap_fishy_dat$pa)))
+for(i in 1:length(ap_fishy_dat$pa)){
+  omega[i,2] = (1/(ap_fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((ap_fishy_dat$temp[i]-ap_fishy_dat$itopt[i])/ap_fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+ap_tmb_data <- list(n = length(ap_fishy_dat$pa),
+                    nyrs = length(unique(ap_fishy_dat$year)),
+                    iyear = ap_fishy_dat$year - min(ap_fishy_dat$year),
+                    k = 1,
+                    pa = ap_fishy_dat$pa,
+                    idmod = ap_fishy_dat$idmod,
+                    ndex = length(unique(ap_fishy_dat$idex)),
+                    idex = ap_fishy_dat$idex,
+                    omega = omega$value,
+                    Omin = unique(omega$min)[2:length(n)],
[…]

### 2024-10-24 Analysis/Campelen/Spring/GH-SprCamp_Length.R

@@ -1,0 +1,82 @@
+# Set up data
+source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")
+
+# Set up model env
+n <- c(length(trawlf$year),
+       length(gh1$year),length(gh2$year))
+pa <- c(trawlf$pa, 
+        gh1$pa, gh2$pa)
+year <- c(trawlf$year, 
+          gh1$year, gh2$year)
+names <- c("Trawl", "gh1","gh2")
+id <- c(seq(0,(length(names)-1)))
+
+
+sd_temp <- c(sd(trawlf$bot.temp),
+             sd(gh1$bot.temp),sd(gh2$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(gh1$bot.temp), median(gh2$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          gh1$bot.temp, gh2$bot.temp)
+
+
+spp_n <- c(length(trawlf$year), 
+           sum(length(gh1$year),length(gh2$year)))
+spp_id <- c(0,1)
+
+model <- 0
+
+gh_fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = gh_fishy_dat$names, value = rep(NA, length(gh_fishy_dat$pa)))
+for(i in 1:length(gh_fishy_dat$pa)){
+  omega[i,2] = (1/(gh_fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((gh_fishy_dat$temp[i]-gh_fishy_dat$itopt[i])/gh_fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+gh_tmb_data <- list(n = length(gh_fishy_dat$pa),
+                    nyrs = length(unique(gh_fishy_dat$year)),
+                    iyear = gh_fishy_dat$year - min(gh_fishy_dat$year),
+                    k = 1,
+                    pa = gh_fishy_dat$pa,
+                    idmod = gh_fishy_dat$idmod,
+                    ndex = length(unique(gh_fishy_dat$idex)),
[…]

### 2024-10-24 Analysis/Campelen/Spring/GHAP-SprCamp_Length.R

@@ -1,0 +1,87 @@
+# Set up data
+source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")
+
+# Set up model env
+n <- c(length(trawlf$year),
+       length(gh1$year),length(gh2$year),
+       length(ap1$year))
+pa <- c(trawlf$pa, 
+        gh1$pa, gh2$pa,
+        ap1$pa)
+year <- c(trawlf$year, 
+          gh1$year, gh2$year,
+          ap1$year)
+names <- c("Trawl", "gh1","gh2", "ap1")
+id <- c(seq(0,(length(names)-1)))
+
+
+sd_temp <- c(sd(trawlf$bot.temp),
+             sd(gh1$bot.temp),sd(gh2$bot.temp),
+             sd(ap1$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(gh1$bot.temp), median(gh2$bot.temp),  
+          median(ap1$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          gh1$bot.temp, gh2$bot.temp,
+          ap1$bot.temp)
+
+
+spp_n <- c(length(trawlf$year), 
+           sum(length(gh1$year),length(gh2$year)),
+           sum(length(ap1$year)))
+spp_id <- c(0,1,2)
+
+
+model <- 0
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
[…]

### 2024-10-24 Analysis/Campelen/Spring/SprCamp-SetUp.R

@@ -1,0 +1,170 @@
+# Set up data
+library(tidyverse)
+library(TMB)
+dyn.load("./TMBcode/SclNLFPM")
+
+
+
+# load rstrap set data
+load(file = "./Data/setdet.rda") 
+setdet <- setdet %>% mutate(v.t.s = paste(vessel,trip,set, sep = ".")) %>% 
+  filter(spec == "889"|spec == "438"|spec == "892") %>%
+  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)),
+         long_dd = as.numeric(format(trimws(long.start), digits = 5)))
+
+
+# load and format trawl and stomach contents data
+camp_spr <- read.csv("./Data/dfo_camp_dat.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = ".")) %>%
+  rename(year = YEAR, trawl_pa = Capelin_PA)
+camp_spr <- left_join(camp_spr, 
+                      setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
+camp_spr <- camp_spr %>% filter(data.series == "Campelen" & season == "SPRING"& is.na(bot.temp) == FALSE) %>%
+  mutate(lat_dd = as.numeric(trimws(lat_dd)),
+         long_dd = as.numeric(trimws(long_dd)))
+
+
+call_spr <- read.csv("./Data/dfo_call_dat.csv")
+call_spr <- left_join(call_spr, 
+                      camp_spr %>% select(v.t.s, lat_dd, long_dd, set.depth.max, bot.temp), by = c("v.t.s"))
+call_spr <- call_spr %>% filter(data.series == "Campelen" & season == "spring" & is.na(bot.temp) == FALSE) %>%
+  mutate(content = rep("called", length(data.series))) %>%
+  select(year, month, content, alt.name, pa, length, bot.temp, lat_dd, long_dd)
+call_spr <- call_spr %>% filter((alt.name == "Atlantic cod" & length > 17)|(alt.name == "Greenland halibut" & length > 19)|(alt.name == "American plaice" & length > 29))
+
+
+full_spr <- read.csv("./Data/NAFC_diet_capelin_COD_TURBOT_PLAICE_2J3KL.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."))
+full_spr <- left_join(full_spr, 
[…]

### 2024-10-24 Analysis/Campelen/Spring/SprCamp_Base.R

@@ -1,0 +1,81 @@
+# Set up data
+source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")
+
+
+
+## Set up for model
+n <- c(length(trawlf$year), length(AC_stof$year), length(GH_stof$year), length(AP_stof$year))
+pa <- c(trawlf$pa, AC_stof$pa, GH_stof$pa, AP_stof$pa)
+year <- c(trawlf$year, AC_stof$year, GH_stof$year, AP_stof$year)
+names <- c("Trawl", "Atlantic cod", "Greenland halibut", "American plaice")
+id = c(0,1,2,3)
+model <- 0
+
+sd_temp <- c(sd(trawlf$bot.temp), 
+             sd(AC_stof$bot.temp), 
+             sd(GH_stof$bot.temp), 
+             sd(AP_stof$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(AC_stof$bot.temp), 
+          median(GH_stof$bot.temp), 
+          median(AP_stof$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          AC_stof$bot.temp, 
+          GH_stof$bot.temp, 
+          AP_stof$bot.temp)
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n), 
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
+                 idmod = fishy_dat$idmod,
+                 ndex = length(unique(fishy_dat$idex)),
[…]

### 2024-10-24 Analysis/Campelen/Spring/SprCamp_Length.R

@@ -1,0 +1,58 @@
+# Set up data
+source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")
+
+
+
+model <- 0
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
+                 idmod = fishy_dat$idmod,
+                 ndex = length(unique(fishy_dat$idex)),
+                 idex = fishy_dat$idex,
+                 omega = omega$value,
+                 Omin = unique(omega$min)[2:length(n)],
+                 Omax = unique(omega$max)[2:length(n)]
+)
+
+param_list <- list(
+  iye = seq(from = log(10), to = log(20), length.out = tmb_data$nyrs),
+  logrw_var = log(1),
+  lchi = c(rep(log(0.5), (length(n)-1))),
+  lbeta = c(rep(log(0.5), (length(n)-1))),
+  lscl = c(rep(log(0.75), (length(n)-1)))
+)
+
+
+map <- list(lscl = as.factor(c(rep(NA, length(param_list$lscl)))))
+
+obj <- MakeADFun(data = tmb_data, map=map,
+                 parameters = param_list,
+                 DLL = "SclNLFPM", 
+                 random = c("iye"))
+
+opt <- nlminb(obj$par, obj$fn, obj$gr, control = list(trace = 10, eval.max = 2000, iter.max = 1000), silent = TRUE)
+
+
+rep <- obj$report()
[…]

### 2024-10-24 Analysis/Engel/Fall/AC-FallEng_Length.R

@@ -1,0 +1,84 @@
+# Set up data
+source("./Analysis/Engel/Fall/FallEng-SetUp.R")
+
+# Set up model env
+n <- c(length(trawlf$year),
+       length(ac1$year),length(ac2$year))
+pa <- c(trawlf$pa, 
+        ac1$pa, ac2$pa)
+year <- c(trawlf$year, 
+          ac1$year, ac2$year)
+names <- c("Trawl", "ac1","ac2")
+id <- c(seq(0,(length(names)-1)))
+
+
+sd_temp <- c(sd(trawlf$bot.temp),
+             sd(ac1$bot.temp),sd(ac2$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(ac1$bot.temp), median(ac2$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          ac1$bot.temp, ac2$bot.temp)
+
+
+spp_n <- c(length(trawlf$year), 
+           sum(length(ac1$year),length(ac2$year)))
+spp_id <- c(0,1)
+
+
+
+model <- 0
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
+                 idmod = fishy_dat$idmod,
+                 ndex = length(unique(fishy_dat$idex)),
+                 idex = fishy_dat$idex,
+                 omega = omega$value,
[…]

### 2024-10-24 Analysis/Engel/Fall/ACAP-FallEng_Length.R

@@ -1,0 +1,91 @@
+# Set up data
+source("./Analysis/Engel/Fall/FallEng-SetUp.R")
+
+# Set up model env
+n <- c(length(trawlf$year),
+       length(ac1$year),length(ac2$year),
+       length(ap1$year))
+pa <- c(trawlf$pa, 
+        ac1$pa, ac2$pa, 
+        ap1$pa)
+year <- c(trawlf$year, 
+          ac1$year, ac2$year,
+          ap1$year)
+names <- c("Trawl", "ac1","ac2", "ap1")
+id <- c(seq(0,(length(names)-1)))
+
+
+sd_temp <- c(sd(trawlf$bot.temp),
+             sd(ac1$bot.temp),sd(ac2$bot.temp),
+             sd(ap1$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(ac1$bot.temp), median(ac2$bot.temp),  
+          median(ap1$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          ac1$bot.temp, ac2$bot.temp,
+          ap1$bot.temp)
+
+
+spp_n <- c(length(trawlf$year), 
+           sum(length(ac1$year),length(ac2$year)), 
+           sum(length(ap1$year)))
+spp_id <- c(0,1,2)
+
+
+
+model <- 0
+
+ac_fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = ac_fishy_dat$names, value = rep(NA, length(ac_fishy_dat$pa)))
+for(i in 1:length(ac_fishy_dat$pa)){
+  omega[i,2] = (1/(ac_fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((ac_fishy_dat$temp[i]-ac_fishy_dat$itopt[i])/ac_fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+ac_tmb_data <- list(n = length(ac_fishy_dat$pa),
+                 nyrs = length(unique(ac_fishy_dat$year)),
+                 iyear = ac_fishy_dat$year - min(ac_fishy_dat$year),
[…]

### 2024-10-24 Analysis/Engel/Fall/AP-FallEng_Length.R

@@ -1,0 +1,84 @@
+# Set up data
+source("./Analysis/Engel/Fall/FallEng-SetUp.R")
+
+# Set up model env
+n <- c(length(trawlf$year),
+       length(ap1$year))
+pa <- c(trawlf$pa, 
+        ap1$pa)
+year <- c(trawlf$year, 
+          ap1$year)
+names <- c("Trawl", "ap1")
+id <- c(seq(0,(length(names)-1)))
+
+
+sd_temp <- c(sd(trawlf$bot.temp),
+             sd(ap1$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(ap1$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          ap1$bot.temp)
+
+
+spp_n <- c(length(trawlf$year), 
+           sum(length(ap1$year)))
+spp_id <- c(0,1)
+
+
+
+model <- 0
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
+                 idmod = fishy_dat$idmod,
+                 ndex = length(unique(fishy_dat$idex)),
+                 idex = fishy_dat$idex,
+                 omega = omega$value,
+                 Omin = unique(omega$min)[2:length(n)],
+                 Omax = unique(omega$max)[2:length(n)]
+)
+
+param_list <- list(
[…]

### 2024-10-24 Analysis/Engel/Fall/FallEng-SetUp.R

@@ -1,0 +1,168 @@
+# Set up data
+library(tidyverse)
+library(TMB)
+dyn.load("./TMBcode/SclNLFPM")
+
+
+# load rstrap set data
+load(file = "./Data/setdet.rda") 
+setdet <- setdet %>% mutate(v.t.s = paste(vessel,trip,set, sep = ".")) %>% 
+  filter(spec == "889"|spec == "438"|spec == "892") %>%
+  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)),
+         long_dd = as.numeric(format(trimws(long.start), digits = 5)))
+
+
+# load and format trawl and stomach contents data
+eng_fall <- read.csv("./Data/dfo_camp_dat.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = ".")) %>%
+  rename(year = YEAR, trawl_pa = Capelin_PA)
+eng_fall <- left_join(eng_fall, 
+                      setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
+eng_fall <- eng_fall %>% filter(data.series == "Engel" & season == "FALL"& is.na(bot.temp) == FALSE) %>%
+  filter(year >= 1981) %>% 
+  mutate(lat_dd = as.numeric(trimws(lat_dd)),
+         long_dd = as.numeric(trimws(long_dd)))
+
+
+call_fall <- read.csv("./Data/engel_call_dat.csv")
+call_fall <- left_join(call_fall, 
+                       eng_fall %>% select(v.t.s, lat_dd, long_dd, set.depth.max, bot.temp), by = c("v.t.s"))
+call_fall <- call_fall %>% filter(data.series == "Engel" & season == "fall" & is.na(bot.temp) == FALSE) %>% 
+  mutate(content = rep("called", length(data.series))) %>% 
+  select(year, alt.name, content, pa, length, bot.temp, lat_dd, long_dd)
+
+
+full_fall <- read.csv("./Data/NAFC_diet_capelin_COD_TURBOT_PLAICE_2J3KL.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."))
+full_fall <- left_join(full_fall, 
+                       eng_fall %>% select(v.t.s, data.series, set.depth.max, bot.temp), by = c("v.t.s"))
+full_fall <- full_fall %>% mutate(alt.name = PRED_COMM_NAME,
[…]

### 2024-10-24 Analysis/Engel/Fall/FallEng_Length.R

@@ -1,0 +1,61 @@
+# Set up data
+source("./Analysis/Engel/Fall/FallEng-SetUp.R")
+
+
+
+model <- 0
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
+                 idmod = fishy_dat$idmod,
+                 ndex = length(unique(fishy_dat$idex)),
+                 idex = fishy_dat$idex,
+                 omega = omega$value,
+                 Omin = unique(omega$min)[2:length(n)],
+                 Omax = unique(omega$max)[2:length(n)]
+)
+
+param_list <- list(
+  iye = seq(from = log(10), to = log(20), length.out = tmb_data$nyrs),
+  logrw_var = log(1),
+  lchi = c(rep(log(0.5), (length(n)-1))),
+  lbeta = c(rep(log(0.5), (length(n)-1))),
+  lscl = c(rep(log(0.75), (length(n)-1)))
+)
+
+
+
+
+
+map <- list(lscl = as.factor(c(rep(NA, length(param_list$lscl)))))
+
+obj <- MakeADFun(data = tmb_data, map=map,
+                 parameters = param_list,
+                 DLL = "SclNLFPM", 
+                 random = c("iye"))
+
+opt <- nlminb(obj$par, obj$fn, obj$gr, control = list(trace = 10, eval.max = 2000, iter.max = 1000), silent = TRUE)
+
+
[…]

### 2024-10-24 Analysis/Engel/Fall/GH-FallEng_Length.R

@@ -1,0 +1,83 @@
+# Set up data
+source("./Analysis/Engel/Fall/FallEng-SetUp.R")
+
+# Set up model env
+n <- c(length(trawlf$year),
+       length(gh1$year),length(gh2$year))
+pa <- c(trawlf$pa, 
+        gh1$pa, gh2$pa)
+year <- c(trawlf$year, 
+          gh1$year, gh2$year)
+names <- c("Trawl", "gh1","gh2")
+id <- c(seq(0,(length(names)-1)))
+
+
+sd_temp <- c(sd(trawlf$bot.temp),
+             sd(gh1$bot.temp),sd(gh2$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(gh1$bot.temp), median(gh2$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          gh1$bot.temp, gh2$bot.temp)
+
+
+spp_n <- c(length(trawlf$year), 
+           sum(length(gh1$year),length(gh2$year)))
+spp_id <- c(0,1)
+
+
+model <- 0
+
+gh_fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = gh_fishy_dat$names, value = rep(NA, length(gh_fishy_dat$pa)))
+for(i in 1:length(gh_fishy_dat$pa)){
+  omega[i,2] = (1/(gh_fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((gh_fishy_dat$temp[i]-gh_fishy_dat$itopt[i])/gh_fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+gh_tmb_data <- list(n = length(gh_fishy_dat$pa),
+                 nyrs = length(unique(gh_fishy_dat$year)),
+                 iyear = gh_fishy_dat$year - min(gh_fishy_dat$year),
+                 k = 1,
+                 pa = gh_fishy_dat$pa,
+                 idmod = gh_fishy_dat$idmod,
+                 ndex = length(unique(gh_fishy_dat$idex)),
[…]

### 2024-10-24 Analysis/Engel/Fall/GHAP-FallEng_Length.R

@@ -1,0 +1,90 @@
+# Set up data
+source("./Analysis/Engel/Fall/FallEng-SetUp.R")
+
+# Set up model env
+n <- c(length(trawlf$year),
+       length(gh1$year),length(gh2$year),
+       length(ap1$year))
+pa <- c(trawlf$pa, 
+        gh1$pa, gh2$pa,
+        ap1$pa)
+year <- c(trawlf$year, 
+          gh1$year, gh2$year,
+          ap1$year)
+names <- c("Trawl", "gh1","gh2", "ap1")
+id <- c(seq(0,(length(names)-1)))
+
+
+sd_temp <- c(sd(trawlf$bot.temp),
+             sd(gh1$bot.temp),sd(gh2$bot.temp),
+             sd(ap1$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(gh1$bot.temp), median(gh2$bot.temp),  
+          median(ap1$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          gh1$bot.temp, gh2$bot.temp,
+          ap1$bot.temp)
+
+
+spp_n <- c(length(trawlf$year), 
+           sum(length(gh1$year),length(gh2$year)),
+           sum(length(ap1$year)))
+spp_id <- c(0,1,2)
+
+
+model <- 0
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
[…]

### 2024-10-24 Analysis/Engel/Spring/ACAP-SprEng_Length.R

@@ -1,0 +1,89 @@
+# Set up data
+source("./Analysis/Engel/Spring/SprEng-SetUp.R")
+
+# Set up model env
+n <- c(length(trawlf$year),
+       length(ac1$year),length(ac2$year),
+       length(ap1$year))
+pa <- c(trawlf$pa, 
+        ac1$pa, ac2$pa, 
+        ap1$pa)
+year <- c(trawlf$year, 
+          ac1$year, ac2$year,
+          ap1$year)
+names <- c("Trawl", "ac1","ac2", "ap1")
+id <- c(seq(0,(length(names)-1)))
+
+
+sd_temp <- c(sd(trawlf$bot.temp),
+             sd(ac1$bot.temp),sd(ac2$bot.temp),
+             sd(ap1$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(ac1$bot.temp), median(ac2$bot.temp),  
+          median(ap1$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          ac1$bot.temp, ac2$bot.temp,
+          ap1$bot.temp)
+
+
+spp_n <- c(length(trawlf$year), 
+           sum(length(ac1$year),length(ac2$year)), 
+           sum(length(ap1$year)))
+spp_id <- c(0,1,2)
+
+model <- 0
+
+ac_fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = ac_fishy_dat$names, value = rep(NA, length(ac_fishy_dat$pa)))
+for(i in 1:length(ac_fishy_dat$pa)){
+  omega[i,2] = (1/(ac_fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((ac_fishy_dat$temp[i]-ac_fishy_dat$itopt[i])/ac_fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+ac_tmb_data <- list(n = length(ac_fishy_dat$pa),
+                    nyrs = length(unique(ac_fishy_dat$year)),
+                    iyear = ac_fishy_dat$year - min(ac_fishy_dat$year),
+                    k = 1,
[…]

### 2024-10-24 Analysis/Engel/Spring/GH-SprEng_Length.R

@@ -1,0 +1,82 @@
+# Set up data
+source("./Analysis/Engel/Spring/SprEng-SetUp.R")
+
+# Set up model env
+n <- c(length(trawlf$year),
+       length(gh1$year),length(gh2$year))
+pa <- c(trawlf$pa, 
+        gh1$pa, gh2$pa)
+year <- c(trawlf$year, 
+          gh1$year, gh2$year)
+names <- c("Trawl", "gh1","gh2")
+id <- c(seq(0,(length(names)-1)))
+
+
+sd_temp <- c(sd(trawlf$bot.temp),
+             sd(gh1$bot.temp),sd(gh2$bot.temp))
+topt <- c(median(trawlf$bot.temp), 
+          median(gh1$bot.temp), median(gh2$bot.temp))
+temp <- c(trawlf$bot.temp, 
+          gh1$bot.temp, gh2$bot.temp)
+
+
+spp_n <- c(length(trawlf$year), 
+           sum(length(gh1$year),length(gh2$year)))
+spp_id <- c(0,1)
+
+model <- 0
+
+gh_fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = gh_fishy_dat$names, value = rep(NA, length(gh_fishy_dat$pa)))
+for(i in 1:length(gh_fishy_dat$pa)){
+  omega[i,2] = (1/(gh_fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((gh_fishy_dat$temp[i]-gh_fishy_dat$itopt[i])/gh_fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+gh_tmb_data <- list(n = length(gh_fishy_dat$pa),
+                    nyrs = length(unique(gh_fishy_dat$year)),
+                    iyear = gh_fishy_dat$year - min(gh_fishy_dat$year),
+                    k = 1,
+                    pa = gh_fishy_dat$pa,
+                    idmod = gh_fishy_dat$idmod,
+                    ndex = length(unique(gh_fishy_dat$idex)),
[…]

### 2024-10-24 Analysis/Engel/Spring/SprEng-SetUp.R

@@ -1,0 +1,167 @@
+# Set up data
+library(tidyverse)
+library(TMB)
+dyn.load("./TMBcode/SclNLFPM")
+
+
+# load rstrap set data
+load(file = "./Data/setdet.rda") 
+setdet <- setdet %>% mutate(v.t.s = paste(vessel,trip,set, sep = ".")) %>% 
+  filter(spec == "889"|spec == "438"|spec == "892") %>%
+  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)),
+         long_dd = as.numeric(format(trimws(long.start), digits = 5)))
+
+
+# load and format trawl and stomach contents data
+eng_spr <- read.csv("./Data/dfo_camp_dat.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = ".")) %>%
+  rename(year = YEAR, trawl_pa = Capelin_PA)
+eng_spr <- left_join(eng_spr, 
+                     setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
+eng_spr <- eng_spr %>% filter(data.series == "Engel" & season == "SPRING" & is.na(bot.temp) == FALSE) %>%
+  filter(year >= 1981) %>% 
+  mutate(lat_dd = as.numeric(trimws(lat_dd)),
+         long_dd = as.numeric(trimws(long_dd)))
+
+
+call_spr <- read.csv("./Data/engel_call_dat.csv")
+call_spr <- left_join(call_spr, 
+                      eng_spr %>% select(v.t.s, lat_dd, long_dd, set.depth.max, bot.temp), by = c("v.t.s"))
+call_spr <- call_spr %>% filter(data.series == "Engel" & season == "spring" & is.na(bot.temp) == FALSE) %>%
+  mutate(content = rep("called", length(data.series))) %>% 
+  select(year, alt.name, content, pa, length, bot.temp, lat_dd, long_dd)
+
+
+full_spr <- read.csv("./Data/NAFC_diet_capelin_COD_TURBOT_PLAICE_2J3KL.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."))
+full_spr <- left_join(full_spr, 
+                      eng_spr %>% select(v.t.s, data.series, set.depth.max, bot.temp), by = c("v.t.s"))
+full_spr <- full_spr %>% mutate(alt.name = PRED_COMM_NAME,
[…]

### 2024-10-24 Analysis/Engel/Spring/SprEng_Length.R

@@ -1,0 +1,59 @@
+# Set up data
+source("./Analysis/Engel/Spring/SprEng-SetUp.R")
+
+
+
+model <- 0
+
+fishy_dat <- data.frame(pa = pa, 
+                        year = year, 
+                        names = rep(names, n),
+                        idmod = rep(model, sum(n)),
+                        idex = rep(id, n),
+                        temp = temp,
+                        isd_temp = rep(sd_temp, n),
+                        itopt = rep(topt, n))
+
+omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
+for(i in 1:length(fishy_dat$pa)){
+  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
+}
+omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+
+tmb_data <- list(n = length(fishy_dat$pa),
+                 nyrs = length(unique(fishy_dat$year)),
+                 iyear = fishy_dat$year - min(fishy_dat$year),
+                 k = 1,
+                 pa = fishy_dat$pa,
+                 idmod = fishy_dat$idmod,
+                 ndex = length(unique(fishy_dat$idex)),
+                 idex = fishy_dat$idex,
+                 omega = omega$value,
+                 Omin = unique(omega$min)[2:length(n)],
+                 Omax = unique(omega$max)[2:length(n)]
+)
+
+param_list <- list(
+  iye = seq(from = log(10), to = log(20), length.out = tmb_data$nyrs),
+  logrw_var = log(1),
+  lchi = c(rep(log(0.5), (length(n)-1))),
+  lbeta = c(rep(log(0.5), (length(n)-1))),
+  lscl = c(rep(log(0.75), (length(n)-1)))
+)
+
+
+
+map <- list(lscl = as.factor(c(rep(NA, length(param_list$lscl)))))
+
+obj <- MakeADFun(data = tmb_data, map=map,
+                 parameters = param_list,
+                 DLL = "SclNLFPM", 
+                 random = c("iye"))
+
+opt <- nlminb(obj$par, obj$fn, obj$gr, control = list(trace = 10, eval.max = 2000, iter.max = 1000), silent = TRUE)
+
+
+rep <- obj$report()
[…]

### 2024-10-24 TMBcode/SclNLFPM.cpp

@@ -1,0 +1,147 @@
+
+#include <TMB.hpp> 
+#include <iostream>
+
+template<class Type> //only list this in whichever cpp file is alphabetically first since thats the first cpp file read in and the others aren't include guarded meaning it will tell you that it has been re-defined
+bool isNA(Type x){
+  return R_IsNA(asDouble(x));
+}
+
+template<class Type>
+Type objective_function<Type>::operator() ()
+{
+  
+  using namespace density;
+  Type nll = 0.0;
+  Type one = 1.0;
+
+  //READ IN THE INPUT DATA
+  DATA_INTEGER(n);
+  DATA_INTEGER(nyrs);
+  // DATA_INTEGER(ndex);
+  DATA_IVECTOR(iyear);
+  DATA_IVECTOR(idex);
+  DATA_SCALAR(k);
+  DATA_VECTOR(pa);
+  DATA_IVECTOR(idmod);
+  //TEMPERATURE MODIFIER
+  DATA_VECTOR(omega);
+  DATA_VECTOR(Omin);
+  DATA_VECTOR(Omax);
+
+  
+  //READ THE PARAMETERS
+  PARAMETER_VECTOR(iye);
+  PARAMETER(logrw_var);  
+  PARAMETER_VECTOR(lchi);
+  PARAMETER_VECTOR(lbeta);
+  PARAMETER_VECTOR(lscl);
+  
+  //TRANSFORM PARAMETERS AND CREATE DERIVED PARAMETERS
+  Type rw_var = exp(logrw_var);
+  vector<Type> beta = exp(lbeta);
+  vector<Type> chi = exp(lchi);
+  
+  // SCALING PARAMETER FOR TEMPERATURE MODIFICATION
+  vector<Type> scl(lscl.size());
+  for(int i = 0; i < lscl.size(); i++){
+    if(idmod(i) == 0){scl(i) = k;}
+    if(idmod(i) == 5){scl(i) = exp(lscl(i))/(1+exp(lscl(i)));}
+  }
+  
+  
+  // SET UP ENV FOR VARIABLES USED IN FUNCTIONAL RESPONSE EQUATION
+  vector<Type> mu(nyrs);
+  vector<Type> new_mu(n);
+  vector<Type> tomega(n);
+  
+  // SET UP ENV FOR RESIDUALS
+  vector<Type> sto_resid(n);
[…]

### 2024-10-30 Cook'sDistance.Rmd
October 30, before committee meeting

--- 2024-10-24 PaperSections.Rmd
@@
-# Setup Env
-
-```{r include=FALSE}
+```{r}
 library(tidyverse)
-library(ggpubr)
-library(cowplot)
-```
-
-# Abundance Section
-
-## Acoustic
-
-### Campelen
-
-```{r}
-# acc_surv <- read.csv("./Data/Capelin_AccSurv.csv") %>% filter(Year > 1980) %>% rename(acsurv_bm = names(Capelin_AccSurv)[2])
-acc_surv <- read.csv("./Data/Capelin_AccSurv.csv") %>% 
-  filter(Year > 1994) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)
-
-## Survey year proper
-p1 <- ggplot(data = acc_surv) +
-  geom_line(aes(x = Year, y = acsurv_bm), colour = "#BB2D05", linewidth = 1) +
-  geom_point(aes(x = Year, y = acsurv_bm), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
-  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1995, 2020.9), breaks = c(seq(1995, 2020, 5))) + 
-  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.009,0), limits = c(0, 1100)) +
-  ggtitle("Campelen\na) Spring") +
-  theme_classic() +
-  theme(legend.position = "none",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.line.x = element_line(size = 0.7), axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"), 
-        plot.title = element_text(size = 16, face = "bold"))
-```
-
-### Engel
-
-```{r}
-acc_surv <- read.csv("./Data/Capelin_AccSurv.csv") %>% 
-  filter(Year > 1980 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)
-
-## Survey year proper
-p2 <- ggplot(data = acc_surv) +
-  geom_line(aes(x = Year, y = acsurv_bm), colour = "#BB2D05", linewidth = 1) +
-  geom_point(aes(x = Year, y = acsurv_bm), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
-  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1981,1995.1), breaks = c(seq(1981,1995, 3))) + 
-  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.009,0), limits = c(0,6000)) +
-  ggtitle("Engel\nb) Spring") +
-  theme_classic() +
-  theme(legend.position = "none",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.line.x = element_line(size = 0.7), axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"), 
-        plot.title = element_text(size = 16, face = "bold"))
 ```
@@
 
-### Spring
-
-```{r}
-load(file = "./ModelSaves/AP-SprCamp_Length.RData")
-load(file = "./ModelSaves/GH-SprCamp_Length.RData")
-
-# Set up index df - GH
-gh_data <- gh_fishy_dat
-gh_uni_names <- unique(gh_data$names)
-gh_dat_names <- c("Index", gh_uni_names)
-
-gh_new_list <- list()
-for(i in 1:length(gh_uni_names)){
-  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
-  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-gh_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  gh_new_list
-)
-
-# Set up index df - AC
-ap_data <- ap_fishy_dat
-ap_uni_names <- unique(ap_data$names)
-ap_dat_names <- c("Index", ap_uni_names)
-
-ap_new_list <- list()
-for(i in 1:length(ap_uni_names)){
-  ap_one_dex <- subset(ap_data, names == ap_uni_names[i])
-  ap_new_list[[i]] <- aggregate(ap_one_dex$pa, by = list(ap_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-ap_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  ap_new_list
-)
-
-gh_low_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] - qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
-gh_high_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] + qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
-gh_ts_df <- data.frame(ts = gh_rep$iye, time = gh_multi_inner[,1], low_sd = gh_low_rho, high_sd = gh_high_rho)
-
-ap_low_rho = ap_sdrep$value[names(ap_sdrep$value) == "iye"] - qnorm(0.975)*ap_sdrep$sd[names(ap_sdrep$value) == "iye"]
-ap_high_rho = ap_sdrep$value[names(ap_sdrep$value) == "iye"] + qnorm(0.975)*ap_sdrep$sd[names(ap_sdrep$value) == "iye"]
-ap_ts_df <- data.frame(ts = ap_rep$iye, time = ap_multi_inner[,1], low_sd = ap_low_rho, high_sd = ap_high_rho)
-
-p3 <- ggplot() +
-  geom_line(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
-  geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
-
-  geom_line(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
-  geom_point(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
-
-  geom_ribbon(data = gh_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
-  geom_point(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
-
-  geom_ribbon(data = ap_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = ap_ts_df, aes(x = time, y = ts, colour = "ap"), size = 1.5) +
-  geom_point(data = ap_ts_df, aes(x = time, y = ts, colour = "ap"), size = 1.5) +
-
-  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1995,2021), breaks = c(seq(1995, 2021, 5))) + 
-  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.6,2.4)) +
-  scale_color_manual(name = "Species Model", values = c(all = "black", surv = "#BB2D05", ap = "#FF7733", gh = "#048BA8"),
-                     labels = c(all = "All species", surv = "Acoustic survey", ap = "Plaice", gh = "Greenland halibut")) +
-  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
-  ggtitle("c) Spring") +
-  theme_classic() +
-  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
-        legend.position = "none",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
-        plot.title = element_text(size = 16, face = "bold"))
-```
-
-### Fall
-
-```{r}
-load(file = "./ModelSaves/FallCamp_Length.RData")
-
-data <- fishy_dat
-uni_names <- unique(data$names)
-dat_names <- c("Index", uni_names)
-
-new_list <- list()
-for(i in 1:length(uni_names)){
-  one_dex <- subset(data, names == uni_names[i])
-  new_list[[i]] <- aggregate(one_dex$pa, by = list(one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  new_list)
-
-# Confidence intervals
-low_rho = sdrep$value[names(sdrep$value) == "iye"] - qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
-high_rho = sdrep$value[names(sdrep$value) == "iye"] + qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
-ts_df <- data.frame(ts = rep$iye, year = multi_inner[,1], low_sd = low_rho, high_sd = high_rho) %>% mutate(acc_year = multi_inner[,1]+1)
-
-p4 <- ggplot() +
-  geom_ribbon(data = ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_point(data = ts_df, aes(x = acc_year, y = ts, colour = "all")) +
-  geom_line(data = ts_df, aes(x = acc_year, y = ts, colour = "all" ), size = 1.5) +
-
-  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1995,2022), breaks = c(seq(1995, 2022, 5))) + 
-  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.45, 1.08)) +
-  scale_color_manual(name = "Species Model", values = c(all = "black", ac = "#BC8DA0", gh = "#048BA8"),
-                     labels = c(all = "All species", ac = "Cod/ Plaice", gh = "Greenland halibut")) +
-  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
-  ggtitle("e) Fall") +
-  theme_classic() +
-  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
-        legend.position = "none",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
-        plot.title = element_text(size = 16, face = "bold"))
-```
-
-## Engel
-
-### Spring
-
-```{r}
-load(file = "./ModelSaves/ACAP-SprEng_Length.RData")
-load(file = "./ModelSaves/GH-SprEng_Length.RData")
-
-# Set up index df - GH
-gh_data <- gh_fishy_dat
-gh_uni_names <- unique(gh_data$names)
-gh_dat_names <- c("Index", gh_uni_names)
-
-gh_new_list <- list()
-for(i in 1:length(gh_uni_names)){
-  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
-  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-gh_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  gh_new_list
-)
-
-# Set up index df - AC
-ac_data <- ac_fishy_dat
-ac_uni_names <- unique(ac_data$names)
-ac_dat_names <- c("Index", ac_uni_names)
-
-ac_new_list <- list()
-for(i in 1:length(ac_uni_names)){
-  ac_one_dex <- subset(ac_data, names == ac_uni_names[i])
-  ac_new_list[[i]] <- aggregate(ac_one_dex$pa, by = list(ac_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-ac_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  ac_new_list
-)
-
-gh_low_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] - qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
-gh_high_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] + qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
-gh_ts_df <- data.frame(ts = gh_rep$iye, time = gh_multi_inner[,1], low_sd = gh_low_rho, high_sd = gh_high_rho)
-
-ac_low_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] - qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
-ac_high_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] + qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
-ac_ts_df <- data.frame(ts = ac_rep$iye, time = ac_multi_inner[,1], low_sd = ac_low_rho, high_sd = ac_high_rho)
-
-p5 <- ggplot() +
-  geom_line(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
-  geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
-
-  geom_line(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
-  geom_point(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
-
-  geom_ribbon(data = gh_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
-  geom_point(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
-
-  geom_ribbon(data = ac_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = ac_ts_df, aes(x = time, y = ts, colour = "ac"), size = 1.5) +
-  geom_point(data = ac_ts_df, aes(x = time, y = ts, colour = "ac"), size = 1.5) +
-
-  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1981,1995), breaks = c(seq(1981, 1995, 3))) + 
-  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.3,2.0)) +
-  scale_color_manual(name = "Species Model", values = c(all = "black", surv = "#BB2D05", ac = "#BC8DA0", gh = "#048BA8"),
-                     labels = c(all = "All species", surv = "Acoustic survey", ac = "Cod/ Plaice", gh = "Greenland halibut")) +
-  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
-  ggtitle("c) Spring") +
-  theme_classic() +
-  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
-        legend.position = "none",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
-        plot.title = element_text(size = 16, face = "bold"))
-```
-
-### Fall
-
-```{r}
-load(file = "./ModelSaves/ACAP-FallEng_Length.RData")
-load(file = "./ModelSaves/GH-FallEng_Length.RData")
-
-# Set up index df - GH
-gh_data <- gh_fishy_dat
-gh_uni_names <- unique(gh_data$names)
-gh_dat_names <- c("Index", gh_uni_names)
-
-gh_new_list <- list()
-for(i in 1:length(gh_uni_names)){
-  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
-  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-gh_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  gh_new_list
-)
-
-# Set up index df - AC
-ac_data <- ac_fishy_dat
-ac_uni_names <- unique(ac_data$names)
-ac_dat_names <- c("Index", ac_uni_names)
-
-ac_new_list <- list()
-for(i in 1:length(ac_uni_names)){
-  ac_one_dex <- subset(ac_data, names == ac_uni_names[i])
-  ac_new_list[[i]] <- aggregate(ac_one_dex$pa, by = list(ac_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-ac_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  ac_new_list
-)
-
-gh_low_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] - qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
-gh_high_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] + qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
-gh_ts_df <- data.frame(ts = gh_rep$iye, time = gh_multi_inner[,1], low_sd = gh_low_rho, high_sd = gh_high_rho) %>% 
-  mutate(acc_year = gh_multi_inner[,1]+1)
-
-ac_low_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] - qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
-ac_high_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] + qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
-ac_ts_df <- data.frame(ts = ac_rep$iye, time = ac_multi_inner[,1], low_sd = ac_low_rho, high_sd = ac_high_rho) %>% 
-  mutate(acc_year = ac_multi_inner[,1]+1)
-
-p6 <- ggplot() +
-  geom_line(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
-  geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
-
-  geom_line(aes(x = 0, y = 0, colour = "ap"), size = 1.5) +
-  geom_point(aes(x = 0, y = 0, colour = "ap"), size = 1.5) +
-
-  geom_ribbon(data = gh_ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = gh_ts_df, aes(x = acc_year, y = ts, colour = "gh"), size = 1.5) +
-  geom_point(data = gh_ts_df, aes(x = acc_year, y = ts, colour = "gh"), size = 1.5) +
-
-  geom_ribbon(data = ac_ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = ac_ts_df, aes(x = acc_year, y = ts, colour = "ac"), size = 1.5) +
-  geom_point(data = ac_ts_df, aes(x = acc_year, y = ts, colour = "ac"), size = 1.5) +
-
-  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1981,1995), breaks = c(seq(1981, 1995, 3))) + 
-  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.21,0.75)) +
-  scale_color_manual(name = "Species Model", values = c(all = "black", ac = "#BC8DA0", gh = "#048BA8", ap = "#FF7733"),
-                     labels = c(all = "All species", ac = "Cod/ Plaice", gh = "Greenland halibut", ap = "American plaice")) +
-  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
-  ggtitle("f) Fall") +
-  theme_classic() +
-  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
-        legend.position = "none",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
-        plot.title = element_text(size = 16, face = "bold"))
-```
-
-## - Figure 2
-
-```{r, fig.width = 16, fig.height=13}
-
-p7 <- ggarrange(p1+theme(axis.title.x = element_blank()),
-          p2+theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
-          p3+theme(),
-          p5+theme(axis.title.y = element_blank()),
-          p4,
-          p6+theme(axis.title.y = element_blank()),
-          nrow = 3, ncol = 2,
-          align = "v", legend = "right", legend.grob = ggpubr::get_legend(p6+theme(legend.position = "right")))
-
-ggsave(filename = "abundancefull.tiff", device = "tiff", plot = p7, path = "./Figures",
-       dpi = 300, width = 16, height = 13, units = "in")
-```
-
-# Survey Comparison
-
-## Campelen
-
-### Fall
+# Fall
 
@@
 
-p8 <- ggplot(data = lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
+fit_cooks <- cooks.distance(fit)
+df <- data.frame(obs = names(fit_cooks),
+                 cooks = fit_cooks)
+ggplot(df, aes(y = cooks, x = obs)) +
+  geom_point() +
+  geom_hline(yintercept = 0.5, linetype = "dashed") +
+  labs(title = "Cook's Distance", x = "Observation Number", y = "Cook's")
 
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
-  ggtitle("Campelen\na) Fall 2J3KL All Speices") +
-  theme_classic() +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-    legend.position = "none",
-    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
-    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
+lr_dat[which(abs(fit_cooks) > 0.5),]
+
+cor.test(x = c(lr_dat$NLFPM_bm[1:18],lr_dat$NLFPM_bm[20:23]), y = c(lr_dat$acc_bm[1:18],lr_dat$acc_bm[20:23]), method = "pearson")
 
@@
 
-### Spring
+# Spring
 
@@
 
-p9 <- ggplot(data = ap_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
+fit_cooks <- cooks.distance(fit)
+df <- data.frame(obs = names(fit_cooks),
+                 cooks = fit_cooks)
+ggplot(df, aes(y = cooks, x = obs)) +
+  geom_point() +
+  geom_hline(yintercept = 0.5, linetype = "dashed") +
+  labs(title = "Cook's Distance", x = "Observation Number", y = "Cook's")
 
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
-  ggtitle(" \nb) Spring 3L Plaice") +
-  theme_classic() +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-    legend.position = 'none',
-    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
-    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
+ap_lr_dat[which(abs(fit_cooks) > 0.5),] # No influence for AP
 
-# Set up relationship data frame - GH
+cor.test(x = ap_lr_dat$NLFPM_bm, y = ap_lr_dat$acc_bm, method = "pearson")
+
 gh_lr_dat <- data.frame(year = acc_surv[2:25,1], acc_bm = acc_surv[2:25,2], NLFPM_bm = gh_rep$iye)
@@
 
-p10 <- ggplot(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
+fit_cooks <- cooks.distance(fit)
+df <- data.frame(obs = names(fit_cooks),
+                 cooks = fit_cooks)
+ggplot(df, aes(y = cooks, x = obs)) +
+  geom_point() +
+  geom_hline(yintercept = 0.5, linetype = "dashed") +
+  labs(title = "Cook's Distance", x = "Observation Number", y = "Cook's")
 
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
-  theme_classic() +
-  ggtitle(" \nc) Spring 3L Halibut") +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-        legend.position = 'none',
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
-        axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
+gh_lr_dat[which(abs(fit_cooks) > 0.5),] # No influence for GH
 
@@
 
-### Fall
+# Fall
 
@@
 
-p11 <- ggplot(data = ac_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
+fit_cooks <- cooks.distance(fit)
+df <- data.frame(obs = names(fit_cooks),
+                 cooks = fit_cooks)
+ggplot(df, aes(y = cooks, x = obs)) +
+  geom_point() +
+  geom_hline(yintercept = 0.5, linetype = "dashed") +
+  labs(title = "Cook's Distance", x = "Observation Number", y = "Cook's")
 
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1981,1995), midpoint = 1987,  low = "blue", mid = "#FFAEFF", high = "red") +
-  ggtitle("Engel\nd) Fall 2J3KL Cod/Plaice") +
-  theme_classic() +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-    legend.position = 'none',
-    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
-    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
+ac_lr_dat[which(abs(fit_cooks) > 0.5),] # No influence for AC
 
@@
 
-p12 <- ggplot(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
+fit_cooks <- cooks.distance(fit)
+df <- data.frame(obs = names(fit_cooks),
+                 cooks = fit_cooks)
+ggplot(df, aes(y = cooks, x = obs)) +
+  geom_point() +
+  geom_hline(yintercept = 0.5, linetype = "dashed") +
+  labs(title = "Cook's Distance", x = "Observation Number", y = "Cook's")
 
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1981,1995), midpoint = 1987,  low = "blue", mid = "#FFAEFF", high = "red") +
-  theme_classic() +
-  ggtitle(" \ne) Fall 2J3KL Halibut") +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-    legend.position = 'none',
-    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
-    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
+gh_lr_dat[which(abs(fit_cooks) > 0.5),] # No influence for GH
 
@@
 
-p13 <- ggplot(data = ac_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
+fit_cooks <- cooks.distance(fit)
+df <- data.frame(obs = names(fit_cooks),
+                 cooks = fit_cooks)
+ggplot(df, aes(y = cooks, x = obs)) +
+  geom_point() +
+  geom_hline(yintercept = 0.5, linetype = "dashed") +
+  labs(title = "Cook's Distance", x = "Observation Number", y = "Cook's")
 
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
-  ggtitle("\nf) Spring 2J3KL Cod/Plaice") +
-  theme_classic() +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-    legend.position = 'none',
-    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
-    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
+ac_lr_dat[which(abs(fit_cooks) > 0.5),] # 1988 influence
+
+cor.test(x = c(ac_lr_dat$NLFPM_bm[1:3],ac_lr_dat$NLFPM_bm[5:8]), y = c(ac_lr_dat$acc_bm[1:3],ac_lr_dat$acc_bm[5:8]), method = "pearson")
 
@@
 
-p14 <- ggplot(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
+fit_cooks <- cooks.distance(fit)
+df <- data.frame(obs = names(fit_cooks),
+                 cooks = fit_cooks)
+ggplot(df, aes(y = cooks, x = obs)) +
+  geom_point() +
+  geom_hline(yintercept = 0.5, linetype = "dashed") +
+  labs(title = "Cook's Distance", x = "Observation Number", y = "Cook's")
 
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
-  theme_classic() +
-  ggtitle(" \ng) Spring 2J3KL Halibut") +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-    legend.position = 'none',
-    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
-    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
+gh_lr_dat[which(abs(fit_cooks) > 0.5),] # 1988 influence
+
+cor.test(x = c(gh_lr_dat$NLFPM_bm[1:3],gh_lr_dat$NLFPM_bm[5:8]), y = c(gh_lr_dat$acc_bm[1:3],gh_lr_dat$acc_bm[5:8]), method = "pearson")
+
 ```
 
-## - Figure 3
-
-```{r, fig.width=14, fig.height=8}
-p0 <- ggplot() +
-  geom_point(aes(x = 0, y = 0, colour = "white"), size = 1.5)+
-  scale_x_continuous(limits = c(0.1,1))+
-  theme_classic()
-
-p15 <- ggarrange(p8+theme(axis.title.x = element_blank()),
-          p9+theme(axis.title.x = element_blank(),axis.title.y = element_blank()),
-          p10+theme(axis.title.x = element_blank(),axis.title.y = element_blank()),
-          p0+theme(text = element_blank(), title = element_blank(), line = element_blank()),
-          nrow = 1, ncol = 4,
-          align = "v", legend = "right", common.legend = T)
-
-p16 <- ggarrange(p11,
-          p12+theme(axis.title.y = element_blank()),
-          p13+theme(axis.title.y = element_blank()),
-          p14+theme(axis.title.y = element_blank()),
-          nrow = 1, ncol = 4,
-          align = "hv", legend = "right", common.legend = T)
-
-p17 <- ggarrange(p15,p16,
-          nrow = 2, ncol = 1, align = "h")
-
-ggsave(filename = "survcomp.tiff", device = "tiff", plot = p17, path = "./Figures",
-       dpi = 300, width = 16, height = 8, units = "in")
-```
-
-# Spatial Comparison
-
-## Fall 2J3KL
+# Spatial
 
@@
 
-car::influencePlot.lm(fit)
+fit_cooks <- cooks.distance(fit)
+df <- data.frame(obs = names(fit_cooks),
+                 cooks = fit_cooks)
+ggplot(df, aes(y = cooks, x = obs)) +
+  geom_point() +
+  geom_hline(yintercept = 0.5, linetype = "dashed") +
+  labs(title = "Cook's Distance", x = "Observation Number", y = "Cook's")
+
+lr_dat[which(abs(fit_cooks) > 0.5),] # 1996 influence
+
+cor.test(x = c(gh_lr_dat$NLFPM_bm[1],gh_lr_dat$NLFPM_bm[3:26]), y = c(gh_lr_dat$acc_bm[1],gh_lr_dat$acc_bm[3:26]), method = "pearson")
 
 ```
-
-## - Figure 4
-
-```{r}
-p18 <- ggplot(data = lr_dat, aes(x = l_NLFPM_bm, y = jkl_NLFPM_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
-
-  scale_x_continuous(name = "3L NLFPM Abundance Index", expand = c(0.005,0)) +
-  scale_y_continuous(name = "2J3KL NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_colour_gradient2(name = "Year", limits = c(1995,2021), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
-  theme_classic() +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-        legend.position = 'right', legend.direction = "vertical",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
-        axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"))
-
-ggsave(filename = "spatialcomp.tiff", device = "tiff", plot = p18, path = "./Figures",
-       dpi = 300, width = 5, height = 4.5, units = "in")
-```

### 2024-10-30 PaperSections.Rmd
October 30, before committee meeting

@@
 library(tidyverse)
+library(cowplot)
 library(ggpubr)
-library(cowplot)
 ```
@@
 ## Acoustic
+
+### Engel
+
+```{r}
+acc_surv <- read.csv("./Data/Capelin_AccSurv.csv") %>% 
+  filter(Year > 1980 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)
+
+## Survey year proper
+p1 <- ggplot(data = acc_surv) +
+  geom_line(aes(x = Year, y = acsurv_bm), colour = "#BB2D05", linewidth = 1) +
+  geom_point(aes(x = Year, y = acsurv_bm), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
+  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1981,1995.1), breaks = c(seq(1981,1995, 3))) + 
+  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.009,0), limits = c(0,6000)) +
+  ggtitle("Engel\na) Spring") +
+  theme_classic() +
+  theme(legend.position = "none",
+        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
+        axis.line.x = element_line(size = 0.7), axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"), 
+        plot.title = element_text(size = 16, face = "bold"))
+```
 
@@
 ## Survey year proper
-p1 <- ggplot(data = acc_surv) +
+p2 <- ggplot(data = acc_surv) +
   geom_line(aes(x = Year, y = acsurv_bm), colour = "#BB2D05", linewidth = 1) +
@@
   scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.009,0), limits = c(0, 1100)) +
-  ggtitle("Campelen\na) Spring") +
+  ggtitle("Campelen\nb) Spring") +
   theme_classic() +
@@
         axis.line.x = element_line(size = 0.7), axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"), 
-        plot.title = element_text(size = 16, face = "bold"))
-```
-
-### Engel
-
-```{r}
-acc_surv <- read.csv("./Data/Capelin_AccSurv.csv") %>% 
-  filter(Year > 1980 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)
-
-## Survey year proper
-p2 <- ggplot(data = acc_surv) +
-  geom_line(aes(x = Year, y = acsurv_bm), colour = "#BB2D05", linewidth = 1) +
-  geom_point(aes(x = Year, y = acsurv_bm), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
-  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1981,1995.1), breaks = c(seq(1981,1995, 3))) + 
-  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.009,0), limits = c(0,6000)) +
-  ggtitle("Engel\nb) Spring") +
-  theme_classic() +
-  theme(legend.position = "none",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.line.x = element_line(size = 0.7), axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"), 
-        plot.title = element_text(size = 16, face = "bold"))
-```
-
-## Campelen
-
-### Spring
-
-```{r}
-load(file = "./ModelSaves/AP-SprCamp_Length.RData")
-load(file = "./ModelSaves/GH-SprCamp_Length.RData")
-
-# Set up index df - GH
-gh_data <- gh_fishy_dat
-gh_uni_names <- unique(gh_data$names)
-gh_dat_names <- c("Index", gh_uni_names)
-
-gh_new_list <- list()
-for(i in 1:length(gh_uni_names)){
-  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
-  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-gh_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  gh_new_list
-)
-
-# Set up index df - AC
-ap_data <- ap_fishy_dat
-ap_uni_names <- unique(ap_data$names)
-ap_dat_names <- c("Index", ap_uni_names)
-
-ap_new_list <- list()
-for(i in 1:length(ap_uni_names)){
-  ap_one_dex <- subset(ap_data, names == ap_uni_names[i])
-  ap_new_list[[i]] <- aggregate(ap_one_dex$pa, by = list(ap_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-ap_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  ap_new_list
-)
-
-gh_low_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] - qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
-gh_high_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] + qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
-gh_ts_df <- data.frame(ts = gh_rep$iye, time = gh_multi_inner[,1], low_sd = gh_low_rho, high_sd = gh_high_rho)
-
-ap_low_rho = ap_sdrep$value[names(ap_sdrep$value) == "iye"] - qnorm(0.975)*ap_sdrep$sd[names(ap_sdrep$value) == "iye"]
-ap_high_rho = ap_sdrep$value[names(ap_sdrep$value) == "iye"] + qnorm(0.975)*ap_sdrep$sd[names(ap_sdrep$value) == "iye"]
-ap_ts_df <- data.frame(ts = ap_rep$iye, time = ap_multi_inner[,1], low_sd = ap_low_rho, high_sd = ap_high_rho)
-
-p3 <- ggplot() +
-  geom_line(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
-  geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
-
-  geom_line(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
-  geom_point(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
-
-  geom_ribbon(data = gh_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
-  geom_point(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
-
-  geom_ribbon(data = ap_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = ap_ts_df, aes(x = time, y = ts, colour = "ap"), size = 1.5) +
-  geom_point(data = ap_ts_df, aes(x = time, y = ts, colour = "ap"), size = 1.5) +
-
-  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1995,2021), breaks = c(seq(1995, 2021, 5))) + 
-  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.6,2.4)) +
-  scale_color_manual(name = "Species Model", values = c(all = "black", surv = "#BB2D05", ap = "#FF7733", gh = "#048BA8"),
-                     labels = c(all = "All species", surv = "Acoustic survey", ap = "Plaice", gh = "Greenland halibut")) +
-  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
-  ggtitle("c) Spring") +
-  theme_classic() +
-  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
-        legend.position = "none",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
-        plot.title = element_text(size = 16, face = "bold"))
-```
-
-### Fall
-
-```{r}
-load(file = "./ModelSaves/FallCamp_Length.RData")
-
-data <- fishy_dat
-uni_names <- unique(data$names)
-dat_names <- c("Index", uni_names)
-
-new_list <- list()
-for(i in 1:length(uni_names)){
-  one_dex <- subset(data, names == uni_names[i])
-  new_list[[i]] <- aggregate(one_dex$pa, by = list(one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  new_list)
-
-# Confidence intervals
-low_rho = sdrep$value[names(sdrep$value) == "iye"] - qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
-high_rho = sdrep$value[names(sdrep$value) == "iye"] + qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
-ts_df <- data.frame(ts = rep$iye, year = multi_inner[,1], low_sd = low_rho, high_sd = high_rho) %>% mutate(acc_year = multi_inner[,1]+1)
-
-p4 <- ggplot() +
-  geom_ribbon(data = ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_point(data = ts_df, aes(x = acc_year, y = ts, colour = "all")) +
-  geom_line(data = ts_df, aes(x = acc_year, y = ts, colour = "all" ), size = 1.5) +
-
-  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1995,2022), breaks = c(seq(1995, 2022, 5))) + 
-  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.45, 1.08)) +
-  scale_color_manual(name = "Species Model", values = c(all = "black", ac = "#BC8DA0", gh = "#048BA8"),
-                     labels = c(all = "All species", ac = "Cod/ Plaice", gh = "Greenland halibut")) +
-  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
-  ggtitle("e) Fall") +
-  theme_classic() +
-  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
-        legend.position = "none",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
         plot.title = element_text(size = 16, face = "bold"))
@@
 
-p5 <- ggplot() +
-  geom_line(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
-  geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
-
-  geom_line(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
-  geom_point(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
+p3 <- ggplot() +
 
@@
   scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.3,2.0)) +
-  scale_color_manual(name = "Species Model", values = c(all = "black", surv = "#BB2D05", ac = "#BC8DA0", gh = "#048BA8"),
-                     labels = c(all = "All species", surv = "Acoustic survey", ac = "Cod/ Plaice", gh = "Greenland halibut")) +
+  scale_color_manual(name = "Species Model", values = c(ac = "#BC8DA0", gh = "#048BA8"),
+                     labels = c(ac = "Cod/ Plaice", gh = "Greenland halibut")) +
   guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
@@
 
-p6 <- ggplot() +
-  geom_line(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
-  geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
-
-  geom_line(aes(x = 0, y = 0, colour = "ap"), size = 1.5) +
-  geom_point(aes(x = 0, y = 0, colour = "ap"), size = 1.5) +
+p4 <- ggplot() +
 
@@
   scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.21,0.75)) +
-  scale_color_manual(name = "Species Model", values = c(all = "black", ac = "#BC8DA0", gh = "#048BA8", ap = "#FF7733"),
-                     labels = c(all = "All species", ac = "Cod/ Plaice", gh = "Greenland halibut", ap = "American plaice")) +
+  scale_color_manual(name = "Species Model", 
+                     values = c(ac = "#BC8DA0", gh = "#048BA8"),
+                     labels = c(ac = "Cod/ Plaice", gh = "Greenland halibut")) +
+  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
+  ggtitle("e) Fall") +
+  theme_classic() +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
+        legend.position = "none",
+        legend.text = element_text(size = 11), legend.title = element_text(size = 16, face = "bold"), legend.spacing.x = unit(0,'cm'),
+        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
+        plot.title = element_text(size = 16, face = "bold"))
+```
+
+## Campelen
+
+### Spring
+
+```{r}
+load(file = "./ModelSaves/AP-SprCamp_Length.RData")
+load(file = "./ModelSaves/GH-SprCamp_Length.RData")
+
+# Set up index df - GH
+gh_data <- gh_fishy_dat
+gh_uni_names <- unique(gh_data$names)
+gh_dat_names <- c("Index", gh_uni_names)
+
+gh_new_list <- list()
+for(i in 1:length(gh_uni_names)){
+  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
+  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
+}
+
+gh_multi_inner <- Reduce(
+  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
+  gh_new_list
+)
+
+# Set up index df - AC
+ap_data <- ap_fishy_dat
+ap_uni_names <- unique(ap_data$names)
+ap_dat_names <- c("Index", ap_uni_names)
+
+ap_new_list <- list()
+for(i in 1:length(ap_uni_names)){
+  ap_one_dex <- subset(ap_data, names == ap_uni_names[i])
+  ap_new_list[[i]] <- aggregate(ap_one_dex$pa, by = list(ap_one_dex$year), FUN = mean, na.rm = TRUE)
+}
+
+ap_multi_inner <- Reduce(
+  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
+  ap_new_list
+)
+
+gh_low_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] - qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
+gh_high_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] + qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
+gh_ts_df <- data.frame(ts = gh_rep$iye, time = gh_multi_inner[,1], low_sd = gh_low_rho, high_sd = gh_high_rho)
+
+ap_low_rho = ap_sdrep$value[names(ap_sdrep$value) == "iye"] - qnorm(0.975)*ap_sdrep$sd[names(ap_sdrep$value) == "iye"]
+ap_high_rho = ap_sdrep$value[names(ap_sdrep$value) == "iye"] + qnorm(0.975)*ap_sdrep$sd[names(ap_sdrep$value) == "iye"]
+ap_ts_df <- data.frame(ts = ap_rep$iye, time = ap_multi_inner[,1], low_sd = ap_low_rho, high_sd = ap_high_rho)
+
+p5 <- ggplot() +
+  geom_line(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
+  geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
+
+  geom_line(aes(x = 0, y = 0, colour = "ac"), size = 1.5) +
+  geom_point(aes(x = 0, y = 0, colour = "ac"), size = 1.5) +
+
+  geom_line(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
+  geom_point(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
+
+  geom_ribbon(data = gh_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
+  geom_line(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
+  geom_point(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
+
+  geom_ribbon(data = ap_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
+  geom_line(data = ap_ts_df, aes(x = time, y = ts, colour = "ap"), size = 1.5) +
+  geom_point(data = ap_ts_df, aes(x = time, y = ts, colour = "ap"), size = 1.5) +
+
+  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1995,2021), breaks = c(seq(1995, 2021, 5))) + 
+  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.6,2.4)) +
+  scale_color_manual(name = "Species Model",
+                     breaks = c("all", "surv", "ac", "gh", "ap"), 
+                     values = c(all = "black", surv = "#BB2D05", ac = "#BC8DA0", gh = "#048BA8", ap = "#FF7733"),
+                     labels = c(all = "All species", surv = "Acoustic survey", ac = "Cod/ Plaice", gh = "Greenland halibut", ap = "American plaice")) +
+  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
+  ggtitle("d) Spring") +
+  theme_classic() +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
+        # legend.position = "none",
+        legend.text = element_text(size = 13), legend.title = element_text(size = 15, face = "bold"), legend.spacing.x = unit(0,'cm'),
+        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
+        plot.title = element_text(size = 16, face = "bold"))
+```
+
+### Fall
+
+```{r}
+load(file = "./ModelSaves/FallCamp_Length.RData")
+
+data <- fishy_dat
+uni_names <- unique(data$names)
+dat_names <- c("Index", uni_names)
+
+new_list <- list()
+for(i in 1:length(uni_names)){
+  one_dex <- subset(data, names == uni_names[i])
+  new_list[[i]] <- aggregate(one_dex$pa, by = list(one_dex$year), FUN = mean, na.rm = TRUE)
+}
+
+multi_inner <- Reduce(
+  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
+  new_list)
+
+# Confidence intervals
+low_rho = sdrep$value[names(sdrep$value) == "iye"] - qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
+high_rho = sdrep$value[names(sdrep$value) == "iye"] + qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
+ts_df <- data.frame(ts = rep$iye, year = multi_inner[,1], low_sd = low_rho, high_sd = high_rho) %>% mutate(acc_year = multi_inner[,1]+1)
+
+p6 <- ggplot() +
+  geom_ribbon(data = ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
+  geom_point(data = ts_df, aes(x = acc_year, y = ts, colour = "all")) +
+  geom_line(data = ts_df, aes(x = acc_year, y = ts, colour = "all" ), size = 1.5) +
+
+  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1995,2022), breaks = c(seq(1995, 2022, 5))) + 
+  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.45, 1.08)) +
+  scale_color_manual(name = "Species Model", values = c(all = "black"),
+                     labels = c(all = "All species")) +
   guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
@@
                 p2+theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
-          p3+theme(),
+                p3,
                 p5+theme(axis.title.y = element_blank()),
@@
                 nrow = 3, ncol = 2,
-          align = "v", legend = "right", legend.grob = ggpubr::get_legend(p6+theme(legend.position = "right")))
+                align = "v", common.legend = TRUE,
+                legend = "right", legend.grob = ggpubr::get_legend(p5+theme(legend.position = "right")))
 
@@
 cor.test(x = lr_dat$NLFPM_bm, y = lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated 
-
 lr_dat <- na.omit(lr_dat)
@@
     legend.position = "none",
-    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
+    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
     axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
@@
     legend.position = 'none',
-    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
+    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
     axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
@@
         legend.position = 'none',
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
+        legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
         axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
@@
 p17 <- ggarrange(p15,p16,
-          nrow = 2, ncol = 1, align = "h")
+          nrow = 2, ncol = 1, align = "v")
 
@@
 
-car::influencePlot.lm(fit)
-
 ```

### 2024-11-04 PaperSections.Rmd
Changes from committee meeting - Nov 1

@@
   scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
-  ggtitle("\nf) Spring 2J3KL Cod/Plaice") +
+  ggtitle("\nf) Spring 3L Cod/Plaice") +
   theme_classic() +
@@
   theme_classic() +
-  ggtitle(" \ng) Spring 2J3KL Halibut") +
+  ggtitle(" \ng) Spring 3L Halibut") +
   theme(
@@
 ```
-
-# Spatial Comparison
-
-## Fall 2J3KL
-
-```{r}
-load(file = "./ModelSaves/FallCamp_Length.RData")
-
-# Set up relationship data frame
-lr_dat <- data.frame(year = unique(fishy_dat$year)[1:26], jkl_NLFPM_bm = rep$iye[1:26])
-
-load(file = "./ModelSaves/3LFallCamp_Length.RData")
-
-lr_dat$l_NLFPM_bm <- rep$iye
-
-# Linear relationship 
-fit <- lm(jkl_NLFPM_bm~l_NLFPM_bm, data = lr_dat)
-cor.test(x = lr_dat$jkl_NLFPM_bm, y = lr_dat$l_NLFPM_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated
-
-```
-
-## - Figure 4
-
-```{r}
-p18 <- ggplot(data = lr_dat, aes(x = l_NLFPM_bm, y = jkl_NLFPM_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
-
-  scale_x_continuous(name = "3L NLFPM Abundance Index", expand = c(0.005,0)) +
-  scale_y_continuous(name = "2J3KL NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_colour_gradient2(name = "Year", limits = c(1995,2021), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
-  theme_classic() +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-        legend.position = 'right', legend.direction = "vertical",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
-        axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"))
-
-ggsave(filename = "spatialcomp.tiff", device = "tiff", plot = p18, path = "./Figures",
-       dpi = 300, width = 5, height = 4.5, units = "in")
-```

### 2024-11-08 Analysis/AR1.Rmd
Addressed committee meeting comments - 08/11/2024

---
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
library(tidyverse)
library(glmmTMB)
library(ggeffects)
```

# AR1

## Campelen

### Fall

```{r}
load(file = "./ModelSaves/FallCamp_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1994) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

lr_dat <- data.frame(year = as.factor(acc_surv[2:28,1]), acc_bm = acc_surv[2:28,2], NLFPM_bm = rep$iye, dummy = as.factor(0))

fcar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = lr_dat)

summary(fcar)

plot(ggpredict(fcar, terms = c("NLFPM_bm")))+
  geom_point(data = lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(lr_dat$acc_bm~lr_dat$NLFPM_bm)

```
Fall Campelen NLFPM correlation to acoustic - not significant positive relationship (Corr = 0.45, p = 0.0811)

### Spring

```{r}
load(file = "./ModelSaves/AP-SprCamp_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1994) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

ap_lr_dat <- data.frame(year = as.factor(acc_surv[2:25,1]), acc_bm = acc_surv[2:25,2], NLFPM_bm = ap_rep$iye, dummy = as.factor(0))

# # Influential points
# ap_lr_dat <- data.frame(year = c(acc_surv[2:18,1], acc_surv[21:25,1]), acc_bm = c(acc_surv[2:18,2], acc_surv[21:25,2]), 
#                         NLFPM_bm = c(ap_rep$iye[2:18],ap_rep$iye[21:25]))

scapar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = ap_lr_dat)

summary(scapar)

plot(ggpredict(scapar, terms = c("NLFPM_bm")))+
  geom_point(data = ap_lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(ap_lr_dat$acc_bm~ap_lr_dat$NLFPM_bm)

```
Spring Campelen AP NLFPM correlation to acoustic - not significant positive relationship (Corr = 0.54, p = 0.673)

```{r}
load(file = "./ModelSaves/GH-SprCamp_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1994) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:25,1]), acc_bm = acc_surv[2:25,2], NLFPM_bm = gh_rep$iye, dummy = as.factor(0))

# gh_lr_dat <- data.frame(year = c(acc_surv[2:18,1], acc_surv[21:25,1]), acc_bm = c(acc_surv[2:18,2], acc_surv[21:25,2]), 
#                         NLFPM_bm = c(gh_rep$iye[2:18],gh_rep$iye[21:25]))

scghar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = gh_lr_dat)

summary(scghar)

plot(ggpredict(scghar, terms = c("NLFPM_bm")))+
  geom_point(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(gh_lr_dat$acc_bm~gh_lr_dat$NLFPM_bm)

```
Spring Campelen GH NLFPM correlation to acoustic - No convergence

## Engel

### Fall
```{r}
load(file = "./ModelSaves/ACAP-FallEng_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1980 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

# Set up relationship data frame - ACAP
ac_lr_dat <- data.frame(year = as.factor(acc_surv[2:15,1]), acc_bm = acc_surv[2:15,2], NLFPM_bm = ac_rep$iye, dummy = as.factor(0)) #have to y+1

feacar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = ac_lr_dat)

summary(feacar)

plot(ggpredict(feacar, terms = c("NLFPM_bm")))+
  geom_point(data = ac_lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(ac_lr_dat$acc_bm~ac_lr_dat$NLFPM_bm)

```
Fall Engel ACAP NLFPM correlation to acoustic - significant positive relationship (Corr = 0.02, p = 0.0376)

```{r}
load(file = "./ModelSaves/GH-FallEng_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1980 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:15,1]), acc_bm = acc_surv[2:15,2], NLFPM_bm = gh_rep$iye, dummy = as.factor(0))

feghar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = gh_lr_dat)

summary(feghar)

plot(ggpredict(feghar, terms = c("NLFPM_bm")))+
  geom_point(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(gh_lr_dat$acc_bm~gh_lr_dat$NLFPM_bm)

```
Fall Engel GH NLFPM correlation to acoustic - No converge

### Spring

```{r}
load(file = "./ModelSaves/ACAP-SprEng_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1983 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

ac_lr_dat <- data.frame(year = as.factor(acc_surv[2:13,1]), acc_bm = acc_surv[2:13,2], NLFPM_bm = c(ac_rep$iye[12], ac_rep$iye[1:11]), dummy = as.factor(0)) #have to y+1

seacar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = ac_lr_dat)

summary(seacar)

plot(ggpredict(seacar, terms = c("NLFPM_bm")))+
  geom_point(data = ac_lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(ac_lr_dat$acc_bm~ac_lr_dat$NLFPM_bm)

```
Spring Engel ACAP NLFPM correlation to acoustic - no significant correlation (Corr = 0.03, p = 0.6177)

```{r}
load(file = "./ModelSaves/GH-SprEng_Length.RData")
acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
  filter(Year > 1983 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)

gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:13,1]), acc_bm = acc_surv[2:13,2], NLFPM_bm = c(gh_rep$iye[12], gh_rep$iye[1:11]), dummy = as.factor(0))

seghar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = gh_lr_dat)

summary(seghar)

plot(ggpredict(seghar, terms = c("NLFPM_bm")))+
  geom_point(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm))

plot(gh_lr_dat$acc_bm~gh_lr_dat$NLFPM_bm)

```
Spring Engel ACAP NLFPM correlation to acoustic - no significant correlation (Corr = 0.09, p = 0.907)

### 2024-11-08 Analysis/Spearman.Rmd
Addressed committee meeting comments - 08/11/2024

--- 2024-11-08 Analysis/AR1.Rmd
@@
 
-lr_dat <- data.frame(year = as.factor(acc_surv[2:28,1]), acc_bm = acc_surv[2:28,2], NLFPM_bm = rep$iye, dummy = as.factor(0))
+lr_dat <- data.frame(year = as.factor(acc_surv[2:28,1]), acc_bm = acc_surv[2:28,2], NLFPM_bm = rep$iye)
 
-fcar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = lr_dat)
-
-summary(fcar)
-
-plot(ggpredict(fcar, terms = c("NLFPM_bm")))+
-  geom_point(data = lr_dat, aes(x = NLFPM_bm, y = acc_bm))
-
-plot(lr_dat$acc_bm~lr_dat$NLFPM_bm)
+cor.test(x = lr_dat$NLFPM_bm, y = lr_dat$acc_bm, method = "spearman")
 
 ```
-Fall Campelen NLFPM correlation to acoustic - not significant positive relationship (Corr = 0.45, p = 0.0811)
+Fall Campelen NLFPM correlation to acoustic - not significant positive relationship (rho = 0.4287, p = 0.05927)
 
@@
 
-ap_lr_dat <- data.frame(year = as.factor(acc_surv[2:25,1]), acc_bm = acc_surv[2:25,2], NLFPM_bm = ap_rep$iye, dummy = as.factor(0))
+ap_lr_dat <- data.frame(year = as.factor(acc_surv[2:25,1]), acc_bm = acc_surv[2:25,2], NLFPM_bm = ap_rep$iye)
 
@@
 
-scapar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = ap_lr_dat)
-
-summary(scapar)
-
-plot(ggpredict(scapar, terms = c("NLFPM_bm")))+
-  geom_point(data = ap_lr_dat, aes(x = NLFPM_bm, y = acc_bm))
-
-plot(ap_lr_dat$acc_bm~ap_lr_dat$NLFPM_bm)
+cor.test(x = ap_lr_dat$NLFPM_bm, y = ap_lr_dat$acc_bm, method = "spearman")
 
 ```
-Spring Campelen AP NLFPM correlation to acoustic - not significant positive relationship (Corr = 0.54, p = 0.673)
+Spring Campelen AP NLFPM correlation to acoustic - not significant negative relationship (Corr = -0.097, p = 0.684)
 
@@
 
-gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:25,1]), acc_bm = acc_surv[2:25,2], NLFPM_bm = gh_rep$iye, dummy = as.factor(0))
+gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:25,1]), acc_bm = acc_surv[2:25,2], NLFPM_bm = gh_rep$iye)
 
-# gh_lr_dat <- data.frame(year = c(acc_surv[2:18,1], acc_surv[21:25,1]), acc_bm = c(acc_surv[2:18,2], acc_surv[21:25,2]), 
-#                         NLFPM_bm = c(gh_rep$iye[2:18],gh_rep$iye[21:25]))
-
-scghar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = gh_lr_dat)
-
-summary(scghar)
-
-plot(ggpredict(scghar, terms = c("NLFPM_bm")))+
-  geom_point(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm))
-
-plot(gh_lr_dat$acc_bm~gh_lr_dat$NLFPM_bm)
+cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "spearman")
 
 ```
-Spring Campelen GH NLFPM correlation to acoustic - No convergence
+Spring Campelen GH NLFPM correlation to acoustic - not significant negative relationship (Corr = -0.3693, p = 0.109)
 
@@
 # Set up relationship data frame - ACAP
-ac_lr_dat <- data.frame(year = as.factor(acc_surv[2:15,1]), acc_bm = acc_surv[2:15,2], NLFPM_bm = ac_rep$iye, dummy = as.factor(0)) #have to y+1
+ac_lr_dat <- data.frame(year = as.factor(acc_surv[2:15,1]), acc_bm = acc_surv[2:15,2], NLFPM_bm = ac_rep$iye) #have to y+1
 
-feacar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = ac_lr_dat)
-
-summary(feacar)
-
-plot(ggpredict(feacar, terms = c("NLFPM_bm")))+
-  geom_point(data = ac_lr_dat, aes(x = NLFPM_bm, y = acc_bm))
-
-plot(ac_lr_dat$acc_bm~ac_lr_dat$NLFPM_bm)
+cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "spearman")
 
 ```
-Fall Engel ACAP NLFPM correlation to acoustic - significant positive relationship (Corr = 0.02, p = 0.0376)
+Fall Engel ACAP NLFPM correlation to acoustic - significant positive relationship (Corr = 0.5272, p = 0.1447)
 
@@
 
-gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:15,1]), acc_bm = acc_surv[2:15,2], NLFPM_bm = gh_rep$iye, dummy = as.factor(0))
+gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:15,1]), acc_bm = acc_surv[2:15,2], NLFPM_bm = gh_rep$iye)
 
-feghar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = gh_lr_dat)
-
-summary(feghar)
-
-plot(ggpredict(feghar, terms = c("NLFPM_bm")))+
-  geom_point(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm))
-
-plot(gh_lr_dat$acc_bm~gh_lr_dat$NLFPM_bm)
+cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "spearman")
 
 ```
-Fall Engel GH NLFPM correlation to acoustic - No converge
+Fall Engel GH NLFPM correlation to acoustic - significant positive relationship (rho = 0.6862, p = 0.04124)
 
@@
 
-ac_lr_dat <- data.frame(year = as.factor(acc_surv[2:13,1]), acc_bm = acc_surv[2:13,2], NLFPM_bm = c(ac_rep$iye[12], ac_rep$iye[1:11]), dummy = as.factor(0)) #have to y+1
+ac_lr_dat <- data.frame(year = as.factor(acc_surv[2:13,1]), acc_bm = acc_surv[2:13,2], NLFPM_bm = c(ac_rep$iye[12], ac_rep$iye[1:11])) #have to y+1
 
-seacar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = ac_lr_dat)
-
-summary(seacar)
-
-plot(ggpredict(seacar, terms = c("NLFPM_bm")))+
-  geom_point(data = ac_lr_dat, aes(x = NLFPM_bm, y = acc_bm))
-
-plot(ac_lr_dat$acc_bm~ac_lr_dat$NLFPM_bm)
+cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "spearman")
 
 ```
-Spring Engel ACAP NLFPM correlation to acoustic - no significant correlation (Corr = 0.03, p = 0.6177)
+Spring Engel ACAP NLFPM correlation to acoustic - no significant correlation (rho = 0.0838, p = 0.8435)
 
@@
 
-gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:13,1]), acc_bm = acc_surv[2:13,2], NLFPM_bm = c(gh_rep$iye[12], gh_rep$iye[1:11]), dummy = as.factor(0))
+gh_lr_dat <- data.frame(year = as.factor(acc_surv[2:13,1]), acc_bm = acc_surv[2:13,2], NLFPM_bm = c(gh_rep$iye[12], gh_rep$iye[1:11]))
 
-seghar <- glmmTMB(scale(acc_bm) ~ NLFPM_bm + ar1(year+0|dummy), data = gh_lr_dat)
-
-summary(seghar)
-
-plot(ggpredict(seghar, terms = c("NLFPM_bm")))+
-  geom_point(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm))
-
-plot(gh_lr_dat$acc_bm~gh_lr_dat$NLFPM_bm)
+cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "spearman")
 
 ```
-Spring Engel ACAP NLFPM correlation to acoustic - no significant correlation (Corr = 0.09, p = 0.907)
+Spring Engel ACAP NLFPM correlation to acoustic - no significant correlation (rho = 0.1198, p = 0.7776)

### 2024-11-08 Analysis/Campelen/Fall/FallCamp-SetUp.R

@@ -3,6 +3,10 @@ library(tidyverse)
 library(TMB)
 dyn.load("./TMBcode/SclNLFPM")
 
+# dyn.unload("./TMBcode/monoTempNLFPM")
+# compile("./TMBcode/monoTempNLFPM.cpp")
+dyn.load("./TMBcode/monoTempNLFPM")
+
 # load rstrap set data
 load(file = "./Data/setdet.rda") 
 setdet <- setdet %>% mutate(v.t.s = paste(vessel,trip,set, sep = ".")) %>% 
@@ -87,7 +91,7 @@ AP_stof <- stom_fall_good %>% filter(alt.name == "American plaice") %>% select(y
 # Set up different length bins
 ac1 <- AC_stof %>% filter(length > 17 & length <= 45)
 ac2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1995)
-ap1 <- AP_stof %>% filter(length > 29) 
+ap1 <- AP_stof %>% filter(length > 29)
 gh1 <- GH_stof %>% filter(length > 19 & length <= 40)
 gh2 <- GH_stof %>% filter(length > 40)
 

### 2024-11-08 Analysis/Campelen/Fall/FallCamp_Base.R

@@ -64,12 +64,6 @@ param_list <- list(
 )
 
 
-library(TMB)
-# dyn.unload("./TMBcode/SclNLFPM")
-# compile("./TMBcode/SclNLFPM.cpp")
-dyn.load("./TMBcode/SclNLFPM")
-
-
 map <- list(lscl = as.factor(c(rep(NA, length(param_list$lscl)))))
 
 obj <- MakeADFun(data = tmb_data, map=map,

### 2024-11-08 Analysis/Campelen/Fall/FallCamp_Temp.R

@@ -64,12 +64,6 @@ param_list <- list(
 )
 
 
-library(TMB)
-# dyn.unload("./TMBcode/SclNLFPM")
-# compile("./TMBcode/SclNLFPM.cpp")
-dyn.load("./TMBcode/SclNLFPM")
-
-
 obj <- MakeADFun(data = tmb_data,
                  parameters = param_list,
                  DLL = "SclNLFPM", 

### 2024-11-08 Analysis/Campelen/Fall/FallCamp_TempLength.R

@@ -42,11 +42,6 @@ param_list <- list(
 )
 
 
-library(TMB)
-# dyn.unload("./TMBcode/SclNLFPM")
-# compile("./TMBcode/SclNLFPM.cpp")
-dyn.load("./TMBcode/SclNLFPM")
-
 
 obj <- MakeADFun(data = tmb_data,
                  parameters = param_list,

### 2024-11-08 Analysis/Campelen/Fall/FallCamp_monoTempLength.R

@@ -3,22 +3,16 @@ source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")
 
 
 
-model <- 0
+
+model <- 5
 
 fishy_dat <- data.frame(pa = pa, 
                         year = year, 
                         names = rep(names, n),
                         idmod = rep(model, sum(n)),
                         idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
+                        sppex = rep(spp_id, spp_n),
+                        temp = temp)
 
 tmb_data <- list(n = length(fishy_dat$pa),
                  nyrs = length(unique(fishy_dat$year)),
@@ -28,9 +22,8 @@ tmb_data <- list(n = length(fishy_dat$pa),
                  idmod = fishy_dat$idmod,
                  ndex = length(unique(fishy_dat$idex)),
                  idex = fishy_dat$idex,
-                 omega = omega$value,
-                 Omin = unique(omega$min)[2:length(n)],
-                 Omax = unique(omega$max)[2:length(n)]
+                 sppex = fishy_dat$sppex,
+                 temp = (fishy_dat$temp-min(fishy_dat$temp))
 )
 
 param_list <- list(
@@ -38,15 +31,15 @@ param_list <- list(
   logrw_var = log(1),
   lchi = c(rep(log(0.5), (length(n)-1))),
   lbeta = c(rep(log(0.5), (length(n)-1))),
-  lscl = c(rep(log(0.75), (length(n)-1)))
+  lmink = c(rep(log(1), (length(spp_n)-1))),
+  slo = c(rep(2, (length(spp_n)-1))),
+  lmidp = c(rep(log(3), (length(spp_n)-1)))
 )
 
 
-map <- list(lscl = as.factor(c(rep(NA, length(param_list$lscl)))))
-
-obj <- MakeADFun(data = tmb_data, map=map,
[…]

### 2024-11-08 TMBcode/SppmonoTempNLFPM.cpp

@@ -1,0 +1,168 @@
+
+#include <TMB.hpp> 
+#include <iostream>
+
+template<class Type> //only list this in whichever cpp file is alphabetically first since thats the first cpp file read in and the others aren't include guarded meaning it will tell you that it has been re-defined
+bool isNA(Type x){
+  return R_IsNA(asDouble(x));
+}
+
+template<class Type>
+Type objective_function<Type>::operator() ()
+{
+  
+  using namespace density;
+  Type nll = 0.0;
+  Type one = 1.0;
+  
+  //READ IN THE INPUT DATA
+  DATA_INTEGER(n);
+  DATA_INTEGER(nyrs);
+  // DATA_INTEGER(ndex);
+  DATA_IVECTOR(iyear);
+  DATA_IVECTOR(idex);
+  DATA_IVECTOR(sppex);
+  DATA_SCALAR(k);
+  DATA_VECTOR(pa);
+  DATA_IVECTOR(idmod);
+  //TEMPERATURE MODIFIER
+  DATA_VECTOR(temp);
+  
+  
+  //READ THE PARAMETERS
+  PARAMETER_VECTOR(iye);
+  PARAMETER(logrw_var);  
+  PARAMETER_VECTOR(lchi);
+  PARAMETER_VECTOR(lbeta);
+  PARAMETER_VECTOR(lmink);
+  PARAMETER_VECTOR(slo);
+  PARAMETER_VECTOR(lmidp);
+  
+  
+  //TRANSFORM PARAMETERS AND CREATE DERIVED PARAMETERS
+  Type rw_var = exp(logrw_var);
+  vector<Type> beta = exp(lbeta);
+  vector<Type> chi = exp(lchi);
+  
+  
+  // SCALING PARAMETER FOR TEMPERATURE MODIFICATION
+  vector<Type> mink(lmink.size());
+  for(int i = 0; i < lmink.size(); i++){
+    if(idmod(i) == 0){mink(i) = k;}
+    if(idmod(i) == 5){mink(i) = 1/(1+exp(-lmink(i)));}
+  }
+  
+  // vector<Type> slo(lslo.size());
+  // for(int i = 0; i < lslo.size(); i++){
+  //   if(idmod(i) == 0){slo(i) = k;}
+  //   if(idmod(i) == 5){slo(i) = exp(lslo(i));}
+  // }
+  
[…]

### 2025-05-08 Analysis/Campelen/Fall/3L/3LFallCamp-SetUp.R
Remove redundant code

@@ -1,170 +1,0 @@
-# Set up data
-library(tidyverse)
-library(TMB)
-dyn.load("./TMBcode/SclNLFPM")
-
-# load rstrap set data
-load(file = "./Data/setdet.rda") 
-setdet <- setdet %>% mutate(v.t.s = paste(vessel,trip,set, sep = ".")) %>% 
-  filter(spec == "889"|spec == "438"|spec == "892") %>%
-  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)),
-         long_dd = as.numeric(format(trimws(long.start), digits = 5)))
-
-
-# load and format trawl and stomach contents data
-camp_fall <- read.csv("./Data/dfo_camp_dat.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = ".")) %>%
-  rename(year = YEAR, trawl_pa = Capelin_PA)
-camp_fall <- left_join(camp_fall, 
-                       setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
-camp_fall <- camp_fall %>% filter(data.series == "Campelen" & season == "FALL"& is.na(bot.temp) == FALSE) %>%
-  mutate(lat_dd = as.numeric(trimws(lat_dd)),
-         long_dd = as.numeric(trimws(long_dd)))
-
-
-call_fall <- read.csv("./Data/dfo_call_dat.csv")
-call_fall <- left_join(call_fall, 
-                       camp_fall %>% select(v.t.s, lat_dd, long_dd, set.depth.max, bot.temp), by = c("v.t.s"))
-call_fall <- call_fall %>% filter(data.series == "Campelen" & season == "fall" & is.na(bot.temp) == FALSE)%>% 
-  mutate(content = rep("called", length(data.series))) %>%
-  select(year, month, content, alt.name, pa, NAFOdiv, length, bot.temp, lat_dd, long_dd)
-call_fall <- call_fall  %>%
-  filter((alt.name == "Atlantic cod" & length > 17)|(alt.name == "Greenland halibut" & length > 19)|(alt.name == "American plaice" & length > 29))
-
-
-full_fall <- read.csv("./Data/NAFC_diet_capelin_COD_TURBOT_PLAICE_2J3KL.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."))
-full_fall <- left_join(full_fall, 
[…]

### 2025-05-08 Analysis/Campelen/Fall/3L/3LFallCamp_Base.R

@@ -1,86 +1,0 @@
-# Set up data
-source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")
-
-
-
-## Set up for model
-n <- c(length(trawlf$year), length(AC_stof$year), length(GH_stof$year), length(AP_stof$year))
-pa <- c(trawlf$pa, AC_stof$pa, GH_stof$pa, AP_stof$pa)
-year <- c(trawlf$year, AC_stof$year, GH_stof$year, AP_stof$year)
-names <- c("Trawl", "Atlantic cod", "Greenland halibut", "American plaice")
-id = c(0,1,2,3)
-model <- 0
-
-sd_temp <- c(sd(trawlf$bot.temp), 
-             sd(AC_stof$bot.temp), 
-             sd(GH_stof$bot.temp), 
-             sd(AP_stof$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(AC_stof$bot.temp), 
-          median(GH_stof$bot.temp), 
-          median(AP_stof$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          AC_stof$bot.temp, 
-          GH_stof$bot.temp, 
-          AP_stof$bot.temp)
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n), 
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
-                 idmod = fishy_dat$idmod,
[…]

### 2025-05-08 Analysis/Campelen/Fall/3L/3LFallCamp_Length.R

@@ -1,60 +1,0 @@
-# Set up data
-source("./Analysis/Campelen/Fall/3L/3LFallCamp-SetUp.R")
-
-
-
-model <- 0
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
-                 idmod = fishy_dat$idmod,
-                 ndex = length(unique(fishy_dat$idex)),
-                 idex = fishy_dat$idex,
-                 omega = omega$value,
-                 Omin = unique(omega$min)[2:length(n)],
-                 Omax = unique(omega$max)[2:length(n)]
-)
-
-param_list <- list(
-  iye = seq(from = log(10), to = log(20), length.out = tmb_data$nyrs),
-  logrw_var = log(1),
-  lchi = c(rep(log(0.5), (length(n)-1))),
-  lbeta = c(rep(log(0.5), (length(n)-1))),
-  lscl = c(rep(log(0.75), (length(n)-1)))
-)
-
-
-
-
-map <- list(lscl = as.factor(c(rep(NA, length(param_list$lscl)))))
-
-obj <- MakeADFun(data = tmb_data, map=map,
-                 parameters = param_list,
-                 DLL = "SclNLFPM", 
-                 random = c("iye"))
-
-opt <- nlminb(obj$par, obj$fn, obj$gr, control = list(trace = 10, eval.max = 2000, iter.max = 1000), silent = TRUE)
-
-
[…]

### 2025-05-08 Analysis/Campelen/Spring/AC-SprCamp_Length.R

@@ -1,79 +1,0 @@
-# Set up data
-source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")
-
-# Set up model env
-n <- c(length(trawlf$year),
-       length(ac1$year),length(ac2$year))
-pa <- c(trawlf$pa, 
-        ac1$pa, ac2$pa)
-year <- c(trawlf$year, 
-          ac1$year, ac2$year)
-names <- c("Trawl", "ac1","ac2")
-id <- c(seq(0,(length(names)-1)))
-
-
-sd_temp <- c(sd(trawlf$bot.temp),
-             sd(ac1$bot.temp),sd(ac2$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(ac1$bot.temp), median(ac2$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          ac1$bot.temp, ac2$bot.temp)
-
-
-spp_n <- c(length(trawlf$year), 
-           sum(length(ac1$year),length(ac2$year)))
-spp_id <- c(0,1)
-
-model <- 0
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
-                 idmod = fishy_dat$idmod,
-                 ndex = length(unique(fishy_dat$idex)),
-                 idex = fishy_dat$idex,
-                 omega = omega$value,
[…]

### 2025-05-08 Analysis/Campelen/Spring/ACAP-SprCamp_Length.R

@@ -1,86 +1,0 @@
-# Set up data
-source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")
-
-# Set up model env
-n <- c(length(trawlf$year),
-       length(ac1$year),length(ac2$year),
-       length(ap1$year))
-pa <- c(trawlf$pa, 
-        ac1$pa, ac2$pa, 
-        ap1$pa)
-year <- c(trawlf$year, 
-          ac1$year, ac2$year,
-          ap1$year)
-names <- c("Trawl", "ac1","ac2", "ap1")
-id <- c(seq(0,(length(names)-1)))
-
-
-sd_temp <- c(sd(trawlf$bot.temp),
-             sd(ac1$bot.temp),sd(ac2$bot.temp),
-             sd(ap1$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(ac1$bot.temp), median(ac2$bot.temp),  
-          median(ap1$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          ac1$bot.temp, ac2$bot.temp,
-          ap1$bot.temp)
-
-
-spp_n <- c(length(trawlf$year), 
-           sum(length(ac1$year),length(ac2$year)), 
-           sum(length(ap1$year)))
-spp_id <- c(0,1,2)
-
-model <- 0
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
[…]

### 2025-05-08 Analysis/Campelen/Spring/AP-SprCamp_Length.R

@@ -1,82 +1,0 @@
-# Set up data
-source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")
-
-# Set up model env
-n <- c(length(trawlf$year),
-       length(ap1$year))
-pa <- c(trawlf$pa, 
-        ap1$pa)
-year <- c(trawlf$year, 
-          ap1$year)
-names <- c("Trawl", "ap1")
-id <- c(seq(0,(length(names)-1)))
-
-
-sd_temp <- c(sd(trawlf$bot.temp),
-             sd(ap1$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(ap1$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          ap1$bot.temp)
-
-
-spp_n <- c(length(trawlf$year), 
-           sum(length(ap1$year)))
-spp_id <- c(0,1)
-
-model <- 0
-
-ap_fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = ap_fishy_dat$names, value = rep(NA, length(ap_fishy_dat$pa)))
-for(i in 1:length(ap_fishy_dat$pa)){
-  omega[i,2] = (1/(ap_fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((ap_fishy_dat$temp[i]-ap_fishy_dat$itopt[i])/ap_fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-ap_tmb_data <- list(n = length(ap_fishy_dat$pa),
-                    nyrs = length(unique(ap_fishy_dat$year)),
-                    iyear = ap_fishy_dat$year - min(ap_fishy_dat$year),
-                    k = 1,
-                    pa = ap_fishy_dat$pa,
-                    idmod = ap_fishy_dat$idmod,
-                    ndex = length(unique(ap_fishy_dat$idex)),
-                    idex = ap_fishy_dat$idex,
-                    omega = omega$value,
-                    Omin = unique(omega$min)[2:length(n)],
[…]

### 2025-05-08 Analysis/Campelen/Spring/GH-SprCamp_Length.R

@@ -1,82 +1,0 @@
-# Set up data
-source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")
-
-# Set up model env
-n <- c(length(trawlf$year),
-       length(gh1$year),length(gh2$year))
-pa <- c(trawlf$pa, 
-        gh1$pa, gh2$pa)
-year <- c(trawlf$year, 
-          gh1$year, gh2$year)
-names <- c("Trawl", "gh1","gh2")
-id <- c(seq(0,(length(names)-1)))
-
-
-sd_temp <- c(sd(trawlf$bot.temp),
-             sd(gh1$bot.temp),sd(gh2$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(gh1$bot.temp), median(gh2$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          gh1$bot.temp, gh2$bot.temp)
-
-
-spp_n <- c(length(trawlf$year), 
-           sum(length(gh1$year),length(gh2$year)))
-spp_id <- c(0,1)
-
-model <- 0
-
-gh_fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = gh_fishy_dat$names, value = rep(NA, length(gh_fishy_dat$pa)))
-for(i in 1:length(gh_fishy_dat$pa)){
-  omega[i,2] = (1/(gh_fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((gh_fishy_dat$temp[i]-gh_fishy_dat$itopt[i])/gh_fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-gh_tmb_data <- list(n = length(gh_fishy_dat$pa),
-                    nyrs = length(unique(gh_fishy_dat$year)),
-                    iyear = gh_fishy_dat$year - min(gh_fishy_dat$year),
-                    k = 1,
-                    pa = gh_fishy_dat$pa,
-                    idmod = gh_fishy_dat$idmod,
-                    ndex = length(unique(gh_fishy_dat$idex)),
[…]

### 2025-05-08 Analysis/Campelen/Spring/GHAP-SprCamp_Length.R

@@ -1,87 +1,0 @@
-# Set up data
-source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")
-
-# Set up model env
-n <- c(length(trawlf$year),
-       length(gh1$year),length(gh2$year),
-       length(ap1$year))
-pa <- c(trawlf$pa, 
-        gh1$pa, gh2$pa,
-        ap1$pa)
-year <- c(trawlf$year, 
-          gh1$year, gh2$year,
-          ap1$year)
-names <- c("Trawl", "gh1","gh2", "ap1")
-id <- c(seq(0,(length(names)-1)))
-
-
-sd_temp <- c(sd(trawlf$bot.temp),
-             sd(gh1$bot.temp),sd(gh2$bot.temp),
-             sd(ap1$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(gh1$bot.temp), median(gh2$bot.temp),  
-          median(ap1$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          gh1$bot.temp, gh2$bot.temp,
-          ap1$bot.temp)
-
-
-spp_n <- c(length(trawlf$year), 
-           sum(length(gh1$year),length(gh2$year)),
-           sum(length(ap1$year)))
-spp_id <- c(0,1,2)
-
-
-model <- 0
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
[…]

### 2025-05-08 Analysis/Campelen/Spring/SprCamp_Base.R

@@ -1,81 +1,0 @@
-# Set up data
-source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")
-
-
-
-## Set up for model
-n <- c(length(trawlf$year), length(AC_stof$year), length(GH_stof$year), length(AP_stof$year))
-pa <- c(trawlf$pa, AC_stof$pa, GH_stof$pa, AP_stof$pa)
-year <- c(trawlf$year, AC_stof$year, GH_stof$year, AP_stof$year)
-names <- c("Trawl", "Atlantic cod", "Greenland halibut", "American plaice")
-id = c(0,1,2,3)
-model <- 0
-
-sd_temp <- c(sd(trawlf$bot.temp), 
-             sd(AC_stof$bot.temp), 
-             sd(GH_stof$bot.temp), 
-             sd(AP_stof$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(AC_stof$bot.temp), 
-          median(GH_stof$bot.temp), 
-          median(AP_stof$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          AC_stof$bot.temp, 
-          GH_stof$bot.temp, 
-          AP_stof$bot.temp)
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n), 
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
-                 idmod = fishy_dat$idmod,
-                 ndex = length(unique(fishy_dat$idex)),
[…]

### 2025-05-08 Analysis/Campelen/Spring/SprCamp_Length.R

@@ -1,58 +1,0 @@
-# Set up data
-source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")
-
-
-
-model <- 0
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
-                 idmod = fishy_dat$idmod,
-                 ndex = length(unique(fishy_dat$idex)),
-                 idex = fishy_dat$idex,
-                 omega = omega$value,
-                 Omin = unique(omega$min)[2:length(n)],
-                 Omax = unique(omega$max)[2:length(n)]
-)
-
-param_list <- list(
-  iye = seq(from = log(10), to = log(20), length.out = tmb_data$nyrs),
-  logrw_var = log(1),
-  lchi = c(rep(log(0.5), (length(n)-1))),
-  lbeta = c(rep(log(0.5), (length(n)-1))),
-  lscl = c(rep(log(0.75), (length(n)-1)))
-)
-
-
-map <- list(lscl = as.factor(c(rep(NA, length(param_list$lscl)))))
-
-obj <- MakeADFun(data = tmb_data, map=map,
-                 parameters = param_list,
-                 DLL = "SclNLFPM", 
-                 random = c("iye"))
-
-opt <- nlminb(obj$par, obj$fn, obj$gr, control = list(trace = 10, eval.max = 2000, iter.max = 1000), silent = TRUE)
-
-
-rep <- obj$report()
[…]

### 2025-05-08 Analysis/Engel/Fall/AC-FallEng_Length.R

@@ -1,84 +1,0 @@
-# Set up data
-source("./Analysis/Engel/Fall/FallEng-SetUp.R")
-
-# Set up model env
-n <- c(length(trawlf$year),
-       length(ac1$year),length(ac2$year))
-pa <- c(trawlf$pa, 
-        ac1$pa, ac2$pa)
-year <- c(trawlf$year, 
-          ac1$year, ac2$year)
-names <- c("Trawl", "ac1","ac2")
-id <- c(seq(0,(length(names)-1)))
-
-
-sd_temp <- c(sd(trawlf$bot.temp),
-             sd(ac1$bot.temp),sd(ac2$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(ac1$bot.temp), median(ac2$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          ac1$bot.temp, ac2$bot.temp)
-
-
-spp_n <- c(length(trawlf$year), 
-           sum(length(ac1$year),length(ac2$year)))
-spp_id <- c(0,1)
-
-
-
-model <- 0
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
-                 idmod = fishy_dat$idmod,
-                 ndex = length(unique(fishy_dat$idex)),
-                 idex = fishy_dat$idex,
-                 omega = omega$value,
[…]

### 2025-05-08 Analysis/Engel/Fall/AP-FallEng_Length.R

@@ -1,84 +1,0 @@
-# Set up data
-source("./Analysis/Engel/Fall/FallEng-SetUp.R")
-
-# Set up model env
-n <- c(length(trawlf$year),
-       length(ap1$year))
-pa <- c(trawlf$pa, 
-        ap1$pa)
-year <- c(trawlf$year, 
-          ap1$year)
-names <- c("Trawl", "ap1")
-id <- c(seq(0,(length(names)-1)))
-
-
-sd_temp <- c(sd(trawlf$bot.temp),
-             sd(ap1$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(ap1$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          ap1$bot.temp)
-
-
-spp_n <- c(length(trawlf$year), 
-           sum(length(ap1$year)))
-spp_id <- c(0,1)
-
-
-
-model <- 0
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
-                 idmod = fishy_dat$idmod,
-                 ndex = length(unique(fishy_dat$idex)),
-                 idex = fishy_dat$idex,
-                 omega = omega$value,
-                 Omin = unique(omega$min)[2:length(n)],
-                 Omax = unique(omega$max)[2:length(n)]
-)
-
-param_list <- list(
[…]

### 2025-05-08 Analysis/Engel/Fall/FallEng_Length.R

@@ -1,61 +1,0 @@
-# Set up data
-source("./Analysis/Engel/Fall/FallEng-SetUp.R")
-
-
-
-model <- 0
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
-                 idmod = fishy_dat$idmod,
-                 ndex = length(unique(fishy_dat$idex)),
-                 idex = fishy_dat$idex,
-                 omega = omega$value,
-                 Omin = unique(omega$min)[2:length(n)],
-                 Omax = unique(omega$max)[2:length(n)]
-)
-
-param_list <- list(
-  iye = seq(from = log(10), to = log(20), length.out = tmb_data$nyrs),
-  logrw_var = log(1),
-  lchi = c(rep(log(0.5), (length(n)-1))),
-  lbeta = c(rep(log(0.5), (length(n)-1))),
-  lscl = c(rep(log(0.75), (length(n)-1)))
-)
-
-
-
-
-
-map <- list(lscl = as.factor(c(rep(NA, length(param_list$lscl)))))
-
-obj <- MakeADFun(data = tmb_data, map=map,
-                 parameters = param_list,
-                 DLL = "SclNLFPM", 
-                 random = c("iye"))
-
-opt <- nlminb(obj$par, obj$fn, obj$gr, control = list(trace = 10, eval.max = 2000, iter.max = 1000), silent = TRUE)
-
-
[…]

### 2025-05-08 Analysis/Engel/Fall/GHAP-FallEng_Length.R

@@ -1,90 +1,0 @@
-# Set up data
-source("./Analysis/Engel/Fall/FallEng-SetUp.R")
-
-# Set up model env
-n <- c(length(trawlf$year),
-       length(gh1$year),length(gh2$year),
-       length(ap1$year))
-pa <- c(trawlf$pa, 
-        gh1$pa, gh2$pa,
-        ap1$pa)
-year <- c(trawlf$year, 
-          gh1$year, gh2$year,
-          ap1$year)
-names <- c("Trawl", "gh1","gh2", "ap1")
-id <- c(seq(0,(length(names)-1)))
-
-
-sd_temp <- c(sd(trawlf$bot.temp),
-             sd(gh1$bot.temp),sd(gh2$bot.temp),
-             sd(ap1$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(gh1$bot.temp), median(gh2$bot.temp),  
-          median(ap1$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          gh1$bot.temp, gh2$bot.temp,
-          ap1$bot.temp)
-
-
-spp_n <- c(length(trawlf$year), 
-           sum(length(gh1$year),length(gh2$year)),
-           sum(length(ap1$year)))
-spp_id <- c(0,1,2)
-
-
-model <- 0
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
[…]

### 2025-05-08 Analysis/Engel/Spring/ACAP-SprEng_Length.R

@@ -1,89 +1,0 @@
-# Set up data
-source("./Analysis/Engel/Spring/SprEng-SetUp.R")
-
-# Set up model env
-n <- c(length(trawlf$year),
-       length(ac1$year),length(ac2$year),
-       length(ap1$year))
-pa <- c(trawlf$pa, 
-        ac1$pa, ac2$pa, 
-        ap1$pa)
-year <- c(trawlf$year, 
-          ac1$year, ac2$year,
-          ap1$year)
-names <- c("Trawl", "ac1","ac2", "ap1")
-id <- c(seq(0,(length(names)-1)))
-
-
-sd_temp <- c(sd(trawlf$bot.temp),
-             sd(ac1$bot.temp),sd(ac2$bot.temp),
-             sd(ap1$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(ac1$bot.temp), median(ac2$bot.temp),  
-          median(ap1$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          ac1$bot.temp, ac2$bot.temp,
-          ap1$bot.temp)
-
-
-spp_n <- c(length(trawlf$year), 
-           sum(length(ac1$year),length(ac2$year)), 
-           sum(length(ap1$year)))
-spp_id <- c(0,1,2)
-
-model <- 0
-
-ac_fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = ac_fishy_dat$names, value = rep(NA, length(ac_fishy_dat$pa)))
-for(i in 1:length(ac_fishy_dat$pa)){
-  omega[i,2] = (1/(ac_fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((ac_fishy_dat$temp[i]-ac_fishy_dat$itopt[i])/ac_fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-ac_tmb_data <- list(n = length(ac_fishy_dat$pa),
-                    nyrs = length(unique(ac_fishy_dat$year)),
-                    iyear = ac_fishy_dat$year - min(ac_fishy_dat$year),
-                    k = 1,
[…]

### 2025-05-08 Analysis/Engel/Spring/GH-SprEng_Length.R

@@ -1,82 +1,0 @@
-# Set up data
-source("./Analysis/Engel/Spring/SprEng-SetUp.R")
-
-# Set up model env
-n <- c(length(trawlf$year),
-       length(gh1$year),length(gh2$year))
-pa <- c(trawlf$pa, 
-        gh1$pa, gh2$pa)
-year <- c(trawlf$year, 
-          gh1$year, gh2$year)
-names <- c("Trawl", "gh1","gh2")
-id <- c(seq(0,(length(names)-1)))
-
-
-sd_temp <- c(sd(trawlf$bot.temp),
-             sd(gh1$bot.temp),sd(gh2$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(gh1$bot.temp), median(gh2$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          gh1$bot.temp, gh2$bot.temp)
-
-
-spp_n <- c(length(trawlf$year), 
-           sum(length(gh1$year),length(gh2$year)))
-spp_id <- c(0,1)
-
-model <- 0
-
-gh_fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = gh_fishy_dat$names, value = rep(NA, length(gh_fishy_dat$pa)))
-for(i in 1:length(gh_fishy_dat$pa)){
-  omega[i,2] = (1/(gh_fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((gh_fishy_dat$temp[i]-gh_fishy_dat$itopt[i])/gh_fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-gh_tmb_data <- list(n = length(gh_fishy_dat$pa),
-                    nyrs = length(unique(gh_fishy_dat$year)),
-                    iyear = gh_fishy_dat$year - min(gh_fishy_dat$year),
-                    k = 1,
-                    pa = gh_fishy_dat$pa,
-                    idmod = gh_fishy_dat$idmod,
-                    ndex = length(unique(gh_fishy_dat$idex)),
[…]

### 2025-05-08 TMBcode/SclNLFPM.cpp
Add choice of ontogentic inclusion/exclusion

@@ -14,134 +14,244 @@ Type objective_function<Type>::operator() ()
   using namespace density;
   Type nll = 0.0;
   Type one = 1.0;
+  
+  DATA_INTEGER(idmod);
+  
+  
+  
+  //NO TEMPERATURE EFFECT  
+  if(idmod == 0){
+    //READ IN THE INPUT DATA
+    DATA_INTEGER(n);
+    DATA_INTEGER(nyrs);
+    DATA_IVECTOR(iyear);
+    DATA_IVECTOR(idex);
+    DATA_SCALAR(k);
+    DATA_VECTOR(pa);
+    
+    //READ THE PARAMETERS
+    PARAMETER_VECTOR(iye);
+    PARAMETER(logrw_var);  
+    PARAMETER_VECTOR(lbeta);
+    PARAMETER_VECTOR(lchi);
+    
+    //TRANSFORM PARAMETERS AND CREATE DERIVED PARAMETERS
+    Type rw_var = exp(logrw_var);
+    vector<Type> beta = exp(lbeta);
+    vector<Type> chi = exp(lchi);
 
-  //READ IN THE INPUT DATA
-  DATA_INTEGER(n);
-  DATA_INTEGER(nyrs);
-  // DATA_INTEGER(ndex);
-  DATA_IVECTOR(iyear);
-  DATA_IVECTOR(idex);
-  DATA_SCALAR(k);
-  DATA_VECTOR(pa);
-  DATA_IVECTOR(idmod);
-  //TEMPERATURE MODIFIER
-  DATA_VECTOR(omega);
-  DATA_VECTOR(Omin);
-  DATA_VECTOR(Omax);
-
-  
-  //READ THE PARAMETERS
-  PARAMETER_VECTOR(iye);
-  PARAMETER(logrw_var);  
-  PARAMETER_VECTOR(lchi);
-  PARAMETER_VECTOR(lbeta);
-  PARAMETER_VECTOR(lscl);
-  
-  //TRANSFORM PARAMETERS AND CREATE DERIVED PARAMETERS
-  Type rw_var = exp(logrw_var);
-  vector<Type> beta = exp(lbeta);
-  vector<Type> chi = exp(lchi);
-  
-  // SCALING PARAMETER FOR TEMPERATURE MODIFICATION
-  vector<Type> scl(lscl.size());
-  for(int i = 0; i < lscl.size(); i++){
[…]

### 2025-05-08 TMBcode/SppmonoTempNLFPM.cpp

@@ -15,154 +15,259 @@ Type objective_function<Type>::operator() ()
   Type nll = 0.0;
   Type one = 1.0;
   
-  //READ IN THE INPUT DATA
-  DATA_INTEGER(n);
-  DATA_INTEGER(nyrs);
-  // DATA_INTEGER(ndex);
-  DATA_IVECTOR(iyear);
-  DATA_IVECTOR(idex);
-  DATA_IVECTOR(sppex);
-  DATA_SCALAR(k);
-  DATA_VECTOR(pa);
-  DATA_IVECTOR(idmod);
-  //TEMPERATURE MODIFIER
-  DATA_VECTOR(temp);
   
+  DATA_INTEGER(idmod);
   
-  //READ THE PARAMETERS
-  PARAMETER_VECTOR(iye);
-  PARAMETER(logrw_var);  
-  PARAMETER_VECTOR(lchi);
-  PARAMETER_VECTOR(lbeta);
-  PARAMETER_VECTOR(lmink);
-  PARAMETER_VECTOR(slo);
-  PARAMETER_VECTOR(lmidp);
-  
-  
-  //TRANSFORM PARAMETERS AND CREATE DERIVED PARAMETERS
-  Type rw_var = exp(logrw_var);
-  vector<Type> beta = exp(lbeta);
-  vector<Type> chi = exp(lchi);
-  
-  
-  // SCALING PARAMETER FOR TEMPERATURE MODIFICATION
-  vector<Type> mink(lmink.size());
-  for(int i = 0; i < lmink.size(); i++){
-    if(idmod(i) == 0){mink(i) = k;}
-    if(idmod(i) == 5){mink(i) = 1/(1+exp(-lmink(i)));}
-  }
-  
-  // vector<Type> slo(lslo.size());
-  // for(int i = 0; i < lslo.size(); i++){
-  //   if(idmod(i) == 0){slo(i) = k;}
-  //   if(idmod(i) == 5){slo(i) = exp(lslo(i));}
-  // }
-  
-  vector<Type> midp(lmidp.size());
-  for(int i = 0; i < lmidp.size(); i++){
-    if(idmod(i) == 0){midp(i) = k;}
-    if(idmod(i) == 5){midp(i) = exp(lmidp(i));}
-  }
-  
-  
-  // SET UP ENV FOR VARIABLES USED IN FUNCTIONAL RESPONSE EQUATION
-  vector<Type> mu(nyrs);
[…]

### 2025-05-08 Analysis/Campelen/Fall/FallCamp-SetUp.R
Model selection from fall Campelen

@@ -1,57 +1,77 @@
-# Set up data
-library(tidyverse)
-library(TMB)
-dyn.load("./TMBcode/SclNLFPM")
-
-# dyn.unload("./TMBcode/monoTempNLFPM")
-# compile("./TMBcode/monoTempNLFPM.cpp")
-dyn.load("./TMBcode/monoTempNLFPM")
-
 # load rstrap set data
 load(file = "./Data/setdet.rda") 
 setdet <- setdet %>% mutate(v.t.s = paste(vessel,trip,set, sep = ".")) %>% 
   filter(spec == "889"|spec == "438"|spec == "892") %>%
-  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)),
-         long_dd = as.numeric(format(trimws(long.start), digits = 5)))
+  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)), # check that lat and longs are the same format in all data sources
+         long_dd = as.numeric(format(trimws(long.start), digits = 5))) # trimws() needed due to data entry errors
 
 
-# load and format trawl and stomach contents data
-camp_fall <- read.csv("./Data/dfo_camp_dat.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = ".")) %>%
-  rename(year = YEAR, trawl_pa = Capelin_PA)
+# Trawl data
+camp_fall <- read.csv("./Data/camp_capelin_2J3KL_FULL.csv") %>% rename(year = YEAR, trawl_pa = Capelin_PA) %>% 
+  mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."),
+         season = ifelse(MONTH == 3|MONTH == 4|MONTH == 5|MONTH == 6|MONTH == 7, "spring", "fall"),
+         lat_dd = as.numeric(format(trimws(lat_dd), digits = 5)), # check that lat and longs are the same format in all data sources
+         long_dd = as.numeric(format(trimws(long_dd), digits = 5))) # trimws() needed due to data entry errors
 camp_fall <- left_join(camp_fall, 
                        setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
-camp_fall <- camp_fall %>% filter(data.series == "Campelen" & season == "FALL"& is.na(bot.temp) == FALSE) %>%
-  mutate(lat_dd = as.numeric(trimws(lat_dd)),
-         long_dd = as.numeric(trimws(long_dd)))
[…]

### 2025-05-08 Analysis/Campelen/Fall/FallCamp_Base.R

@@ -1,79 +1,62 @@
-# Set up data
-source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")
+# Set up environment
+library(tidyverse)
+library(TMB)
+
+# Load functions
+source("./Functions/make_data.R")
+source("./Functions/model_data.R")
+source("./Functions/model_param.R")
+
+# Load TMB models
+dyn.load("./TMBcode/SclNLFPM")
+dyn.load("./TMBcode/SppmonoTempNLFPM")
 
 
+# Set up data for model
+load(file = "./ModelSaves/Set_Up/FC-2020.RData")
 
-## Set up for model
-n <- c(length(trawlf$year), length(AC_stof$year), length(GH_stof$year), length(AP_stof$year))
-pa <- c(trawlf$pa, AC_stof$pa, GH_stof$pa, AP_stof$pa)
-year <- c(trawlf$year, AC_stof$year, GH_stof$year, AP_stof$year)
-names <- c("Trawl", "Atlantic cod", "Greenland halibut", "American plaice")
-id = c(0,1,2,3)
-model <- 0
-
-sd_temp <- c(sd(trawlf$bot.temp), 
-             sd(AC_stof$bot.temp), 
-             sd(GH_stof$bot.temp), 
-             sd(AP_stof$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(AC_stof$bot.temp), 
-          median(GH_stof$bot.temp), 
-          median(AP_stof$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          AC_stof$bot.temp, 
-          GH_stof$bot.temp, 
-          AP_stof$bot.temp)
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n), 
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
[…]

### 2025-05-08 Analysis/Campelen/Fall/FallCamp_Length.R

@@ -1,57 +1,48 @@
-# Set up data
-source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")
+# Set up environment
+library(tidyverse)
+library(TMB)
+
+# Load functions
+source("./Functions/make_data.R")
+source("./Functions/model_data.R")
+source("./Functions/model_param.R")
+
+# Load TMB models
+dyn.load("./TMBcode/SclNLFPM")
+dyn.load("./TMBcode/SppmonoTempNLFPM")
 
 
+# Set up data for model
+load(file = "./ModelSaves/Set_Up/FC-2020.RData")
 
-model <- 0
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
-                 idmod = fishy_dat$idmod,
-                 ndex = length(unique(fishy_dat$idex)),
-                 idex = fishy_dat$idex,
-                 omega = omega$value,
-                 Omin = unique(omega$min)[2:length(n)],
-                 Omax = unique(omega$max)[2:length(n)]
-)
-
-param_list <- list(
-  iye = seq(from = log(10), to = log(20), length.out = tmb_data$nyrs),
-  logrw_var = log(1),
-  lchi = c(rep(log(0.5), (length(n)-1))),
-  lbeta = c(rep(log(0.5), (length(n)-1))),
-  lscl = c(rep(log(0.75), (length(n)-1)))
+fishy_dat <- make_data(n = n,
+                       pa = pa, 
[…]

### 2025-05-08 Analysis/Campelen/Fall/FallCamp_TempLength.R

@@ -1,56 +1,49 @@
-# Set up data
-source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")
+# Set up environment
+library(tidyverse)
+library(TMB)
+
+# Load functions
+source("./Functions/make_data.R")
+source("./Functions/model_data.R")
+source("./Functions/model_param.R")
+
+# Load TMB models
+dyn.load("./TMBcode/SclNLFPM")
+dyn.load("./TMBcode/SppmonoTempNLFPM")
 
 
+# Set up data for model
+load(file = "./ModelSaves/Set_Up/FC-2020.RData")
 
-model <- 5
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
-                 idmod = fishy_dat$idmod,
-                 ndex = length(unique(fishy_dat$idex)),
-                 idex = fishy_dat$idex,
-                 omega = omega$value,
-                 Omin = unique(omega$min)[2:length(n)],
-                 Omax = unique(omega$max)[2:length(n)]
-)
-
-param_list <- list(
-  iye = seq(from = log(10), to = log(20), length.out = tmb_data$nyrs),
-  logrw_var = log(1),
-  lchi = c(rep(log(0.5), (length(n)-1))),
-  lbeta = c(rep(log(0.5), (length(n)-1))),
-  lscl = c(rep(log(0.75), (length(n)-1)))
+fishy_dat <- make_data(n = n,
+                       pa = pa, 
[…]

### 2025-05-08 Analysis/Campelen/Fall/FallCamp_monoTemp.R

@@ -30,7 +30,9 @@ fishy_dat <- make_data(n = c(length(trawlf$year),
                                 c(ap1$year)), 
                        names = c("Trawl", "Atlantic cod", "Greenland halibut", "American plaice"), 
                        onto = F,
-                       tempType = "scaledTemp",
+                       tempType = "monoTemp",
+                       spp_id = spp_id,
+                       spp_n = spp_n,
                        temp = c(trawlf$bot.temp, 
                                 c(ac1$bot.temp, ac2$bot.temp),
                                 c(gh1$bot.temp, gh2$bot.temp),
@@ -39,9 +41,8 @@ fishy_dat <- make_data(n = c(length(trawlf$year),
 
 
 
-
 # Set up data to be passed into TMB
-tmb_data <- model_data(fishy_dat = fishy_dat, modType = "nonlinear", tempType = "scaledTemp",
+tmb_data <- model_data(fishy_dat = fishy_dat, modType = "nonlinear", tempType = "monoTemp",
                        n = c(length(trawlf$year), 
                              length(c(ac1$year, ac2$year)), 
                              length(c(gh1$year, gh2$year)), 
@@ -51,13 +52,13 @@ tmb_data <- model_data(fishy_dat = fishy_dat, modType = "nonlinear", tempType = 
 
 
 # Set up parameters estimated by TMB
-tmb_params <- model_param(tmb_data = tmb_data, lbeta = log(0.5), lchi = log(0.5), lscl = log(0.75))
+tmb_params <- model_param(tmb_data = tmb_data, lbeta = log(0.5), lchi = log(0.5), lmink = log(1), lmidp = log(15))
 
 
 # Run model
 obj <- MakeADFun(data = tmb_data,
                  parameters = tmb_params,
-                 DLL = "SclNLFPM", 
+                 DLL = "SppmonoTempNLFPM", 
                  random = c("iye"))
 
 opt <- nlminb(obj$par, obj$fn, obj$gr, control = list(trace = 10, eval.max = 2000, iter.max = 1000), silent = TRUE)
@@ -67,4 +68,3 @@ rep <- obj$report()
 sdrep <- sdreport(obj)
 sdrep
 2*opt$objective + 2*length(opt$par)
-

### 2025-05-08 Analysis/Campelen/Fall/FallCamp_monoTempLength.R

@@ -1,51 +1,51 @@
-# Set up data
-source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")
+# Set up environment
+library(tidyverse)
+library(TMB)
+
+# Load functions
+source("./Functions/make_data.R")
+source("./Functions/model_data.R")
+source("./Functions/model_param.R")
+
+# Load TMB models
+dyn.load("./TMBcode/SclNLFPM")
+dyn.load("./TMBcode/SppmonoTempNLFPM")
 
 
+# Set up data for model
+load(file = "./ModelSaves/Set_Up/FC-2020.RData")
 
-
-model <- 5
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        sppex = rep(spp_id, spp_n),
-                        temp = temp)
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
-                 idmod = fishy_dat$idmod,
-                 ndex = length(unique(fishy_dat$idex)),
-                 idex = fishy_dat$idex,
-                 sppex = fishy_dat$sppex,
-                 temp = (fishy_dat$temp-min(fishy_dat$temp))
-)
-
-param_list <- list(
-  iye = seq(from = log(10), to = log(20), length.out = tmb_data$nyrs),
-  logrw_var = log(1),
-  lchi = c(rep(log(0.5), (length(n)-1))),
-  lbeta = c(rep(log(0.5), (length(n)-1))),
-  lmink = c(rep(log(1), (length(spp_n)-1))),
-  slo = c(rep(2, (length(spp_n)-1))),
-  lmidp = c(rep(log(3), (length(spp_n)-1)))
+fishy_dat <- make_data(n = n,
+                       pa = pa, 
+                       year = year, 
+                       names = names,
+                       tempType = "monoTemp",
+                       onto = T,
+                       temp = temp,
+                       spp_id = spp_id,
+                       spp_n = spp_n
 )
 
 
+# Set up data to be passed into TMB
[…]

### 2025-05-08 Analysis/Campelen/Spring/SprCamp-SetUp.R
Add spring Campelen models

@@ -1,51 +1,74 @@
-# Set up data
-library(tidyverse)
-library(TMB)
-dyn.load("./TMBcode/SclNLFPM")
-
-
-
 # load rstrap set data
 load(file = "./Data/setdet.rda") 
 setdet <- setdet %>% mutate(v.t.s = paste(vessel,trip,set, sep = ".")) %>% 
   filter(spec == "889"|spec == "438"|spec == "892") %>%
-  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)),
-         long_dd = as.numeric(format(trimws(long.start), digits = 5)))
+  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)), # check that lat and longs are the same format in all data sources
+         long_dd = as.numeric(format(trimws(long.start), digits = 5))) # trimws() needed due to data entry errors
 
 
-# load and format trawl and stomach contents data
-camp_spr <- read.csv("./Data/dfo_camp_dat.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = ".")) %>%
-  rename(year = YEAR, trawl_pa = Capelin_PA)
+# Trawl data
+camp_spr <- read.csv("./Data/camp_capelin_2J3KL_FULL.csv") %>% rename(year = YEAR, trawl_pa = Capelin_PA) %>% 
+  mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."),
+         season = ifelse(MONTH == 3|MONTH == 4|MONTH == 5|MONTH == 6|MONTH == 7, "spring", "spr"),
+         lat_dd = as.numeric(format(trimws(lat_dd), digits = 5)), # check that lat and longs are the same format in all data sources
+         long_dd = as.numeric(format(trimws(long_dd), digits = 5))) # trimws() needed due to data entry errors
 camp_spr <- left_join(camp_spr, 
                       setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
-camp_spr <- camp_spr %>% filter(data.series == "Campelen" & season == "SPRING"& is.na(bot.temp) == FALSE) %>%
-  mutate(lat_dd = as.numeric(trimws(lat_dd)),
-         long_dd = as.numeric(trimws(long_dd)))
+camp_spr <- camp_spr %>% filter(data.series == "Campelen" & 
+                                  season == "spring"& 
[…]

### 2025-05-08 Analysis/Engel/Fall/ACAP-FallEng_Length.R
Add fall Engel models

@@ -1,91 +1,56 @@
-# Set up data
-source("./Analysis/Engel/Fall/FallEng-SetUp.R")
+# Set up environment
+library(tidyverse)
+library(TMB)
 
-# Set up model env
-n <- c(length(trawlf$year),
-       length(ac1$year),length(ac2$year),
-       length(ap1$year))
-pa <- c(trawlf$pa, 
-        ac1$pa, ac2$pa, 
-        ap1$pa)
-year <- c(trawlf$year, 
-          ac1$year, ac2$year,
-          ap1$year)
-names <- c("Trawl", "ac1","ac2", "ap1")
-id <- c(seq(0,(length(names)-1)))
+# Load functions
+source("./Functions/make_data.R")
+source("./Functions/model_data.R")
+source("./Functions/model_param.R")
+
+# Load TMB models
+dyn.load("./TMBcode/SclNLFPM")
+dyn.load("./TMBcode/SppmonoTempNLFPM")
 
 
-sd_temp <- c(sd(trawlf$bot.temp),
-             sd(ac1$bot.temp),sd(ac2$bot.temp),
-             sd(ap1$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(ac1$bot.temp), median(ac2$bot.temp),  
-          median(ap1$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          ac1$bot.temp, ac2$bot.temp,
-          ap1$bot.temp)
+# Set up data for model
+load(file = "./ModelSaves/Set_Up/FE-1994.RData")
 
-
-spp_n <- c(length(trawlf$year), 
-           sum(length(ac1$year),length(ac2$year)), 
-           sum(length(ap1$year)))
-spp_id <- c(0,1,2)
-
-
-
-model <- 0
-
-ac_fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = ac_fishy_dat$names, value = rep(NA, length(ac_fishy_dat$pa)))
-for(i in 1:length(ac_fishy_dat$pa)){
[…]

### 2025-05-08 Analysis/Engel/Fall/FallEng-SetUp.R

@@ -1,51 +1,78 @@
-# Set up data
-library(tidyverse)
-library(TMB)
-dyn.load("./TMBcode/SclNLFPM")
-
-
 # load rstrap set data
 load(file = "./Data/setdet.rda") 
 setdet <- setdet %>% mutate(v.t.s = paste(vessel,trip,set, sep = ".")) %>% 
   filter(spec == "889"|spec == "438"|spec == "892") %>%
-  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)),
-         long_dd = as.numeric(format(trimws(long.start), digits = 5)))
+  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)), # check that lat and longs are the same format in all data sources
+         long_dd = as.numeric(format(trimws(long.start), digits = 5))) # trimws() needed due to data entry errors
 
 
-# load and format trawl and stomach contents data
-eng_fall <- read.csv("./Data/dfo_camp_dat.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = ".")) %>%
-  rename(year = YEAR, trawl_pa = Capelin_PA)
+# Trawl data
+eng_fall <- read.csv("./Data/camp_capelin_2J3KL_FULL.csv") %>% rename(year = YEAR, trawl_pa = Capelin_PA) %>% 
+  mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."),
+         season = ifelse(MONTH == 3|MONTH == 4|MONTH == 5|MONTH == 6|MONTH == 7, "spring", "fall"),
+         lat_dd = as.numeric(format(trimws(lat_dd), digits = 5)), # check that lat and longs are the same format in all data sources
+         long_dd = as.numeric(format(trimws(long_dd), digits = 5))) # trimws() needed due to data entry errors
+
 eng_fall <- left_join(eng_fall, 
                       setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
-eng_fall <- eng_fall %>% filter(data.series == "Engel" & season == "FALL"& is.na(bot.temp) == FALSE) %>%
-  filter(year >= 1981) %>% 
-  mutate(lat_dd = as.numeric(trimws(lat_dd)),
-         long_dd = as.numeric(trimws(long_dd)))
+eng_fall <- eng_fall %>% filter(data.series == "Engel" & 
+                                  season == "fall" & 
[…]

### 2025-05-08 Analysis/Engel/Fall/GH-FallEng_Length.R

@@ -1,83 +1,52 @@
-# Set up data
-source("./Analysis/Engel/Fall/FallEng-SetUp.R")
+# Set up environment
+library(tidyverse)
+library(TMB)
 
-# Set up model env
-n <- c(length(trawlf$year),
-       length(gh1$year),length(gh2$year))
-pa <- c(trawlf$pa, 
-        gh1$pa, gh2$pa)
-year <- c(trawlf$year, 
-          gh1$year, gh2$year)
-names <- c("Trawl", "gh1","gh2")
-id <- c(seq(0,(length(names)-1)))
+# Load functions
+source("./Functions/make_data.R")
+source("./Functions/model_data.R")
+source("./Functions/model_param.R")
 
-
-sd_temp <- c(sd(trawlf$bot.temp),
-             sd(gh1$bot.temp),sd(gh2$bot.temp))
-topt <- c(median(trawlf$bot.temp), 
-          median(gh1$bot.temp), median(gh2$bot.temp))
-temp <- c(trawlf$bot.temp, 
-          gh1$bot.temp, gh2$bot.temp)
+# Load TMB models
+dyn.load("./TMBcode/SclNLFPM")
+dyn.load("./TMBcode/SppmonoTempNLFPM")
 
 
-spp_n <- c(length(trawlf$year), 
-           sum(length(gh1$year),length(gh2$year)))
-spp_id <- c(0,1)
+# Set up data for model
+load(file = "./ModelSaves/Set_Up/FE-1994.RData")
 
-
-model <- 0
-
-gh_fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = gh_fishy_dat$names, value = rep(NA, length(gh_fishy_dat$pa)))
-for(i in 1:length(gh_fishy_dat$pa)){
-  omega[i,2] = (1/(gh_fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((gh_fishy_dat$temp[i]-gh_fishy_dat$itopt[i])/gh_fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
[…]

### 2025-05-08 Analysis/Engel/Spring/SprEng-SetUp.R
Add spring Engel models

@@ -1,51 +1,77 @@
-# Set up data
-library(tidyverse)
-library(TMB)
-dyn.load("./TMBcode/SclNLFPM")
-
-
 # load rstrap set data
 load(file = "./Data/setdet.rda") 
 setdet <- setdet %>% mutate(v.t.s = paste(vessel,trip,set, sep = ".")) %>% 
   filter(spec == "889"|spec == "438"|spec == "892") %>%
-  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)),
-         long_dd = as.numeric(format(trimws(long.start), digits = 5)))
+  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)), # check that lat and longs are the same format in all data sources
+         long_dd = as.numeric(format(trimws(long.start), digits = 5))) # trimws() needed due to data entry errors
 
 
-# load and format trawl and stomach contents data
-eng_spr <- read.csv("./Data/dfo_camp_dat.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = ".")) %>%
-  rename(year = YEAR, trawl_pa = Capelin_PA)
+# Trawl data
+eng_spr <- read.csv("./Data/camp_capelin_2J3KL_FULL.csv") %>% rename(year = YEAR, trawl_pa = Capelin_PA) %>% 
+  mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."),
+         season = ifelse(MONTH == 3|MONTH == 4|MONTH == 5|MONTH == 6|MONTH == 7, "spring", "spr"),
+         lat_dd = as.numeric(format(trimws(lat_dd), digits = 5)), # check that lat and longs are the same format in all data sources
+         long_dd = as.numeric(format(trimws(long_dd), digits = 5))) # trimws() needed due to data entry errors
 eng_spr <- left_join(eng_spr, 
                      setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
-eng_spr <- eng_spr %>% filter(data.series == "Engel" & season == "SPRING" & is.na(bot.temp) == FALSE) %>%
-  filter(year >= 1981) %>% 
-  mutate(lat_dd = as.numeric(trimws(lat_dd)),
-         long_dd = as.numeric(trimws(long_dd)))
+eng_spr <- eng_spr %>% filter(data.series == "Engel" & 
+                                season == "spring"& 
[…]

### 2025-05-08 Analysis/Engel/Spring/SprEng_Length.R

@@ -1,59 +1,49 @@
-# Set up data
-source("./Analysis/Engel/Spring/SprEng-SetUp.R")
+# Set up environment
+library(tidyverse)
+library(TMB)
+
+# Load functions
+source("./Functions/make_data.R")
+source("./Functions/model_data.R")
+source("./Functions/model_param.R")
+
+# Load TMB models
+dyn.load("./TMBcode/SclNLFPM")
+dyn.load("./TMBcode/SppmonoTempNLFPM")
 
 
+# Set up data for model
+load(file = "./ModelSaves/Set_Up/SE-1995.RData")
 
-model <- 0
-
-fishy_dat <- data.frame(pa = pa, 
-                        year = year, 
-                        names = rep(names, n),
-                        idmod = rep(model, sum(n)),
-                        idex = rep(id, n),
-                        temp = temp,
-                        isd_temp = rep(sd_temp, n),
-                        itopt = rep(topt, n))
-
-omega <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
-for(i in 1:length(fishy_dat$pa)){
-  omega[i,2] = (1/(fishy_dat$isd_temp[i]*sqrt(2*pi)))*exp((-0.5)*((fishy_dat$temp[i]-fishy_dat$itopt[i])/fishy_dat$isd_temp[i])^2)
-}
-omega <- omega %>% group_by(species) %>% mutate(min = min(value), max = max(value))
-
-tmb_data <- list(n = length(fishy_dat$pa),
-                 nyrs = length(unique(fishy_dat$year)),
-                 iyear = fishy_dat$year - min(fishy_dat$year),
-                 k = 1,
-                 pa = fishy_dat$pa,
-                 idmod = fishy_dat$idmod,
-                 ndex = length(unique(fishy_dat$idex)),
-                 idex = fishy_dat$idex,
-                 omega = omega$value,
-                 Omin = unique(omega$min)[2:length(n)],
-                 Omax = unique(omega$max)[2:length(n)]
-)
-
-param_list <- list(
-  iye = seq(from = log(10), to = log(20), length.out = tmb_data$nyrs),
-  logrw_var = log(1),
-  lchi = c(rep(log(0.5), (length(n)-1))),
-  lbeta = c(rep(log(0.5), (length(n)-1))),
-  lscl = c(rep(log(0.75), (length(n)-1)))
+fishy_dat <- make_data(n = n,
+                       pa = pa, 
[…]

### 2025-05-08 PaperSections.Rmd
To match manuscript version 23.04.2025

@@
 library(ggpubr)
+```
+
+# Map
+
+```{r}
+library(ggOceanMaps)
+library(grid)
+library(sf)
+library(ggspatial)
+
+# .ggOceanMapsenv <- new.env() ## set new environment to save shape file
+# .ggOceanMapsenv$datapath <- "./Data/dd_rbathy_cont.rda"
+
+notenclosed <- read_sf("C:/Users/klynch/OneDrive - Marine Institute of Memorial University (1)/Thesis/Manu_1/Code/Chap1/Data/NAFO_Divisions_SHP/NAFO_Divisions_2021_line_not_enclosed.shp")
+JKsubocean <- notenclosed %>% filter(Division == "2J"|Division == "3K") 
+Lsubocean <- notenclosed %>% filter(Division == "3L")
+
+poly <- read_sf("C:/Users/klynch/OneDrive - Marine Institute of Memorial University (1)/Thesis/Manu_1/Code/Chap1/Data/NAFO_Divisions_SHP/NAFO_Divisions_2021_poly_clipped.shp")
+JKsubpoly <- poly %>% filter(Division == "2J"|Division == "3K")
+Lsubpoly <- poly %>% filter(Division == "3L")
+
+acsurv <- read_sf("C:/Users/klynch/OneDrive - Marine Institute of Memorial University (1)/Thesis/Manu_1/Code/Chap1/Data/Survey_Area/general_survey_area.shp")
+
+```
+## - Figure 2
+```{r, fig.width=5, fig.height=5}
+load("./Data/nlbasemap.RData")
+
+map <-  nlmap +
+  geom_spatial_text(aes(x = -50, y = c(53.5, 51, 47.5), label = c("2J","3K","3L")))+
+
+  geom_sf(data = JKsubocean,  color = "red", linewidth = 0.5, fill = NA) +
+  geom_sf(data = Lsubocean, colour = "red", linewidth = 0.5, fill = NA) +
+  geom_sf(data = acsurv, colour = "blue", linewidth = 0.5, fill = NA) +
+
+  scale_x_continuous(name = "Longitude", breaks = seq(-59, -42, 4), expand = c(0,0)) +
+  scale_y_continuous(name = "Latitude", breaks = seq(46, 56, 4), expand = c(0,0)) +
+
+  annotation_scale(location = "br") +
+  annotation_north_arrow(location = "tr", which_north = "true", height = unit(0.7, "cm"), width = unit(0.7, "cm")) +
+  theme(legend.position = "none")
+
+ggsave(filename = "map.tiff", device = "tiff", plot = map, path = "./Figures",
+       dpi = 300, width = 5, height = 5, units = "in")
+
 ```
@@
 ```{r}
-acc_surv <- read.csv("./Data/Capelin_AccSurv.csv") %>% 
-  filter(Year > 1980 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)
+eng_ac_surv <- read.csv("./Data/Capelin_AccSurv_85-2024.csv") %>% 
+  filter(year > 1980 & year < 1996)
 
 ## Survey year proper
-p1 <- ggplot(data = acc_surv) +
-  geom_line(aes(x = Year, y = acsurv_bm), colour = "#BB2D05", linewidth = 1) +
-  geom_point(aes(x = Year, y = acsurv_bm), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
-  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1981,1995.1), breaks = c(seq(1981,1995, 3))) + 
-  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.009,0), limits = c(0,6000)) +
-  ggtitle("Engel\na) Spring") +
+p1 <- ggplot(data = eng_ac_surv) +
+  geom_line(aes(x = year, y = biomass_med), colour = "#BB2D05", linewidth = 1) +
+  geom_point(aes(x = year, y = biomass_med), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
+
+  geom_errorbar(aes(x = year, y = biomass_med, ymin = bm_lci, ymax = bm_uci), colour = "#BB2D05", width = 0.2) +
+
+  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
+  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.02,0), limits = c(0,9000)) +
+  ggtitle("Engel Timeseries\na) 3L Spring") +
   theme_classic() +
   theme(legend.position = "none",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.line.x = element_line(size = 0.7), axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"), 
+        axis.line.x = element_line(size = 0.5), 
+        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
         plot.title = element_text(size = 16, face = "bold"))
+
 ```
@@
 ```{r}
-# acc_surv <- read.csv("./Data/Capelin_AccSurv.csv") %>% filter(Year > 1980) %>% rename(acsurv_bm = names(Capelin_AccSurv)[2])
-acc_surv <- read.csv("./Data/Capelin_AccSurv.csv") %>% 
-  filter(Year > 1994) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)
+camp_ac_surv <- read.csv("./Data/Capelin_AccSurv_85-2024.csv") %>% 
+  filter(year > 1994)
 
 ## Survey year proper
-p2 <- ggplot(data = acc_surv) +
-  geom_line(aes(x = Year, y = acsurv_bm), colour = "#BB2D05", linewidth = 1) +
-  geom_point(aes(x = Year, y = acsurv_bm), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
-  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1995, 2020.9), breaks = c(seq(1995, 2020, 5))) + 
-  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.009,0), limits = c(0, 1100)) +
-  ggtitle("Campelen\nb) Spring") +
+p2 <- ggplot(data = camp_ac_surv) +
+  geom_line(aes(x = year, y = biomass_med), colour = "#BB2D05", linewidth = 1) +
+  geom_point(aes(x = year, y = biomass_med), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
+
+  geom_errorbar(aes(x = year, y = biomass_med, ymin = bm_lci, ymax = bm_uci), colour = "#BB2D05", width = 0.2) +
+
+  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1994.9,2022.1), breaks = c(seq(1995, 2022, 5))) +
+  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.02,0), limits = c(0, 1100)) +
+  ggtitle("Campelen Timeseries\nb) 3L Spring") +
   theme_classic() +
   theme(legend.position = "none",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.line.x = element_line(size = 0.7), axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"), 
+        axis.line.x = element_line(size = 0.5), 
+        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
         plot.title = element_text(size = 16, face = "bold"))
@@
 ```{r}
-load(file = "./ModelSaves/ACAP-SprEng_Length.RData")
-load(file = "./ModelSaves/GH-SprEng_Length.RData")
+load(file = "./ModelSaves/SprEng_Length.RData")
 
-# Set up index df - GH
-gh_data <- gh_fishy_dat
-gh_uni_names <- unique(gh_data$names)
-gh_dat_names <- c("Index", gh_uni_names)
-
-gh_new_list <- list()
-for(i in 1:length(gh_uni_names)){
-  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
-  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-gh_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  gh_new_list
-)
-
-# Set up index df - AC
-ac_data <- ac_fishy_dat
-ac_uni_names <- unique(ac_data$names)
-ac_dat_names <- c("Index", ac_uni_names)
-
-ac_new_list <- list()
-for(i in 1:length(ac_uni_names)){
-  ac_one_dex <- subset(ac_data, names == ac_uni_names[i])
-  ac_new_list[[i]] <- aggregate(ac_one_dex$pa, by = list(ac_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-ac_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  ac_new_list
-)
-
-gh_low_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] - qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
-gh_high_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] + qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
-gh_ts_df <- data.frame(ts = gh_rep$iye, time = gh_multi_inner[,1], low_sd = gh_low_rho, high_sd = gh_high_rho)
-
-ac_low_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] - qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
-ac_high_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] + qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
-ac_ts_df <- data.frame(ts = ac_rep$iye, time = ac_multi_inner[,1], low_sd = ac_low_rho, high_sd = ac_high_rho)
+# Confidence intervals
+low_rho = sdrep$value[names(sdrep$value) == "iye"] - qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
+high_rho = sdrep$value[names(sdrep$value) == "iye"] + qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
+ts_df <- data.frame(ts = rep$iye, year = sort(unique(fishy_dat$year)), low_sd = low_rho, high_sd = high_rho)
 
@@
 
-  geom_ribbon(data = gh_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
-  geom_point(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
+  geom_ribbon(data = ts_df, aes(x = year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
+  geom_line(data = ts_df, aes(x = year, y = ts, colour = "all" ), linewidth = 1.5) +
+  geom_point(data = ts_df, aes(x = year, y = ts, colour = "all"), size = 1.5) +
 
-  geom_ribbon(data = ac_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = ac_ts_df, aes(x = time, y = ts, colour = "ac"), size = 1.5) +
-  geom_point(data = ac_ts_df, aes(x = time, y = ts, colour = "ac"), size = 1.5) +
+  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
+  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.3,2.0)) +
+  scale_color_manual(name = "Species Model", values = c(all = "black"), labels = c(all = "All species")) +
+  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
 
-  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1981,1995), breaks = c(seq(1981, 1995, 3))) + 
-  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.3,2.0)) +
-  scale_color_manual(name = "Species Model", values = c(ac = "#BC8DA0", gh = "#048BA8"),
-                     labels = c(ac = "Cod/ Plaice", gh = "Greenland halibut")) +
-  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
-  ggtitle("c) Spring") +
+  ggtitle("c) 3L Spring") +
   theme_classic() +
@@
         legend.position = "none",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
+        axis.line.x = element_line(size = 0.5), 
+        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
         plot.title = element_text(size = 16, face = "bold"))
+
 ```
@@
 
-# Set up index df - GH
-gh_data <- gh_fishy_dat
-gh_uni_names <- unique(gh_data$names)
-gh_dat_names <- c("Index", gh_uni_names)
-
-gh_new_list <- list()
-for(i in 1:length(gh_uni_names)){
-  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
-  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-gh_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  gh_new_list
-)
-
-# Set up index df - AC
-ac_data <- ac_fishy_dat
-ac_uni_names <- unique(ac_data$names)
-ac_dat_names <- c("Index", ac_uni_names)
-
-ac_new_list <- list()
-for(i in 1:length(ac_uni_names)){
-  ac_one_dex <- subset(ac_data, names == ac_uni_names[i])
-  ac_new_list[[i]] <- aggregate(ac_one_dex$pa, by = list(ac_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-ac_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  ac_new_list
-)
-
+# Confidence intervals for Greenland halibut model
 gh_low_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] - qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
 gh_high_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] + qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
-gh_ts_df <- data.frame(ts = gh_rep$iye, time = gh_multi_inner[,1], low_sd = gh_low_rho, high_sd = gh_high_rho) %>% 
-  mutate(acc_year = gh_multi_inner[,1]+1)
+gh_ts_df <- data.frame(ts = gh_rep$iye, time = sort(unique(gh_fishy_dat$year)), low_sd = gh_low_rho, high_sd = gh_high_rho) %>% 
+  mutate(acc_year = sort(unique(gh_fishy_dat$year))+1) # since comparing fall to next year spring, lagged to year+1
 
+# Confidence intervals for Atlantic cod/American plaice model
 ac_low_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] - qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
 ac_high_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] + qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
-ac_ts_df <- data.frame(ts = ac_rep$iye, time = ac_multi_inner[,1], low_sd = ac_low_rho, high_sd = ac_high_rho) %>% 
-  mutate(acc_year = ac_multi_inner[,1]+1)
+ac_ts_df <- data.frame(ts = ac_rep$iye, time = sort(unique(ac_fishy_dat$year)), low_sd = ac_low_rho, high_sd = ac_high_rho) %>% 
+  mutate(acc_year = sort(unique(ac_fishy_dat$year))+1) # since comparing fall to next year spring, lagged to year+1
 
@@
   geom_ribbon(data = gh_ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = gh_ts_df, aes(x = acc_year, y = ts, colour = "gh"), size = 1.5) +
+  geom_line(data = gh_ts_df, aes(x = acc_year, y = ts, colour = "gh"), linewidth = 1.5) +
   geom_point(data = gh_ts_df, aes(x = acc_year, y = ts, colour = "gh"), size = 1.5) +
@@
   geom_ribbon(data = ac_ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = ac_ts_df, aes(x = acc_year, y = ts, colour = "ac"), size = 1.5) +
+  geom_line(data = ac_ts_df, aes(x = acc_year, y = ts, colour = "ac"), linewidth = 1.5) +
   geom_point(data = ac_ts_df, aes(x = acc_year, y = ts, colour = "ac"), size = 1.5) +
 
-  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1981,1995), breaks = c(seq(1981, 1995, 3))) + 
-  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.21,0.75)) +
+  scale_x_continuous(name = "Year+1", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
+  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.24,0.8)) +
   scale_color_manual(name = "Species Model", 
@@
   guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
-  ggtitle("e) Fall") +
+
+  ggtitle("e) 2J3KL Fall") +
   theme_classic() +
@@
         legend.position = "none",
-        legend.text = element_text(size = 11), legend.title = element_text(size = 16, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
+        axis.line.x = element_line(size = 0.5), 
+        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
         plot.title = element_text(size = 16, face = "bold"))
@@
 ```{r}
-load(file = "./ModelSaves/AP-SprCamp_Length.RData")
-load(file = "./ModelSaves/GH-SprCamp_Length.RData")
+load(file = "./ModelSaves/ACAP-SprCamp_Base.RData")
+load(file = "./ModelSaves/GH-SprCamp_Base.RData")
 
-# Set up index df - GH
-gh_data <- gh_fishy_dat
-gh_uni_names <- unique(gh_data$names)
-gh_dat_names <- c("Index", gh_uni_names)
-
-gh_new_list <- list()
-for(i in 1:length(gh_uni_names)){
-  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
-  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-gh_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  gh_new_list
-)
-
-# Set up index df - AC
-ap_data <- ap_fishy_dat
-ap_uni_names <- unique(ap_data$names)
-ap_dat_names <- c("Index", ap_uni_names)
-
-ap_new_list <- list()
-for(i in 1:length(ap_uni_names)){
-  ap_one_dex <- subset(ap_data, names == ap_uni_names[i])
-  ap_new_list[[i]] <- aggregate(ap_one_dex$pa, by = list(ap_one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-ap_multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  ap_new_list
-)
-
+# Confidence intervals for Greenland halibut model
 gh_low_rho = gh_sdrep$value[names(gh_sdrep$value) == "iye"] - qnorm(0.975)*gh_sdrep$sd[names(gh_sdrep$value) == "iye"]
@@
 
-ap_low_rho = ap_sdrep$value[names(ap_sdrep$value) == "iye"] - qnorm(0.975)*ap_sdrep$sd[names(ap_sdrep$value) == "iye"]
-ap_high_rho = ap_sdrep$value[names(ap_sdrep$value) == "iye"] + qnorm(0.975)*ap_sdrep$sd[names(ap_sdrep$value) == "iye"]
-ap_ts_df <- data.frame(ts = ap_rep$iye, time = ap_multi_inner[,1], low_sd = ap_low_rho, high_sd = ap_high_rho)
+# Confidence intervals for Atlantic cod/American plaice model
+ac_low_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] - qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
+ac_high_rho = ac_sdrep$value[names(ac_sdrep$value) == "iye"] + qnorm(0.975)*ac_sdrep$sd[names(ac_sdrep$value) == "iye"]
+ac_ts_df <- data.frame(ts = ac_rep$iye, time = ac_multi_inner[,1], low_sd = ac_low_rho, high_sd = ac_high_rho)
 
 p5 <- ggplot() +
-  geom_line(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
+  # Taking common legend from this plot, have to make stand-in lines
+  geom_line(aes(x = 0, y = 0, colour = "all"), linewidth = 1.5) +
   geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
-
-  geom_line(aes(x = 0, y = 0, colour = "ac"), size = 1.5) +
+  geom_line(aes(x = 0, y = 0, colour = "ac"), linewidth = 1.5) +
   geom_point(aes(x = 0, y = 0, colour = "ac"), size = 1.5) +
-
-  geom_line(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
+  geom_line(aes(x = 0, y = 0, colour = "surv"), linewidth = 1.5) +
   geom_point(aes(x = 0, y = 0, colour = "surv"), size = 1.5) +
@@
   geom_ribbon(data = gh_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
+  geom_line(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), linewidth = 1.5) +
   geom_point(data = gh_ts_df, aes(x = time, y = ts, colour = "gh"), size = 1.5) +
 
-  geom_ribbon(data = ap_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_line(data = ap_ts_df, aes(x = time, y = ts, colour = "ap"), size = 1.5) +
-  geom_point(data = ap_ts_df, aes(x = time, y = ts, colour = "ap"), size = 1.5) +
+  geom_ribbon(data = ac_ts_df, aes(x = time, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
+  geom_line(data = ac_ts_df, aes(x = time, y = ts, colour = "ac"), linewidth = 1.5) +
+  geom_point(data = ac_ts_df, aes(x = time, y = ts, colour = "ac"), size = 1.5) +
 
-  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1995,2021), breaks = c(seq(1995, 2021, 5))) + 
-  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.6,2.4)) +
+  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1994.9,2022), breaks = c(seq(1995, 2022, 5))) + 
+  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.59, 2.2)) +
   scale_color_manual(name = "Species Model",
@@
   guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
-  ggtitle("d) Spring") +
+
+  ggtitle("d) 3L Spring") +
   theme_classic() +
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
-        # legend.position = "none",
-        legend.text = element_text(size = 13), legend.title = element_text(size = 15, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
+        legend.text = element_text(size = 15), legend.title = element_text(size = 16, face = "bold"), legend.spacing.x = unit(0,'cm'),
+        axis.line.x = element_line(size = 0.5), 
+        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
         plot.title = element_text(size = 16, face = "bold"))
@@
 
-data <- fishy_dat
-uni_names <- unique(data$names)
-dat_names <- c("Index", uni_names)
-
-new_list <- list()
-for(i in 1:length(uni_names)){
-  one_dex <- subset(data, names == uni_names[i])
-  new_list[[i]] <- aggregate(one_dex$pa, by = list(one_dex$year), FUN = mean, na.rm = TRUE)
-}
-
-multi_inner <- Reduce(
-  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
-  new_list)
-
 # Confidence intervals
@@
 high_rho = sdrep$value[names(sdrep$value) == "iye"] + qnorm(0.975)*sdrep$sd[names(sdrep$value) == "iye"]
-ts_df <- data.frame(ts = rep$iye, year = multi_inner[,1], low_sd = low_rho, high_sd = high_rho) %>% mutate(acc_year = multi_inner[,1]+1)
+ts_df <- data.frame(ts = rep$iye, year = sort(unique(fishy_dat$year)), low_sd = low_rho, high_sd = high_rho) %>% 
+  mutate(acc_year = sort(unique(fishy_dat$year))+1) # since comparing fall to next year spring, lagged to year+1
 
@@
   geom_ribbon(data = ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
-  geom_point(data = ts_df, aes(x = acc_year, y = ts, colour = "all")) +
-  geom_line(data = ts_df, aes(x = acc_year, y = ts, colour = "all" ), size = 1.5) +
+  geom_line(data = ts_df, aes(x = acc_year, y = ts, colour = "all" ), linewidth = 1.5) +
+  geom_point(data = ts_df, aes(x = acc_year, y = ts, colour = "all"), size = 1.5) +
 
-  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1995,2022), breaks = c(seq(1995, 2022, 5))) + 
+  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1994.9,2022), breaks = c(seq(1995, 2022, 5))) + 
   scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.45, 1.08)) +
-  scale_color_manual(name = "Species Model", values = c(all = "black"),
-                     labels = c(all = "All species")) +
+  scale_color_manual(name = "Species Model", values = c(all = "black"), labels = c(all = "All species")) +
   guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
-  ggtitle("f) Fall") +
+
+  ggtitle("f) 2J3KL Fall") +
   theme_classic() +
@@
         legend.position = "none",
-        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
-        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
+        axis.line.x = element_line(size = 0.5), 
+        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
         plot.title = element_text(size = 16, face = "bold"))
 ```
-
-## - Figure 2
-
-```{r, fig.width = 16, fig.height=13}
-
+## - Figure 3
+```{r, fig.width = 16, fig.height=14}
 p7 <- ggarrange(p1+theme(axis.title.x = element_blank()),
@@
 ggsave(filename = "abundancefull.tiff", device = "tiff", plot = p7, path = "./Figures",
-       dpi = 300, width = 16, height = 13, units = "in")
+       dpi = 300, width = 16, height = 14, units = "in")
 ```
@@
 
-## Campelen
+## Engel
 
-### Fall
+### Spring
+Spring NLFPM estimates are representative of the same year's acoustic survey biomass estimates.
 
+Spring NLFPM: 1984-1995
+Spring acoustic: 1985-1996
+
+Correlation range: 1985-1995
 ```{r}
-load(file = "./ModelSaves/FallCamp_Length.RData")
-acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
-  filter(Year > 1994) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)
+load(file = "./ModelSaves/SprEng_Length.RData")
+
+eng_ac_surv <- read.csv("./Data/Capelin_AccSurv_85-2024.csv") %>% 
+  filter(year > 1980 & year < 1997)
+
+sort(unique(fishy_dat$year))[2:12]
+unique(eng_ac_surv$year)[1:11]
 
 # Set up relationship data frame
-lr_dat <- data.frame(year = acc_surv[2:28,1], acc_bm = acc_surv[2:28,2], NLFPM_bm = rep$iye) #have to go y+1
+lr_dat <- data.frame(year = as.factor(seq(1985,1995,1)), 
+                     acc_bm = eng_ac_surv$biomass_med[1:11], 
+                     NLFPM_bm = rep$iye[2:12])
 
-# Linear relationship 
-fit <- lm(acc_bm~NLFPM_bm, data = lr_dat)
-cor.test(x = lr_dat$NLFPM_bm, y = lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated 
-lr_dat <- na.omit(lr_dat)
-
-p8 <- ggplot(data = lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
-
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
-  ggtitle("Campelen\na) Fall 2J3KL All Speices") +
-  theme_classic() +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-    legend.position = "none",
-    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
-    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
+# Spearman correlation
+cor.test(x = lr_dat$NLFPM_bm, y = lr_dat$acc_bm, method = "spearman")
 
@@
 
-### Spring
+### Fall
+Fall NLFPM estimates are representative of the following year's acoustic survey biomass estimates.
 
-```{r}
-load(file = "./ModelSaves/AP-SprCamp_Length.RData")
-load(file = "./ModelSaves/GH-SprCamp_Length.RData")
+Fall NLFPM: 1984-1994
+Spring acoustic: 1985-1995
 
-acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
-  filter(Year > 1994) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)
-
-# Set up relationship data frame - ACAP
-ap_lr_dat <- data.frame(year = acc_surv[2:25,1], acc_bm = acc_surv[2:25,2], NLFPM_bm = ap_rep$iye)
-
-# This doesnt change corelation coefficient 
-ap_lr_dat <- data.frame(year = c(acc_surv[2:18,1], acc_surv[21:25,1]), acc_bm = c(acc_surv[2:18,2], acc_surv[21:25,2]), 
-                        NLFPM_bm = c(ap_rep$iye[2:18],ap_rep$iye[21:25]))
-
-# Linear relationship 
-fit <- lm(acc_bm~NLFPM_bm, data = ap_lr_dat) # thought is: can NLFPM predict acoustic survey accurately
-cor.test(x = ap_lr_dat$NLFPM_bm, y = ap_lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated
-
-ap_lr_dat <- na.omit(ap_lr_dat)
-
-p9 <- ggplot(data = ap_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
-
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
-  ggtitle(" \nb) Spring 3L Plaice") +
-  theme_classic() +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-    legend.position = 'none',
-    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
-    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
-
-# Set up relationship data frame - GH
-gh_lr_dat <- data.frame(year = acc_surv[2:25,1], acc_bm = acc_surv[2:25,2], NLFPM_bm = gh_rep$iye)
-
-# This does change the correlation coefficient
-gh_lr_dat <- data.frame(year = c(acc_surv[2:18,1], acc_surv[21:25,1]), acc_bm = c(acc_surv[2:18,2], acc_surv[21:25,2]), 
-                        NLFPM_bm = c(gh_rep$iye[2:18],gh_rep$iye[21:25]))
-
-# Linear relationship 
-fit <- lm(acc_bm~NLFPM_bm, data = gh_lr_dat) # thought is: can NLFPM predict acoustic survey accurately
-cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated
-
-gh_lr_dat <- na.omit(gh_lr_dat)
-
-p10 <- ggplot(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
-
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
-  theme_classic() +
-  ggtitle(" \nc) Spring 3L Halibut") +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-        legend.position = 'none',
-        legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
-        axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
-
-```
-
-## Engel
-
-### Fall
-
+Correlation range: 1985-1995
 ```{r}
@@
 
-acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
-  filter(Year > 1980 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)
+eng_ac_surv <- read.csv("./Data/Capelin_AccSurv_85-2024.csv") %>% 
+  filter(year > 1980 & year < 1996)
+
+unique(ac_fishy_dat$year)
+unique(eng_ac_surv$year)
 
 # Set up relationship data frame - ACAP
-ac_lr_dat <- data.frame(year = acc_surv[2:15,1], acc_bm = acc_surv[2:15,2], NLFPM_bm = ac_rep$iye) #have to y+1
+ac_lr_dat <- data.frame(year = as.factor(seq(1985,1995,1)),
+                        acc_bm = eng_ac_surv$biomass_med, 
+                        NLFPM_bm = ac_rep$iye)
 
-# Linear relationship 
-fit <- lm(acc_bm~NLFPM_bm, data = ac_lr_dat) # thought is: can NLFPM predict acoustic survey accurately
-cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated
-
-ac_lr_dat <- na.omit(ac_lr_dat)
-
-p11 <- ggplot(data = ac_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
-
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1981,1995), midpoint = 1987,  low = "blue", mid = "#FFAEFF", high = "red") +
-  ggtitle("Engel\nd) Fall 2J3KL Cod/Plaice") +
-  theme_classic() +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-    legend.position = 'none',
-    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
-    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
+# Spearman correlation
+cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "spearman")
 
 # Set up relationship data frame - GH
-gh_lr_dat <- data.frame(year = acc_surv[2:15,1], acc_bm = acc_surv[2:15,2], NLFPM_bm = gh_rep$iye)
+unique(gh_fishy_dat$year)
 
-# Linear relationship 
-fit <- lm(acc_bm~NLFPM_bm, data = gh_lr_dat) # thought is: can NLFPM predict acoustic survey accurately
-cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated
+gh_lr_dat <- data.frame(year = as.factor(seq(1985,1995,1)), 
+                        acc_bm = eng_ac_surv$biomass_med, 
+                        NLFPM_bm = gh_rep$iye)
 
-gh_lr_dat <- na.omit(gh_lr_dat)
-
-p12 <- ggplot(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
-
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1981,1995), midpoint = 1987,  low = "blue", mid = "#FFAEFF", high = "red") +
-  theme_classic() +
-  ggtitle(" \ne) Fall 2J3KL Halibut") +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-    legend.position = 'none',
-    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
-    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
+# Spearman correlation
+cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "spearman")
 
@@
 
+## Campelen
+
 ### Spring
+Spring NLFPM year is acoustic survey year.
 
+Spring NLFPM: 1996-2019
+Spring acoustic: 1995-2024
+
+Correlation range:
 ```{r}
-load(file = "./ModelSaves/ACAP-SprEng_Length.RData")
-load(file = "./ModelSaves/GH-SprEng_Length.RData")
+load(file = "./ModelSaves/ACAP-SprCamp_Base.RData")
+load(file = "./ModelSaves/GH-SprCamp_Base.RData")
 
-acc_surv <- read.csv("./Data/Capelin_AccSurv.csv")[1:2] %>% 
-  filter(Year > 1983 & Year < 1996) %>% rename(acsurv_bm = X3L.Spring..Acoustic.Capelin.Biomass..kt.)
+camp_ac_surv <- read.csv("./Data/Capelin_AccSurv_85-2024.csv") %>% 
+  filter(year > 1994)
 
-# Set up relationship data frame - ACAP
-ac_lr_dat <- data.frame(year = acc_surv[2:13,1], acc_bm = acc_surv[2:13,2], NLFPM_bm = c(ac_rep$iye[12], ac_rep$iye[1:11])) #have to y+1
+unique(ac_fishy_dat$year)
+unique(camp_ac_surv$year)
 
-# Linear relationship 
-fit <- lm(acc_bm~NLFPM_bm, data = ac_lr_dat) # thought is: can NLFPM predict acoustic survey accurately
-cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated
+# Set up relationship data frame - ACAP, yr = yr
+ac_lr_dat <- data.frame(year = as.factor(seq(1996,2019,1)), 
+                        acc_bm = camp_ac_surv$biomass_med[2:25], 
+                        NLFPM_bm = ac_rep$iye)
 
-ac_lr_dat <- na.omit(ac_lr_dat)
+# Spearman correlation
+cor.test(x = ac_lr_dat$NLFPM_bm, y = ac_lr_dat$acc_bm, method = "spearman")
 
-p13 <- ggplot(data = ac_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
+# Set up relationship data frame - GH, yr = yr
+unique(gh_fishy_dat$year)
+gh_lr_dat <- data.frame(year = as.factor(seq(1996,2019,1)), 
+                        acc_bm = camp_ac_surv$biomass_med[2:25], 
+                        NLFPM_bm = gh_rep$iye)
 
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
-  ggtitle("\nf) Spring 3L Cod/Plaice") +
-  theme_classic() +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-    legend.position = 'none',
-    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
-    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
+# Spearman correlation
+cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "spearman")
 
-# Set up relationship data frame - GH
-gh_lr_dat <- data.frame(year = acc_surv[2:13,1], acc_bm = acc_surv[2:13,2], NLFPM_bm = c(gh_rep$iye[12], gh_rep$iye[1:11]))
-
-# Linear relationship 
-fit <- lm(acc_bm~NLFPM_bm, data = gh_lr_dat) # thought is: can NLFPM predict acoustic survey accurately
-cor.test(x = gh_lr_dat$NLFPM_bm, y = gh_lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated
-
-gh_lr_dat <- na.omit(gh_lr_dat)
-
-p14 <- ggplot(data = gh_lr_dat, aes(x = NLFPM_bm, y = acc_bm)) +
-  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
-  geom_point(aes(colour = year), size = 1.5) +
-
-  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
-  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
-  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
-  theme_classic() +
-  ggtitle(" \ng) Spring 3L Halibut") +
-  theme(
-    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
-    legend.position = 'none',
-    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
-    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
-    plot.title = element_text(size = 13, face = "bold"))
 ```
 
-## - Figure 3
+### Fall
+Fall NLFPM estimates are representative of the following year's acoustic survey biomass estimates.
 
-```{r, fig.width=14, fig.height=8}
-p0 <- ggplot() +
-  geom_point(aes(x = 0, y = 0, colour = "white"), size = 1.5)+
-  scale_x_continuous(limits = c(0.1,1))+
-  theme_classic()
+Fall NLFPM: 1995-2020
+Spring acoustic: 1995-2024
 
-p15 <- ggarrange(p8+theme(axis.title.x = element_blank()),
-          p9+theme(axis.title.x = element_blank(),axis.title.y = element_blank()),
-          p10+theme(axis.title.x = element_blank(),axis.title.y = element_blank()),
-          p0+theme(text = element_blank(), title = element_blank(), line = element_blank()),
-          nrow = 1, ncol = 4,
-          align = "v", legend = "right", common.legend = T)
+Correlation range: 1996-2021
+```{r}
+load(file = "./ModelSaves/FallCamp_Length.RData")
 
-p16 <- ggarrange(p11,
-          p12+theme(axis.title.y = element_blank()),
-          p13+theme(axis.title.y = element_blank()),
-          p14+theme(axis.title.y = element_blank()),
-          nrow = 1, ncol = 4,
-          align = "hv", legend = "right", common.legend = T)
+camp_ac_surv <- read.csv("./Data/Capelin_AccSurv_85-2024.csv") %>% 
+  filter(year > 1994)
 
-p17 <- ggarrange(p15,p16,
-          nrow = 2, ncol = 1, align = "v")
+unique(fishy_dat$year)
+unique(camp_ac_surv$year)
 
-ggsave(filename = "survcomp.tiff", device = "tiff", plot = p17, path = "./Figures",
-       dpi = 300, width = 16, height = 8, units = "in")
+# Set up relationship data frame
+lr_dat <- data.frame(year = as.factor(seq(1996, 2021,1)), 
+                     acc_bm = camp_ac_surv$biomass_med[2:27], 
+                     NLFPM_bm = rep$iye)
+
+# Spearman correlation
+cor.test(x = lr_dat$NLFPM_bm, y = lr_dat$acc_bm, method = "spearman")
+
 ```
+
+# y Timeseries comparison
+
+## Engel
+spring range: 1984-1995
+AC fall range: 1984-1994
+GH fall range: 1984-1994
+
+Correlation ranging from 1985-1995
+```{r}
+load(file = "./ModelSaves/SprEng_Length.RData")
+load(file = "./ModelSaves/ACAP-FallEng_Length.RData")
+load(file = "./ModelSaves/GH-FallEng_Length.RData")
+
+# Look at year range
+sort(unique(fishy_dat$year))
+unique(ac_fishy_dat$year)
+unique(gh_fishy_dat$year)
+
+# Set up relationship data frame
+lr_dat <- data.frame(year = as.factor(seq(1985,1995,1)), 
+                     SE = rep$iye[2:12],
+                     FEACAP = ac_rep$iye,
+                     FEGH = gh_rep$iye)
+
+# ACAP
+# Spearman correlation
+cor.test(x = lr_dat$FEACAP, y = lr_dat$SE, method = "spearman")
+
+ # GH
+# Spearman correlation
+cor.test(x = lr_dat$FEGH, y = lr_dat$SE, method = "spearman")
+
+```
+
+## Campelen
+fall range: 1995-2020
+acap spring range: 1996-2019
+gh spring range: 1996-2019
+
+Correlation ranging from 1996-2019
+```{r}
+load(file = "./ModelSaves/FallCamp_Length.RData")
+load(file = "./ModelSaves/ACAP-SprCamp_Base.RData")
+load(file = "./ModelSaves/GH-SprCamp_Base.RData")
+
+# Look at year range
+unique(fishy_dat$year) # this will have to be lagged +1 yr
+unique(ac_fishy_dat$year)
+unique(gh_fishy_dat$year)
+
+# Set up relationship data frame
+lr_dat <- data.frame(year = as.factor(seq(1996,2019,1)), 
+                     FC = rep$iye[1:24], 
+                     SCACAP = ac_rep$iye, 
+                     SCGH = gh_rep$iye)
+
+# ACAP
+# Spearman correlation
+cor.test(x = lr_dat$FC, y = lr_dat$SCACAP, method = "spearman")
+
+# GH
+# Spearman correlation
+cor.test(x = lr_dat$FC, y = lr_dat$SCGH, method = "spearman")
+
+```
+
+# y+1 Timeseries comparison
+
+## Engel
+spring range: 1984-1995
+AC fall range: 1984-1994
+GH fall range: 1984-1994
+
+Correlation ranging from 1984-1994
+```{r}
+load(file = "./ModelSaves/SprEng_Length.RData")
+load(file = "./ModelSaves/ACAP-FallEng_Length.RData")
+load(file = "./ModelSaves/GH-FallEng_Length.RData")
+
+# Look at year range
+sort(unique(fishy_dat$year))
+unique(ac_fishy_dat$year)
+unique(gh_fishy_dat$year)
+
+# Set up relationship data frame
+lr_dat <- data.frame(year = as.factor(seq(1984,1994,1)), 
+                     SE = rep$iye[1:11],
+                     FEACAP = ac_rep$iye,
+                     FEGH = gh_rep$iye)
+
+# ACAP
+# Spearman correlation
+cor.test(x = lr_dat$FEACAP, y = lr_dat$SE, method = "spearman")
+
+# GH
+# Spearman correlation
+cor.test(x = lr_dat$FEGH, y = lr_dat$SE, method = "spearman")
+
+```
+
+## Campelen
+fall range: 1995-2020
+acap spring range: 1996-2019
+gh spring range: 1996-2019
+
+Correlation ranging from 1996-2019
+```{r}
+load(file = "./ModelSaves/FallCamp_Length.RData")
+load(file = "./ModelSaves/ACAP-SprCamp_Base.RData")
+load(file = "./ModelSaves/GH-SprCamp_Base.RData")
+
+# Look at year range
+unique(fishy_dat$year)[2:25]
+unique(ac_fishy_dat$year)
+unique(gh_fishy_dat$year)
+
+# Set up relationship data frame
+lr_dat <- data.frame(year = as.factor(seq(1996,2019,1)), 
+                     FC = rep$iye[2:25], 
+                     SCACAP = ac_rep$iye, 
+                     SCGH = gh_rep$iye)
+
+# ACAP
+# Spearman correlation
+cor.test(x = lr_dat$FC, y = lr_dat$SCACAP, method = "spearman")
+
+# GH
+# Spearman correlation
+cor.test(x = lr_dat$FC, y = lr_dat$SCGH, method = "spearman")
+
+```

### 2025-05-08 SuppSections.Rmd
To match manuscript version 23.04.2025

---
output: html_document
editor_options: 
  chunk_output_type: inline
---
# Setup Env

```{r include=FALSE}
library(tidyverse)
library(cowplot)
library(ggpubr)
library(glmmTMB)
```

# Data removed maps

## Engel

### Spring

```{r}
source("./Analysis/Engel/Spring/SprEng-SetUp.R")

capelin_catch_raster <- terra::as.data.frame(mean_catch, xy = TRUE)

# ggplot(capelin_catch_raster, aes(x = x, y = y, fill = pa))+
#   geom_raster() +
#   scale_fill_viridis_c() +
#   labs(title = "Proportion of Capelin catches")

capelin_catch_raster <- capelin_catch_raster %>%  mutate(color_category = ifelse(pa == 0, "Zero", "Non-Zero"))

# ggplot(capelin_catch_raster, aes(x = x, y = y, fill = pa))+
#   geom_raster() +
#   scale_fill_viridis_c() +
#   labs(title = "Proportion of Capelin catches")

pMSE <- ggplot() +
  geom_tile(data = filter(capelin_catch_raster, color_category == "Zero"), aes(x = x, y = y), fill = "grey80") +
  geom_tile(data = filter(capelin_catch_raster, color_category == "Non-Zero"), aes(x = x, y = y, fill = pa)) +

  scale_x_continuous(name = "Longitude", limits = c(-59, -45), breaks = c(seq(-59, -42, 4)), expand = c(0,0)) +
  scale_y_continuous(name = "Latitude", limits = c(45, 56), breaks = c(seq(46, 56, 4)), expand = c(0,0)) +
  scale_fill_viridis_c(name = "Proportion of \ncapelin catches", limits = c(0,1)) +
  ggtitle("Engel\na) 3L Spring ") +

  theme_minimal() +
  theme(legend.position = "none", title = element_text(size = 15, face = "bold"),
        axis.title.x = element_blank(), axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"))

```

### Fall

```{r}

source("./Analysis/Engel/Fall/FallEng-SetUp.R")

capelin_catch_raster <- terra::as.data.frame(mean_catch, xy = TRUE)

# ggplot(capelin_catch_raster, aes(x = x, y = y, fill = pa))+
#   geom_raster() +
#   scale_fill_viridis_c() +
#   labs(title = "Proportion of Capelin catches")

capelin_catch_raster <- capelin_catch_raster %>%  mutate(color_category = ifelse(pa == 0, "Zero", "Non-Zero"))

# ggplot(capelin_catch_raster, aes(x = x, y = y, fill = pa))+
#   geom_raster() +
#   scale_fill_viridis_c() +
#   labs(title = "Proportion of Capelin catches")

pMFE <- ggplot() +
  geom_tile(data = filter(capelin_catch_raster, color_category == "Zero"), aes(x = x, y = y), fill = "grey80") +
  geom_tile(data = filter(capelin_catch_raster, color_category == "Non-Zero"), aes(x = x, y = y, fill = pa)) +

  scale_x_continuous(name = "Longitude", limits = c(-59, -45), breaks = c(seq(-59, -42, 4)), expand = c(0,0)) +
  scale_y_continuous(name = "Latitude", limits = c(45, 56), breaks = c(seq(46, 56, 4)), expand = c(0,0)) +
  scale_fill_viridis_c(name = "Proportion of \ncapelin catches", limits = c(0,1)) +

  ggtitle("c) 2J3KL Fall") +
  theme_minimal() +
  theme(legend.position = "none", title = element_text(size = 15, face = "bold"),

        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"))

```

## Campelen

### Spring

```{r}
source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")

capelin_catch_raster <- terra::as.data.frame(mean_catch, xy = TRUE)

# ggplot(capelin_catch_raster, aes(x = x, y = y, fill = pa))+
#   geom_raster() +
#   scale_fill_viridis_c() +
#   labs(title = "Proportion of Capelin catches")

capelin_catch_raster <- capelin_catch_raster %>%  mutate(color_category = ifelse(pa == 0, "Zero", "Non-Zero"))

# ggplot(capelin_catch_raster, aes(x = x, y = y, fill = pa))+
#   geom_raster() +
#   scale_fill_viridis_c() +
#   labs(title = "Proportion of Capelin catches")

pMSC <- ggplot() +
  geom_tile(data = filter(capelin_catch_raster, color_category == "Zero"), aes(x = x, y = y), fill = "grey80") +
  geom_tile(data = filter(capelin_catch_raster, color_category == "Non-Zero"), aes(x = x, y = y, fill = pa)) +

  scale_x_continuous(name = "Longitude", limits = c(-59, -45), breaks = c(seq(-59, -42, 4)), expand = c(0,0)) +
  scale_y_continuous(name = "Latitude", limits = c(45, 56), breaks = c(seq(46, 56, 4)), expand = c(0,0)) +
  scale_fill_viridis_c(name = "Proportion of \ncapelin catches", limits = c(0,1)) +

  ggtitle("Campelen\nb) 3L Spring") +

  theme_minimal() +
  theme(legend.position = "none", title = element_text(size = 15, face = "bold"),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"))

```

### Fall

```{r, fig.width=5, fig.height=6}

source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")

capelin_catch_raster <- terra::as.data.frame(mean_catch, xy = TRUE)

# ggplot(capelin_catch_raster, aes(x = x, y = y, fill = pa))+
#   geom_raster() +
#   scale_fill_viridis_c() +
#   labs(title = "Proportion of Capelin catches")

capelin_catch_raster <- capelin_catch_raster %>%  mutate(color_category = ifelse(pa == 0, "Zero", "Non-Zero"))

# ggplot(capelin_catch_raster, aes(x = x, y = y, fill = pa))+
#   geom_raster() +
#   scale_fill_viridis_c() +
#   labs(title = "Proportion of Capelin catches")

pMFC <- ggplot() +
  geom_tile(data = filter(capelin_catch_raster, color_category == "Zero"), aes(x = x, y = y), fill = "grey80") +
  geom_tile(data = filter(capelin_catch_raster, color_category == "Non-Zero"), aes(x = x, y = y, fill = pa)) +

  scale_x_continuous(name = "Longitude", limits = c(-59, -45), breaks = c(seq(-59, -42, 4)), expand = c(0,0)) +
  scale_y_continuous(name = "Latitude", limits = c(45, 56), breaks = c(seq(46, 56, 4)), expand = c(0,0)) +
  scale_fill_viridis_c(name = "Proportion of \ncapelin catches", limits = c(0,1)) +

  ggtitle("d) 2J3KL Fall") +

  theme_minimal() +
  theme(legend.position = "none", title = element_text(size = 15, face = "bold"),
        axis.title.y = element_blank(), axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"))

```

## - Figure 1
```{r, fig.width=10, fig.height=10}

pmaps <- ggpubr::ggarrange(pMSE,
                           pMSC,
                           pMFE,
                           pMFC,
                           nrow = 2, ncol = 2,
                           align = "v", common.legend = TRUE,
                           legend = "right", legend.grob = ggpubr::get_legend(pMSC+theme(legend.position = "right"))
)

ggsave(filename = "datamaps.tiff", device = "tiff", plot = pmaps, path = "./Figures",
       dpi = 300, width = 10, height = 10, units = "in")

```

# Sample size

## Engel

### Spring
```{r}
load(file = "./ModelSaves/Set_Up/SE-1995.RData")

acs1 <- AC_stos %>% filter(length > 17 & length <= 45)
acs2 <- AC_stos %>% filter(length > 45)
aps1 <- AP_stos %>% filter(length > 29)
ghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
ghs2 <- GH_stos %>% filter(length > 40)

acs0 <- AC_stos %>% filter(length < 18)
aps0 <- AP_stos %>% filter(length < 30)
ghs0 <- GH_stos %>% filter(length < 20)

# table(acs0$pa, acs0$year)
# table(acs1$pa, acs1$year)
# table(acs2$pa, acs2$year)
# table(aps0$pa, aps0$year)
# table(aps1$pa, aps1$year)
# table(ghs0$pa, ghs0$year)
# table(ghs1$pa, ghs1$year)
# table(ghs2$pa, ghs2$year)

Eacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1995)
Eacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 1995)
Eaps1 <- AP_stos %>% filter(length > 29)
Eghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
Eghs2 <- GH_stos %>% filter(length > 40)

Eacs0 <- AC_stos %>% filter(length < 18) %>% filter(year == 1982)
Eaps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 1984)
Eghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 1984)

```

### Fall
```{r}
load(file = "./ModelSaves/Set_Up/FE-1994.RData")

acf1 <- AC_stof %>% filter(length > 17 & length <= 45)
acf2 <- AC_stof %>% filter(length > 45)
apf1 <- AP_stof %>% filter(length > 29)
ghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
ghf2 <- GH_stof %>% filter(length > 40)

acf0 <- AC_stof %>% filter(length < 18)
apf0 <- AP_stof %>% filter(length < 30)
ghf0 <- GH_stof %>% filter(length < 20)

# table(acf0$pa, acf0$year)
# table(acf1$pa, acf1$year)
# table(acf2$pa, acf2$year)
# table(apf0$pa, apf0$year)
# table(apf1$pa, apf1$year)
# table(ghf0$pa, ghf0$year)
# table(ghf1$pa, ghf1$year)
# table(ghf2$pa, ghf2$year)

Eacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Eacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1994)
Eapf1 <- AP_stof %>% filter(length > 29)
Eghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Eghf2 <- GH_stof %>% filter(length > 40)

Eacf0 <- AC_stof %>% filter(length < 18) %>% filter(year == 1982 & year == 1983 & year == 1988)
Eapf0 <- AP_stof %>% filter(length < 30)
Eghf0 <- GH_stof %>% filter(length < 20)

```

### Total
```{r}
Eac0 <- rbind(acs0, acf0) %>% mutate(alt.name = "Atlantic cod")
Eac1 <- rbind(acs1, acf1) %>% mutate(alt.name = "Atlantic cod")
Eac2 <- rbind(acs2, acf2) %>% mutate(alt.name = "Atlantic cod")
Eap0 <- rbind(aps0, apf0) %>% mutate(alt.name = "American plaice")
Eap1 <- rbind(aps1, apf1) %>% mutate(alt.name = "American plaice")
Egh0 <- rbind(ghs0, ghf0) %>% mutate(alt.name = "Greenland halibut")
Egh1 <- rbind(ghs1, ghf1) %>% mutate(alt.name = "Greenland halibut")
Egh2 <- rbind(ghs2, ghf2) %>% mutate(alt.name = "Greenland halibut")

# table(Eac0$year, Eac0$season)
# table(Eac1$year, Eac1$season)
# table(Eac2$year, Eac2$season)
# table(Egh0$year, Egh0$season)
# table(Egh1$year, Egh1$season)
# table(Egh2$year, Egh2$season)
# table(Eap0$year, Eap0$season)
# table(Eap1$year, Eap1$season)

```

## Campelen

### Spring
```{r}
load(file = "./ModelSaves/Set_Up/SC-2019.RData")

acs1 <- AC_stos %>% filter(length > 17 & length <= 45)
acs2 <- AC_stos %>% filter(length > 45)
aps1 <- AP_stos %>% filter(length > 29)
ghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
ghs2 <- GH_stos %>% filter(length > 40)

acs0 <- AC_stos %>% filter(length < 18)
aps0 <- AP_stos %>% filter(length < 30)
ghs0 <- GH_stos %>% filter(length < 20)

# table(acs0$pa, acs0$year)
# table(acs1$pa, acs1$year)
# table(acs2$pa, acs2$year)
# table(aps0$pa, aps0$year)
# table(aps1$pa, aps1$year)
# table(ghs0$pa, ghs0$year)
# table(ghs1$pa, ghs1$year)
# table(ghs2$pa, ghs2$year)

Cacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1998 & year != 2017)
Cacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 2015)
Caps1 <- AP_stos %>% filter(length > 29) %>% filter(year != 2017)
Cghs1 <- GH_stos %>% filter(length > 19 & length <= 40) %>% filter(year != 2017)
Cghs2 <- GH_stos %>% filter(length > 40)

Cacs0 <- AC_stos %>% filter(length < 18) %>% filter(year != 1996 & year != 1998 & year != 1999 & year != 2006 & year != 2011 & year != 2017)
Caps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 2017)
Cghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 2015 & year != 2017)

```

### Fall
```{r}
# load rstrap set data
load(file = "./ModelSaves/Set_Up/FC-2020.RData")

acf1 <- AC_stof %>% filter(length > 17 & length <= 45)
acf2 <- AC_stof %>% filter(length > 45)
apf1 <- AP_stof %>% filter(length > 29)
ghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
ghf2 <- GH_stof %>% filter(length > 40)

acf0 <- AC_stof %>% filter(length < 18)
apf0 <- AP_stof %>% filter(length < 30)
ghf0 <- GH_stof %>% filter(length < 20)

# table(acf0$pa, acf0$year)
# table(acf1$pa, acf1$year)
# table(acf2$pa, acf2$year)
# table(apf0$pa, apf0$year)
# table(apf1$pa, apf1$year)
# table(ghf0$pa, ghf0$year)
# table(ghf1$pa, ghf1$year)
# table(ghf2$pa, ghf2$year)

Cacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
Cacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1995)
Capf1 <- AP_stof %>% filter(length > 29) %>% filter(year != 2014)
Cghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
Cghf2 <- GH_stof %>% filter(length > 40)

Cacf0 <- AC_stof %>% filter(length < 18) %>% filter(year != 2011 & year != 2020)
Capf0 <- AP_stof %>% filter(length < 30) %>% filter(year != 2014)
Cghf0 <- GH_stof %>% filter(length < 20)

```

### Total
```{r}

Cac0 <- rbind(Cacs0, Cacf0) %>% mutate(alt.name = "Atlantic cod")
Cac1 <- rbind(Cacs1, Cacf1) %>% mutate(alt.name = "Atlantic cod")
Cac2 <- rbind(Cacs2, Cacf2) %>% mutate(alt.name = "Atlantic cod")
Cap0 <- rbind(Caps0, Capf0) %>% mutate(alt.name = "American plaice")
Cap1 <- rbind(Caps1, Capf1) %>% mutate(alt.name = "American plaice")
Cgh0 <- rbind(Cghs0, Cghf0) %>% mutate(alt.name = "Greenland halibut")
Cgh1 <- rbind(Cghs1, Cghf1) %>% mutate(alt.name = "Greenland halibut")
Cgh2 <- rbind(Cghs2, Cghf2) %>% mutate(alt.name = "Greenland halibut")

```

## All data
```{r}
# Combine seasonal data for
## Engel
Eac0 <- rbind(Eacs0, Eacf0) %>% mutate(alt.name = "Atlantic cod")
Eac1 <- rbind(Eacs1, Eacf1) %>% mutate(alt.name = "Atlantic cod")
Eac2 <- rbind(Eacs2, Eacf2) %>% mutate(alt.name = "Atlantic cod")

Eap0 <- rbind(Eaps0, Eapf0) %>% mutate(alt.name = "American plaice")
Eap1 <- rbind(Eaps1, Eapf1) %>% mutate(alt.name = "American plaice")

Egh0 <- rbind(Eghs0, Eghf0) %>% mutate(alt.name = "Greenland halibut")
Egh1 <- rbind(Eghs1, Eghf1) %>% mutate(alt.name = "Greenland halibut")
Egh2 <- rbind(Eghs2, Eghf2) %>% mutate(alt.name = "Greenland halibut")

## Campelen
Cac0 <- rbind(Cacs0, Cacf0) %>% mutate(alt.name = "Atlantic cod")
Cac1 <- rbind(Cacs1, Cacf1) %>% mutate(alt.name = "Atlantic cod")
Cac2 <- rbind(Cacs2, Cacf2) %>% mutate(alt.name = "Atlantic cod")

Cap0 <- rbind(Caps0, Capf0) %>% mutate(alt.name = "American plaice")
Cap1 <- rbind(Caps1, Capf1) %>% mutate(alt.name = "American plaice")

Cgh0 <- rbind(Cghs0, Cghf0) %>% mutate(alt.name = "Greenland halibut")
Cgh1 <- rbind(Cghs1, Cghf1) %>% mutate(alt.name = "Greenland halibut")
Cgh2 <- rbind(Cghs2, Cghf2) %>% mutate(alt.name = "Greenland halibut")

# Combine species data from the Engel and Campelen timeseries
Tac0 <- rbind(Eac0, Cac0)
Tac1 <- rbind(Eac1, Cac1)
Tac2 <- rbind(Eac2, Cac2)

Tap0 <- rbind(Eap0, Cap0)
Tap1 <- rbind(Eap1, Cap1)

Tgh0 <- rbind(Egh0, Cgh0)
Tgh1 <- rbind(Egh1, Cgh1)
Tgh2 <- rbind(Egh2, Cgh2)

# Turn into dataframe
dfac0 <- reshape(data.frame(table(Tac0$year, Tac0$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(ac0_spring = Freq.spring, ac0_fall = Freq.fall)
dfgh0 <- reshape(data.frame(table(Tgh0$year, Tgh0$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(gh0_spring = Freq.spring, gh0_fall = Freq.fall)
dfap0 <- reshape(data.frame(table(Tap0$year, Tap0$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>%  
  rename(ap0_spring = Freq.spring, ap0_fall = Freq.fall)

dfac1 <- reshape(data.frame(table(Tac1$year, Tac1$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(ac1_spring = Freq.spring, ac1_fall = Freq.fall)
dfac2 <- reshape(data.frame(table(Tac2$year, Tac2$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(ac2_spring = Freq.spring, ac2_fall = Freq.fall)

dfgh1 <- reshape(data.frame(table(Tgh1$year, Tgh1$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(gh1_spring = Freq.spring, gh1_fall = Freq.fall)
dfgh2 <- reshape(data.frame(table(Tgh2$year, Tgh2$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(gh2_spring = Freq.spring, gh2_fall = Freq.fall)
dfap1 <- reshape(data.frame(table(Tap1$year, Tap1$season)), idvar = "Var1", timevar = "Var2", direction = "wide") %>% 
  rename(ap1_spring = Freq.spring, ap1_fall = Freq.fall)

ac <- data.frame(year = seq(1984,2020,1), 
                 ac0_spring = c(rep(0,11), dfac0$ac0_spring[1:16], 0, dfac0$ac0_spring[17:24], rep(0,1)),
                 ac1_spring = c(dfac1$ac1_spring),
                 ac2_spring = c(dfac2$ac2_spring[1:11], 0, dfac2$ac2_spring[12:36]),

                 ac0_fall = c(rep(0,11), dfac0$ac0_fall[1:16], 0, dfac0$ac0_fall[17:24], rep(0,1)),
                 ac1_fall = c(dfac1$ac1_fall),
                 ac2_fall = c(dfac2$ac2_fall[1:11], 0, dfac2$ac2_fall[12:36]))
write.csv(ac, file = "./Extra/acseason.csv")

gh <- data.frame(year = seq(1984,2020,1), 
                 gh0_spring = c(dfgh0$gh0_spring),
                 gh1_spring = c(dfgh1$gh1_spring),
                 gh2_spring = c(dfgh2$gh2_spring),

                 gh0_fall = c(dfgh0$gh0_fall),
                 gh1_fall = c(dfgh1$gh1_fall),
                 gh2_fall = c(dfgh2$gh2_fall))
write.csv(gh, file = "./Extra/ghseason.csv")

ap <- data.frame(year = seq(1984,2020,1), 
                 ap0_spring = c(dfap0$ap0_spring),
                 ap1_spring = c(dfap1$ap1_spring),

                 ap0_fall = c(dfap0$ap0_fall),
                 ap1_fall = c(dfap1$ap1_fall))
write.csv(ap, file = "./Extra/apseason.csv")

```

## - Table 1
```{r}

sample_size <- data.frame(
  E.C.Spr = c(nrow(filter(Tac0, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tac1, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tac2, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tgh0, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tgh1, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tgh2, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tap0, geartype == "engel" & season == "spring" & content == "called")),
              nrow(filter(Tap1, geartype == "engel" & season == "spring" & content == "called"))),
  E.C.Fall = c(nrow(filter(Tac0, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tac1, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tac2, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tgh0, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tgh1, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tgh2, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tap0, geartype == "engel" & season == "fall" & content == "called")),
               nrow(filter(Tap1, geartype == "engel" & season == "fall" & content == "called"))),
  E.F.Spr = c(nrow(filter(Tac0, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tac1, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tac2, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tgh0, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tgh1, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tgh2, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tap0, geartype == "engel" & season == "spring" & content == "full")),
              nrow(filter(Tap1, geartype == "engel" & season == "spring" & content == "full"))),
  E.F.Fall = c(nrow(filter(Tac0, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tac1, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tac2, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tgh0, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tgh1, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tgh2, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tap0, geartype == "engel" & season == "fall" & content == "full")),
               nrow(filter(Tap1, geartype == "engel" & season == "fall" & content == "full"))),
  E.pempty =  c(nrow(filter(Tac0, geartype == "engel" & pa == "0"))/nrow(filter(Tac0, geartype == "engel"))*100,
                nrow(filter(Tac1, geartype == "engel" & pa == "0"))/nrow(filter(Tac1, geartype == "engel"))*100,
                nrow(filter(Tac2, geartype == "engel" & pa == "0"))/nrow(filter(Tac2, geartype == "engel"))*100,
                nrow(filter(Tgh0, geartype == "engel" & pa == "0"))/nrow(filter(Tgh0, geartype == "engel"))*100,
                nrow(filter(Tgh1, geartype == "engel" & pa == "0"))/nrow(filter(Tgh1, geartype == "engel"))*100,
                nrow(filter(Tgh2, geartype == "engel" & pa == "0"))/nrow(filter(Tgh2, geartype == "engel"))*100,
                nrow(filter(Tap0, geartype == "engel" & pa == "0"))/nrow(filter(Tap0, geartype == "engel"))*100,
                nrow(filter(Tap1, geartype == "engel" & pa == "0"))/nrow(filter(Tap1, geartype == "engel"))*100),

  C.C.Spr = c(nrow(filter(Tac0, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tac1, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tac2, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tgh0, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tgh1, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tgh2, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tap0, geartype == "campelen" & season == "spring" & content == "called")),
              nrow(filter(Tap1, geartype == "campelen" & season == "spring" & content == "called"))),
  C.C.Fall = c(nrow(filter(Tac0, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tac1, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tac2, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tgh0, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tgh1, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tgh2, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tap0, geartype == "campelen" & season == "fall" & content == "called")),
               nrow(filter(Tap1, geartype == "campelen" & season == "fall" & content == "called"))),
  C.F.Spr = c(nrow(filter(Tac0, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tac1, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tac2, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tgh0, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tgh1, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tgh2, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tap0, geartype == "campelen" & season == "spring" & content == "full")),
              nrow(filter(Tap1, geartype == "campelen" & season == "spring" & content == "full"))),
  C.F.Fall = c(nrow(filter(Tac0, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tac1, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tac2, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tgh0, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tgh1, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tgh2, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tap0, geartype == "campelen" & season == "fall" & content == "full")),
               nrow(filter(Tap1, geartype == "campelen" & season == "fall" & content == "full"))),
  C.pempty =  c(nrow(filter(Tac0, geartype == "campelen" & pa == "0"))/nrow(filter(Tac0, geartype == "campelen"))*100,
                nrow(filter(Tac1, geartype == "campelen" & pa == "0"))/nrow(filter(Tac1, geartype == "campelen"))*100,
                nrow(filter(Tac2, geartype == "campelen" & pa == "0"))/nrow(filter(Tac2, geartype == "campelen"))*100,
                nrow(filter(Tgh0, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh0, geartype == "campelen"))*100,
                nrow(filter(Tgh1, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh1, geartype == "campelen"))*100,
                nrow(filter(Tgh2, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh2, geartype == "campelen"))*100,
                nrow(filter(Tap0, geartype == "campelen" & pa == "0"))/nrow(filter(Tap0, geartype == "campelen"))*100,
                nrow(filter(Tap1, geartype == "campelen" & pa == "0"))/nrow(filter(Tap1, geartype == "campelen"))*100)

)

sample_size <- sample_size %>% mutate(E.pempty = format(E.pempty, digits = 4), C.pempty = format(C.pempty, digits = 4))

write.csv(x = sample_size, file = "./Extra/samplesize.csv")

```

# Annual input trends

## Engel

### Spring

```{r}

load(file = "./ModelSaves/SprEng_Length.RData")

data <- fishy_dat

uni_names <- unique(data$names)
dat_names <- c("Index", uni_names)

new_list <- list()

for(i in 1:length(uni_names)){
  one_dex <- subset(data, names == uni_names[i])
  new_list[[i]] <- aggregate(one_dex$pa, by = list(one_dex$year), FUN = mean, na.rm = TRUE)
}

multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  new_list
)

#Functional Response equation
for(i in 1:(length(uni_names)-1)){
  multi_inner[,i+(length(uni_names)+1)] <- ((multi_inner[ ,i+2]*(rep$chi[i]^rep$beta[i]))/(1-multi_inner[ ,i+2]))^(1/rep$beta[i])
}

# Reverse log transform input values
multi_inner[,2] <- log(1/(1-multi_inner[ ,2]))
for(i in 1:(length(uni_names)-1)){
  multi_inner[,i+(length(uni_names)+1)] <- log(1/(1-multi_inner[ ,i+(length(uni_names)+1)])) # produces NAs but not to worry about
}

# Add all input data into one dataframe
plotdf <- data.frame(time = multi_inner[,1], 
                     ts = multi_inner[,2],
                     ac1 = multi_inner[,8], 
                     ac2 = multi_inner[,9],
                     gh1 = multi_inner[,10],
                     gh2 = multi_inner[,11],
                     ap1 = multi_inner[,12]
                     )

# plot
se <- ggplot(data = plotdf) +  
  geom_line(aes(x = time, y = ts, colour = "trawl"), size = 1.4, linetype = "dashed") +

  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), size = 1.4) +

  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), size = 1.4) +

  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), size = 1.4) +

  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.0,1.7)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "", values = c(medium = "solid", large = "dotdash"),
                        labels = c(medium = "Medium", large = "Large")) +
  ggtitle("Engel\na) 3L Spring") +
  theme_classic() +
  theme(legend.position = "none", 
        axis.title.x = element_blank(),
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))

```

### Fall

```{r, fig.width=10, fig.height=8}

load(file = "./ModelSaves/ACAP-FallEng_Length.RData")
load(file = "./ModelSaves/GH-FallEng_Length.RData")

# Set up index df - GH
gh_data <- gh_fishy_dat
gh_uni_names <- unique(gh_data$names)
gh_dat_names <- c("Index", gh_uni_names)

gh_new_list <- list()
for(i in 1:length(gh_uni_names)){
  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
}

gh_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  gh_new_list
)

#Functional Response equation
for(i in 1:(length(gh_uni_names)-1)){
  gh_multi_inner[,i+(length(gh_uni_names)+1)] <- ((gh_multi_inner[ ,i+2]*(gh_rep$chi[i]^gh_rep$beta[i]))/(1-gh_multi_inner[ ,i+2]))^(1/gh_rep$beta[i])
}

# Reverse log transform input values
gh_multi_inner[,2] <- log(1/(1-gh_multi_inner[ ,2]))
for(i in 1:(length(gh_uni_names)-1)){
  gh_multi_inner[,i+(length(gh_uni_names)+1)] <- log(1/(1-gh_multi_inner[ ,i+(length(gh_uni_names)+1)])) # produces NAs but not to worry about
}

# Set up index df - AC
ac_data <- ac_fishy_dat
ac_uni_names <- unique(ac_data$names)
ac_dat_names <- c("Index", ac_uni_names)

ac_new_list <- list()
for(i in 1:length(ac_uni_names)){
  ac_one_dex <- subset(ac_data, names == ac_uni_names[i])
  ac_new_list[[i]] <- aggregate(ac_one_dex$pa, by = list(ac_one_dex$year), FUN = mean, na.rm = TRUE)
}

ac_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  ac_new_list
)

#Functional Response equation
for(i in 1:(length(ac_uni_names)-1)){
  ac_multi_inner[,i+(length(ac_uni_names)+1)] <- ((ac_multi_inner[ ,i+2]*(ac_rep$chi[i]^ac_rep$beta[i]))/(1-ac_multi_inner[ ,i+2]))^(1/ac_rep$beta[i])
}

# Reverse log transform input values
ac_multi_inner[,2] <- log(1/(1-ac_multi_inner[ ,2])) # have to transform trawl separately bc at start of df
for(i in 1:(length(ac_uni_names)-1)){
  ac_multi_inner[,i+(length(ac_uni_names)+1)] <- log(1/(1-ac_multi_inner[ ,i+(length(ac_uni_names)+1)])) # produces NAs but not to worry about
}

# Add all input data into one dataframe
plotdf <- data.frame(time = gh_multi_inner[,1], 
                     ts = gh_multi_inner[,2],
                     ac1 = ac_multi_inner[,6], 
                     ac2 = ac_multi_inner[,7],
                     gh1 = gh_multi_inner[,5],
                     gh2 = gh_multi_inner[,6],
                     ap1 = ac_multi_inner[,8]
                     )

# plot
fe <- ggplot(data = plotdf) +  
  geom_line(aes(x = time, y = ts, colour = "trawl"), size = 1.4, linetype = "dashed") +

  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), size = 1.4) +

  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), size = 1.4) +

  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), size = 1.4) +

  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "", values = c(medium = "solid", large = "dotdash"),
                        labels = c(medium = "Medium", large = "Large")) +
  ggtitle("c) 2J3KL Fall") + 
  theme_classic() +
  theme(legend.position = "none",
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))

```

## Campelen

### Spring

```{r Fall Campelen, fig.height=8, fig.width=10}

load(file = "./ModelSaves/ACAP-SprCamp_Base.RData")
load(file = "./ModelSaves/GH-SprCamp_Base.RData")

# Set up index df - GH
gh_data <- gh_fishy_dat
gh_uni_names <- unique(gh_data$names)
gh_dat_names <- c("Index", gh_uni_names)

gh_new_list <- list()
for(i in 1:length(gh_uni_names)){
  gh_one_dex <- subset(gh_data, names == gh_uni_names[i])
  gh_new_list[[i]] <- aggregate(gh_one_dex$pa, by = list(gh_one_dex$year), FUN = mean, na.rm = TRUE)
}

gh_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  gh_new_list
)

#Functional Response equation
for(i in 1:(length(gh_uni_names)-1)){
  gh_multi_inner[,i+(length(gh_uni_names)+1)] <- ((gh_multi_inner[ ,i+2]*(gh_rep$chi[i]^gh_rep$beta[i]))/(1-gh_multi_inner[ ,i+2]))^(1/gh_rep$beta[i])
}

# Reverse log transform input values
gh_multi_inner[,2] <- log(1/(1-gh_multi_inner[ ,2]))
for(i in 1:(length(gh_uni_names)-1)){
  gh_multi_inner[,i+(length(gh_uni_names)+1)] <- log(1/(1-gh_multi_inner[ ,i+(length(gh_uni_names)+1)])) # produces NAs but not to worry about
}

# Set up index df - AC
ac_data <- ac_fishy_dat
ac_uni_names <- unique(ac_data$names)
ac_dat_names <- c("Index", ac_uni_names)

ac_new_list <- list()
for(i in 1:length(ac_uni_names)){
  ac_one_dex <- subset(ac_data, names == ac_uni_names[i])
  ac_new_list[[i]] <- aggregate(ac_one_dex$pa, by = list(ac_one_dex$year), FUN = mean, na.rm = TRUE)
}

ac_multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  ac_new_list
)

#Functional Response equation
for(i in 1:(length(ac_uni_names)-1)){
  ac_multi_inner[,i+(length(ac_uni_names)+1)] <- ((ac_multi_inner[ ,i+2]*(ac_rep$chi[i]^ac_rep$beta[i]))/(1-ac_multi_inner[ ,i+2]))^(1/ac_rep$beta[i])
}

# Reverse log transform input values
ac_multi_inner[,2] <- log(1/(1-ac_multi_inner[ ,2])) # have to transform trawl separately bc at start of df
for(i in 1:(length(ac_uni_names)-1)){
  ac_multi_inner[,i+(length(ac_uni_names)+1)] <- log(1/(1-ac_multi_inner[ ,i+(length(ac_uni_names)+1)])) # produces NAs but not to worry about
}

# Add all input data into one dataframe
plotdf <- data.frame(time = gh_multi_inner[,1], 
                     ts = gh_multi_inner[,2],
                     ac1 = ac_multi_inner[,5], 
                     gh1 = gh_multi_inner[,4],
                     ap1 = ac_multi_inner[,6]
                     )

# plot
sc <- ggplot(data = plotdf) +  
  geom_line(aes(x = time, y = ts, colour = "trawl"), size = 1.4, linetype = "dashed") +

  geom_line( aes(x = time, y = ac1, colour = "ac"), size = 1.4, linetype = "solid") +

  geom_line(aes(x = time, y = gh1, colour = "gh"), size = 1.4, linetype = "solid") +

  geom_line(aes(x = time, y = ap1, colour = "ap"), size = 1.4, linetype = "solid") +

  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1994.9,2022), breaks = c(seq(1995, 2022, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.95, 2.2)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  ggtitle("Campelen\nb) 3L Spring") + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))

```

### Fall

```{r Fall Campelen, fig.height=8, fig.width=10}

load(file = "./ModelSaves/FallCamp_Length.RData")

data <- fishy_dat

uni_names <- unique(data$names)
dat_names <- c("Index", uni_names)

new_list <- list()

for(i in 1:length(uni_names)){
  one_dex <- subset(data, names == uni_names[i])
  new_list[[i]] <- aggregate(one_dex$pa, by = list(one_dex$year), FUN = mean, na.rm = TRUE)
}

multi_inner <- Reduce(
  function(x, y, ...) plyr::join(x, y, by = "Group.1", ...), 
  new_list
)

#Functional Response equation
for(i in 1:(length(uni_names)-1)){
  multi_inner[,i+(length(uni_names)+1)] <- ((multi_inner[ ,i+2]*(rep$chi[i]^rep$beta[i]))/(1-multi_inner[ ,i+2]))^(1/rep$beta[i])
}

# Reverse log transform input values
multi_inner[,2] <- log(1/(1-multi_inner[ ,2]))
for(i in 1:(length(uni_names)-1)){
  multi_inner[,i+(length(uni_names)+1)] <- log(1/(1-multi_inner[ ,i+(length(uni_names)+1)])) # produces NAs but not to worry about
}

# Add all input data into one dataframe
plotdf <- data.frame(time = multi_inner[,1], 
                     ts = multi_inner[,2],
                     ac1 = multi_inner[,8], 
                     ac2 = multi_inner[,9],
                     gh1 = multi_inner[,10],
                     gh2 = multi_inner[,11],
                     ap1 = multi_inner[,12]
                     )

# plot
fc <- ggplot(data = plotdf) +  
  geom_line(aes(x = time, y = ts, colour = "trawl"), size = 1.4, linetype = "dashed") +

  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), size = 1.4) +

  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), size = 1.4) +
  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), size = 1.4) +

  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), size = 1.4) +

  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1994.9,2022), breaks = c(seq(1995, 2022, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.32, 1.6)) +
  scale_color_manual(name = "", values = c(trawl = "brown", ac = "#BC8DA0", gh = "#048BA8", ap = "#AFD5AA"),
                     labels = c(trawl = "Trawl", ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "", values = c(medium = "solid", large = "dotdash"),
                        labels = c(medium = "Medium", large = "Large")) +
  ggtitle("d) 2J3KL Fall") + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title.y = element_blank(),
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))

```
## - Figure 2
```{r, fig.height=10, fig.width=12}

p1 <- ggarrange(se,
          sc,
          fe,
          fc,
          nrow = 2, ncol = 2,
          align = "v", common.legend = TRUE,
          legend = "right", legend.grob = ggpubr::get_legend(fc+theme(legend.position = "right", lengend.text = element_text(size = 15))))

ggsave(filename = "inputdata1.tiff", device = "tiff", plot = p1, path = "./Figures",
       dpi = 300, width = 14, height = 10, units = "in")

```

# Residuals

## - Figure 3
```{r, fig.width=7, fig.height=4}
load(file = "./ModelSaves/FallCamp_Length.RData")

sim_response <- replicate(250, obj$simulate()$pa)

sim_res <- DHARMa::createDHARMa(simulatedResponse = sim_response, observedResponse = tmb_data$pa, fittedPredictedResponse = rep$new_mu)

DHARMa::plotQQunif(sim_res, testUniformity=F, testDispersion = F, testOutliers = F)

DHARMa::plotResiduals(sim_res, form = as.factor(tmb_data$idex))
DHARMa::plotResiduals(sim_res, form = as.factor(tmb_data$iyear))

```

# Functional response

```{r, fig.width=5, fig.height=5}
load(file = "./ModelSaves/FallCamp_Length.RData")

# Setup df for FR curve
newx <- seq(from = 0, to = 1, by = 0.001)

## set estimates
beta_est <- as.numeric(sdrep$value[names(sdrep$value) == "beta"])
chi_est <- as.numeric(sdrep$value[names(sdrep$value) == "chi"])
scl_est <- as.numeric(sdrep$value[names(sdrep$value) == "scl"])

#set up for temperature modification on fr
omega_df <- data.frame(tomega = rep$tomega, id = fishy_dat$idex) %>% filter(id > 0) %>% 
  mutate(omega = ((tomega-rep(rep$scl, n[2:6]))/(1-rep(rep$scl, n[2:6]))))
omega_df <- data.frame(tomega = rep$tomega, idex = rep$idex) # match omega vector with idex vector
omega_df <- subset(omega_df, idex > 0) # removes trawl omega because it doenst have FR
omega_df[,3] <- ((omega_df$tomega-rep(rep$scl, n[2:6]))/(1-rep(rep$scl, n[2:6])))
omega_df <- aggregate(omega_df[,3], by = list(omega_df[,2]), FUN = mean)
omega <- omega_df$x # take only omega value

idmod <- unique(rep$idmod)

rate <- list()
for(i in 1:length(rep$scl)){
  rate[[i]] <- ((1*(newx^beta_est[i]))/((chi_est[i]^beta_est[i])+(newx^beta_est[i])))
}

# CI
## format standard deviation
beta_sd <- as.numeric(sdrep$sd[names(sdrep$value) == "beta"])
## generate confidence intervals
beta_low <- vector()
beta_high <- vector()
for(i in 1:length(beta_sd)){
  beta_low[i] <- beta_est[i] - qnorm(0.975)*beta_sd[i]
  beta_high[i] <- beta_est[i] + qnorm(0.975)*beta_sd[i]
}

## format standard deviation
chi_sd <- as.numeric(sdrep$sd[names(sdrep$value) == "chi"])
## generate confidence intervals
chi_low <- vector()
chi_high <- vector()
for(i in 1:length(chi_sd)){
  chi_low[i] <- chi_est[i] - qnorm(0.975)*chi_sd[i]
  chi_high[i] <- chi_est[i] + qnorm(0.975)*chi_sd[i]
}

## format standard deviation
scl_sd <- as.numeric(sdrep$sd[names(sdrep$value) == "scl"])
## generate confidence intervals
scl_low <- vector()
scl_high <- vector()
for(i in 1:length(scl_sd)){
  scl_low[i] <- scl_est[i] - qnorm(0.975)*scl_sd[i]
  scl_high[i] <- scl_est[i] + qnorm(0.975)*scl_sd[i]
}

rate_high <- list()
rate_low <- list()
for(i in 1:length(chi_est)){
  rate_high[[i]] <- ((1*(newx^beta_high[i]))/((chi_high[i]^beta_high[i])+(newx^beta_high[i])))
  rate_low[[i]] <- ((1*(newx^beta_low[i]))/((chi_low[i]^beta_low[i])+(newx^beta_low[i])))
}

```

## - Table 2
```{r}
load(file = "./ModelSaves/FallCamp_Length.RData")

beta_est <- as.numeric(sdrep$value[names(sdrep$value) == "beta"])
chi_est <- as.numeric(sdrep$value[names(sdrep$value) == "chi"])
scl_est <- as.numeric(sdrep$value[names(sdrep$value) == "scl"])

# CI
beta_sd <- as.numeric(sdrep$sd[names(sdrep$value) == "beta"])
beta_low <- vector()
beta_high <- vector()
for(i in 1:length(beta_sd)){
  beta_low[i] <- beta_est[i] - qnorm(0.975)*beta_sd[i]
  beta_high[i] <- beta_est[i] + qnorm(0.975)*beta_sd[i]}

chi_sd <- as.numeric(sdrep$sd[names(sdrep$value) == "chi"])
chi_low <- vector()
chi_high <- vector()
for(i in 1:length(chi_sd)){
  chi_low[i] <- chi_est[i] - qnorm(0.975)*chi_sd[i]
  chi_high[i] <- chi_est[i] + qnorm(0.975)*chi_sd[i]}

scl_sd <- as.numeric(sdrep$sd[names(sdrep$value) == "scl"])
scl_low <- vector()
scl_high <- vector()
for(i in 1:length(scl_sd)){
  scl_low[i] <- scl_est[i] - qnorm(0.975)*scl_sd[i]
  scl_high[i] <- scl_est[i] + qnorm(0.975)*scl_sd[i]}

this <- data.frame(
  estimate = c(
    format(beta_est[1], digits = 4),format(chi_est[1], digits = 4),format(scl_est[1], digits = 4), 
    format(beta_est[2], digits = 4),format(chi_est[2], digits = 4),format(scl_est[2], digits = 4), 
    format(beta_est[3], digits = 4),format(chi_est[3], digits = 4),format(scl_est[3], digits = 4), 
    format(beta_est[4], digits = 4),format(chi_est[4], digits = 4),format(scl_est[4], digits = 4), 
    format(beta_est[5], digits = 4),format(chi_est[5], digits = 4),format(scl_est[5], digits = 4)),
  CI = c(
    paste("[", format(beta_low[1], digits = 3), ",", format(beta_high[1], digits = 3), "]", sep = ""),
    paste("[", format(chi_low[1], digits = 3), ",", format(chi_high[1], digits = 3), "]", sep = ""),
    paste("[", format(scl_low[1], digits = 3), ",", format(scl_high[1], digits = 3), "]", sep = ""),
    paste("[", format(beta_low[2], digits = 3), ",", format(beta_high[2], digits = 3), "]", sep = ""),
    paste("[", format(chi_low[2], digits = 3), ",", format(chi_high[2], digits = 3), "]", sep = ""),
    paste("[", format(scl_low[2], digits = 3), ",", format(scl_high[2], digits = 3), "]", sep = ""),
    paste("[", format(beta_low[3], digits = 3), ",", format(beta_high[3], digits = 3), "]", sep = ""),
    paste("[", format(chi_low[3], digits = 3), ",", format(chi_high[3], digits = 3), "]", sep = ""),
    paste("[", format(scl_low[3], digits = 3), ",", format(scl_high[3], digits = 3), "]", sep = ""),
    paste("[", format(beta_low[4], digits = 3), ",", format(beta_high[4], digits = 3), "]", sep = ""),
    paste("[", format(chi_low[4], digits = 3), ",", format(chi_high[4], digits = 3), "]", sep = ""),
    paste("[", format(scl_low[4], digits = 3), ",", format(scl_high[4], digits = 3), "]", sep = ""),
    paste("[", format(beta_low[5], digits = 3), ",", format(beta_high[5], digits = 3), "]", sep = ""),
    paste("[", format(chi_low[5], digits = 3), ",", format(chi_high[5], digits = 3), "]", sep = ""),
    paste("[", format(scl_low[5], digits = 3), ",", format(scl_high[5], digits = 3), "]", sep = ""))
)

write.csv(x = this, file = "./Figures/frestimates.csv")

```

## - Figure 4
```{r}

ggplot() +
  geom_line(aes(x = newx, y = rate[[1]], colour = "ac", linetype = "c1"), size = 0.8) +
  geom_line(aes(x = newx, y = rate[[2]], colour = "ac", linetype = "c2"), size = 0.8) +
  geom_line(aes(x = newx, y = rate[[3]], colour = "gh", linetype = "c1"), size = 0.8) +
  geom_line(aes(x = newx, y = rate[[4]], colour = "gh", linetype = "c2"), size = 0.8) +
  geom_line(aes(x = newx, y = rate[[5]], colour = "ap", linetype = "c2"), size = 0.8) +

  scale_x_continuous(name = "Relative prey density", limits = c(0,1.02), breaks = c(seq(0,1,0.5)), expand = c(0,0)) +
  scale_y_continuous(name = "Probability of consumption", limits = c(0,1.01), breaks = c(seq(0,1,0.5)), expand = c(0,0)) +
  scale_color_manual(name = "Species", values = c(ac = "#A4243B", gh = "#048BA8", ap = "#FF7733"),
                     labels = c(ac = "Atlantic cod", gh = "Greenland halibut", ap = "American plaice")) +
  scale_linetype_manual(name = "Length category", , values = c(c1 = "solid", c2 = "dotdash"),
                        labels = c(c1 = "Medium", c2 = "Large")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm"),
         linetype = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = c(0.35,0.68), legend.direction = "vertical", legend.spacing.y = unit(.1, 'cm'), 
        legend.text = element_text(size = 15), legend.title = element_text(size = 16, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.line.x = element_line(size = 0.5), 
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
)

ggsave(filename = "bestfr.tiff", device = "tiff", plot = last_plot(), path = "./Figures",
       dpi = 300, width = 5, height = 5, units = "in")

```

# Called to full contents

## Engel

```{r, fig.width=14,fig.height=14}
# load rstrap set data
load(file = "./Data/setdet.rda") 
setdet <- setdet %>% mutate(v.t.s = paste(vessel,trip,set, sep = ".")) %>% 
  filter(spec == "889"|spec == "438"|spec == "892") %>%
  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)),
         long_dd = as.numeric(format(trimws(long.start), digits = 5)))

# Trawl data
eng_fall <- read.csv("./Data/camp_capelin_2J3KL_FULL.csv") %>% rename(year = YEAR, trawl_pa = Capelin_PA) %>% 
  mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."),
         season = ifelse(MONTH == 3|MONTH == 4|MONTH == 5|MONTH == 6|MONTH == 7, "spring", "fall"))
eng_fall <- left_join(eng_fall, 
                       setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
eng_fall <- eng_fall %>% filter(data.series == "Engel" & 
                                    season == "fall"& 
                                    is.na(bot.temp) == FALSE) %>%
  mutate(lat_dd = as.numeric(trimws(lat_dd)),
         long_dd = as.numeric(trimws(long_dd))) %>% 
  filter(year >= 1984)

# Called stomach data
load(file = "./Data/ag.rda")

call_fall <- ag %>% select(-c(source.file, oedge:gutremvol)) %>%  
  filter((spec == "889" | spec == "438" | spec == "892") & 
           (NAFOdiv == "2J" | NAFOdiv == "3K" |NAFOdiv == "3L") &
           which.survey == "multispecies") %>% 
  mutate(v.t.s = paste(vessel, trip, set, sep = "."),
         alt.name = spec,
         alt.name = ifelse(alt.name == "889", "American plaice", alt.name),
         alt.name = ifelse(alt.name == "438", "Atlantic cod", alt.name),
         alt.name = ifelse(alt.name == "892", "Greenland halibut", alt.name),
         pa = ifelse(prey1 == "Capelin"|prey2 == "Capelin", 1, 0), 
         content = rep("called", length(data.series)),
         season = ifelse(month == 3|month == 4|month == 5|month == 6|month == 7, "spring", "fall"))
call_fall <- left_join(call_fall, 
                       setdet %>% select(v.t.s, lat_dd, long_dd, set.depth.max, bot.temp), by = c("v.t.s"), multiple = "any")
call_fall <- call_fall %>%
  filter(data.series == "Engel" & 
           is.na(length) == FALSE & 
           is.na(empty) == FALSE & 
           is.na(bot.temp) == FALSE)

# Full stomach data
full_fall <- read.csv("./Data/NAFC_diet_capelin_COD_TURBOT_PLAICE_2J3KL.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."))
full_fall <- left_join(full_fall, 
                       setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
full_fall <- full_fall %>% mutate(alt.name = PRED_COMM_NAME,
                                  alt.name = ifelse(alt.name == "AMERICAN PLAICE", "American plaice", alt.name),
                                  alt.name = ifelse(alt.name == "COD,ATLANTIC", "Atlantic cod", alt.name),
                                  alt.name = ifelse(alt.name == "TURBOT", "Greenland halibut", alt.name),
                                  pa = ifelse(PREY_CAP == "Capelin", 1, 0),
                                  empty = ifelse(PREY_CAP == "Empty", TRUE, FALSE),
                                  content = rep("full", length(PRED_COMM_NAME)),
                                  SEASON = ifelse(MONTH == 3|MONTH == 4|MONTH == 5|MONTH == 6|MONTH == 7, "spring", "fall")) %>% 
  rename(year = YEAR, month = MONTH, length = LENGTH, NAFOdiv = NAFO, season = SEASON) %>%
  filter(data.series == "Engel" & 
           length < 400 & 
           is.na(length) == FALSE & 
           is.na(bot.temp) == FALSE)

ratiod <- data.frame(content = c(call_fall$content, full_fall$content), 
                     pa = c(call_fall$pa, full_fall$pa), 
                     year = c(call_fall$year, full_fall$year),
                     alt.name = c(call_fall$alt.name, full_fall$alt.name),
                     season = c(call_fall$season, full_fall$season))

avvspp <- ratiod %>% count(content, year, pa, alt.name, season) %>% group_by(content, year, alt.name, season) %>% mutate(freq = n/sum(n))

only1s <- subset(avvspp, pa == 1) %>% filter(year > 1983)
only1s$freq <- as.numeric(only1s$freq)

# Create a blank data frame representing all years 
blank <- data.frame(content = c(rep("called", 72),rep("full", 72)),
           year = c(rep(seq(1984,1995),6), rep(seq(1984,1995),6)),
           pa = rep(1, 144),
           alt.name = rep(c(rep("American plaice", 12), rep("Atlantic cod", 12), rep("Greenland halibut", 12)), 2),
           season = rep(c(rep("spring", 36), rep("fall", 36)), 2),
           n = rep(NA, 144),
           freq = rep(NA, 144)
)

# Add observations from initial data.frame while retaining NAs
for(i in 1:nrow(blank)){
  for(j in 1:nrow(only1s)){
    if(only1s[j,1] == blank[i,1] & only1s[j,2] == blank[i,2] & only1s[j,4] == blank[i,4] & only1s[j,5] == blank[i,5]){
      blank[i,6] = only1s[j,6]
      blank[i,7] = only1s
    }
  }
  }

# Format blank data.frame for nice figure
blank <- blank %>% mutate(season = ifelse(season == "fall", "Fall", "Spring"),
                          content = ifelse(content == "called", "Called", "Full"))

ggplot(blank) +
  geom_line(aes(x = year, y = freq, colour = as.factor(content), group = as.factor(content))) +
  geom_point(aes(x = year, y = freq, colour = as.factor(content), group = as.factor(content))) +

  scale_x_continuous(name = "Year", expand = c(0,0.2), breaks = c(seq(1984,1994,2))) + 
  scale_y_continuous(name = "Frequency of present capelin", expand = c(0,0)) + 
  scale_colour_discrete(name = "Stomach content") +

  facet_wrap(vars(alt.name, season), scales = "free_y", nrow = 3) +
  theme_bw() +
  theme(panel.grid.major.y = element_blank(), panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(),
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        legend.text = element_text(size = 13), legend.title = element_text(size = 14))

ggsave(filename = "engcalltofull.tiff", device = "tiff", plot = last_plot(), path = "./Figures",
       dpi = 300, width = 16, height = 14, units = "in")

```

## Campelen

```{r, fig.width=16,fig.height=14}

# load rstrap set data
load(file = "./Data/setdet.rda") 
setdet <- setdet %>% mutate(v.t.s = paste(vessel,trip,set, sep = ".")) %>% 
  filter(spec == "889"|spec == "438"|spec == "892") %>%
  mutate(lat_dd = as.numeric(format(trimws(lat.start), digits = 5)),
         long_dd = as.numeric(format(trimws(long.start), digits = 5)))

# Trawl data
camp_fall <- read.csv("./Data/camp_capelin_2J3KL_FULL.csv") %>% rename(year = YEAR, trawl_pa = Capelin_PA) %>% 
  mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."),
         season = ifelse(MONTH == 3|MONTH == 4|MONTH == 5|MONTH == 6|MONTH == 7, "spring", "fall"))
camp_fall <- left_join(camp_fall, 
                       setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
camp_fall <- camp_fall %>% filter(data.series == "Campelen" & 
                                    season == "fall"& 
                                    is.na(bot.temp) == FALSE) %>%
  mutate(lat_dd = as.numeric(trimws(lat_dd)),
         long_dd = as.numeric(trimws(long_dd))) %>%
filter(year <= 2020)

# Called stomach data
load(file = "./Data/ag.rda")

call_fall <- ag %>% select(-c(source.file, oedge:gutremvol)) %>%  
  filter((spec == "889" | spec == "438" | spec == "892") & 
           (NAFOdiv == "2J" | NAFOdiv == "3K" |NAFOdiv == "3L") &
           which.survey == "multispecies") %>% 
  mutate(v.t.s = paste(vessel, trip, set, sep = "."),
         alt.name = spec,
         alt.name = ifelse(alt.name == "889", "American plaice", alt.name),
         alt.name = ifelse(alt.name == "438", "Atlantic cod", alt.name),
         alt.name = ifelse(alt.name == "892", "Greenland halibut", alt.name),
         pa = ifelse(prey1 == "Capelin"|prey2 == "Capelin", 1, 0), 
         content = rep("called", length(data.series)),
         season = ifelse(month == 3|month == 4|month == 5|month == 6|month == 7, "spring", "fall"))
call_fall <- left_join(call_fall, 
                       setdet %>% select(v.t.s, lat_dd, long_dd, set.depth.max, bot.temp), by = c("v.t.s"), multiple = "any")
call_fall <- call_fall %>%
  filter(data.series == "Campelen" & 
           is.na(length) == FALSE & 
           is.na(empty) == FALSE & 
           is.na(bot.temp) == FALSE)

# Full stomach data
full_fall <- read.csv("./Data/NAFC_diet_capelin_COD_TURBOT_PLAICE_2J3KL.csv") %>% mutate(v.t.s = paste(VESSEL,TRIP,SET, sep = "."))
full_fall <- left_join(full_fall, 
                      setdet %>% select(v.t.s, set.depth.max, data.series, bot.temp), by = c("v.t.s"), multiple = "any")
full_fall <- full_fall %>% mutate(alt.name = PRED_COMM_NAME,
                                alt.name = ifelse(alt.name == "AMERICAN PLAICE", "American plaice", alt.name),
                                alt.name = ifelse(alt.name == "COD,ATLANTIC", "Atlantic cod", alt.name),
                                alt.name = ifelse(alt.name == "TURBOT", "Greenland halibut", alt.name),
                                pa = ifelse(PREY_CAP == "Capelin", 1, 0),
                                empty = ifelse(PREY_CAP == "Empty", TRUE, FALSE),
                                content = rep("full", length(PRED_COMM_NAME)),
                                SEASON = ifelse(MONTH == 3|MONTH == 4|MONTH == 5|MONTH == 6|MONTH == 7, "spring", "fall")) %>% 
  rename(year = YEAR, month = MONTH, length = LENGTH, NAFOdiv = NAFO, season = SEASON) %>%
  filter(data.series == "Campelen" & 
           length < 400 & 
           is.na(length) == FALSE & 
           is.na(bot.temp) == FALSE)

ratiod <- data.frame(content = c(call_fall$content, full_fall$content), 
                     pa = c(call_fall$pa, full_fall$pa), 
                     year = c(call_fall$year, full_fall$year),
                     alt.name = c(call_fall$alt.name, full_fall$alt.name),
                     season = c(call_fall$season, full_fall$season))
ratiod <- ratiod %>% filter(year > 1994)

avvspp <- ratiod %>% count(content, year, pa, alt.name, season) %>% group_by(content, year, alt.name, season) %>% mutate(freq = n/sum(n))

only1s <- subset(avvspp, pa == 1)
only1s$freq <- as.numeric(only1s$freq)

# Create a blank data frame representing all years 
blank <- data.frame(content = c(rep("called", 156),rep("full", 156)),
           year = rep(rep(seq(1995,2020),6), 2),
           pa = rep(1, 312),
           alt.name = rep(c(rep("American plaice", 26), rep("Atlantic cod", 26), rep("Greenland halibut", 26)), 2),
           season = rep(c(rep("spring", 78), rep("fall", 78)), 2),
           n = rep(NA, 312),
           freq = rep(NA, 312)
)

# Add observations from initial data.frame while retaining NAs
for(i in 1:nrow(blank)){
  for(j in 1:nrow(only1s)){

    if(only1s[j,1] == blank[i,1] & only1s[j,2] == blank[i,2] & only1s[j,4] == blank[i,4] & only1s[j,5] == blank[i,5]){
      blank[i,6] = only1s[j,6]
      blank[i,7] = only1s[j,7]
    }

  }
}

# Format blank data.frame for nice figure
blank <- blank %>% mutate(season = ifelse(season == "fall", "Fall", "Spring"),
                          content = ifelse(content == "called", "Called", "Full"))

ggplot(blank) +
  geom_line(aes(x = year, y = freq, colour = as.factor(content), group = as.factor(content))) +
  geom_point(aes(x = year, y = freq, colour = as.factor(content), group = as.factor(content))) +

  scale_x_continuous(name = "Year", expand = c(0,0.2), breaks = c(seq(1995, 2022, 5))) + 
  scale_y_continuous(name = "Frequency of present capelin", expand = c(0,0)) + 
  scale_colour_discrete(name = "Stomach content") +

  facet_wrap(vars(alt.name, season), scales = "free_y", nrow = 3) +
  theme_bw() +
  theme(panel.grid.major.y = element_blank(), panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(),
        axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        legend.text = element_text(size = 13), legend.title = element_text(size = 14))

ggsave(filename = "campcalltofull.tiff", device = "tiff", plot = last_plot(), path = "./Figures",
       dpi = 300, width = 16, height = 14, units = "in")

```

# Predator feeding ranges

## Spring Engel

```{r}
source("./Analysis/Engel/Spring/SprEng-SetUp.R")

pTSE <- ggplot(stom_spr_good) +
  geom_boxplot(aes(x = alt.name, y = bot.temp)) +

  scale_x_discrete(name = "Predator species") +
  scale_y_continuous(name = "Bottom temperature (°C)", limits = c(min(stom_spr_good$bot.temp)-0.1, max(stom_spr_good$bot.temp)+0.1)) +

  theme_classic() +
  theme(axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), axis.title.x = element_blank(),
        legend.text = element_text(size = 13), legend.title = element_text(size = 14)
  )

```

## Fall Engel

```{r}
source("./Analysis/Engel/Fall/FallEng-SetUp.R")

pTFE <- ggplot(stom_fall_good) +
  geom_boxplot(aes(x = alt.name, y = bot.temp)) +

  scale_x_discrete(name = "Predator species") +
  scale_y_continuous(name = "Bottom temperature (°C)", limits = c(min(stom_fall_good$bot.temp)-0.1, max(stom_fall_good$bot.temp)+0.1)) +

  theme_classic() +
  theme(axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        legend.text = element_text(size = 13), legend.title = element_text(size = 14)
  )

```

## Spring Campelen

```{r}
source("./Analysis/Campelen/Spring/SprCamp-SetUp.R")

pTSC <- ggplot(stom_spr_good) +
  geom_boxplot(aes(x = alt.name, y = bot.temp)) +

  scale_x_discrete(name = "Predator species") +
  scale_y_continuous(name = "Bottom temperature (°C)", limits = c(min(stom_spr_good$bot.temp)-0.1, max(stom_spr_good$bot.temp)+0.1)) +

  theme_classic() +
  theme(axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        legend.text = element_text(size = 13), legend.title = element_text(size = 14)
  )

```

## Fall Campelen

```{r}
source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")

pTFC <- ggplot(stom_fall_good) +
  geom_boxplot(aes(x = alt.name, y = bot.temp)) +

  scale_x_discrete(name = "Predator species") +
  scale_y_continuous(name = "Bottom temperature (°C)", limits = c(min(stom_fall_good$bot.temp)-0.1, max(stom_fall_good$bot.temp)+0.1)) +

  theme_classic() +
  theme(axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), axis.title.y = element_blank(),
        legend.text = element_text(size = 13), legend.title = element_text(size = 14)
  )

```
## - Figure 5
```{r, fig.width=10.5, fig.height=8}
ggpubr::ggarrange(pTSE+ggtitle("Engel\na) 3L Spring")+theme(plot.title = element_text(face = "bold")),
                  pTSC+ggtitle("Campelen\nb) 3L Spring")+theme(plot.title = element_text(face = "bold")),
                  pTFE+ggtitle("c) 2J3KL Fall")+theme(plot.title = element_text(face = "bold")),
                  pTFC+ggtitle("d) 2J3KL Fall")+theme(plot.title = element_text(face = "bold"))

)

ggsave(filename = "tempranges.tiff", device = "tiff", plot = last_plot(), path = "./Figures",
       dpi = 300, width = 10.5, height = 8, units = "in")

```

# Additional
## Mean sizes of fish within size categories across years?

```{r}
source("./Analysis/Campelen/Fall/FallCamp-SetUp.R")
# Set up different length bins
ac0c <- AC_stof %>% filter(length <= 17)
ac1c <- AC_stof %>% filter(length > 17 & length <= 45)
ac2c <- AC_stof %>% filter(length > 45) %>% filter(year != 1994)
ap0c <- AP_stof %>% filter(length <= 29)
ap1c <- AP_stof %>% filter(length > 29)
gh0c <- GH_stof %>% filter(length <= 19)
gh1c <- GH_stof %>% filter(length > 19 & length <= 40)
gh2c <- GH_stof %>% filter(length > 40)

source("./Analysis/Engel/Fall/FallEng-SetUp.R")
# Set up different length bins
ac0e <- AC_stof %>% filter(length <= 17)
ac1e <- AC_stof %>% filter(length > 17 & length <= 45)
ac2e <- AC_stof %>% filter(length > 45) %>% filter(year != 1994)
ap0e <- AP_stof %>% filter(length <= 29)
ap1e <- AP_stof %>% filter(length > 29)
gh0e <- GH_stof %>% filter(length <= 19)
gh1e <- GH_stof %>% filter(length > 19 & length <= 40)
gh2e <- GH_stof %>% filter(length > 40)

data.frame("lenbin" = c("ac0","ac1","ac2", "ap0","ap1", "gh0","gh1","gh2"),
           "engel" = c(mean(ac0e$length), mean(ac1e$length),mean(ac2e$length),
                          mean(ap0e$length), mean(ap1e$length),
                          mean(gh0e$length), mean(gh1e$length), mean(gh2e$length)),
           "campelen" = c(mean(ac0c$length), mean(ac1c$length),mean(ac2c$length),
                          mean(ap0c$length), mean(ap1c$length),
                          mean(gh0c$length), mean(gh1c$length), mean(gh2c$length)))

data.frame("lenbin" = c("ac0","ac1","ac2", "ap0","ap1", "gh0","gh1","gh2"),
           "engel" = c(median(ac0e$length), median(ac1e$length),median(ac2e$length),
                          median(ap0e$length), median(ap1e$length),
                          median(gh0e$length), median(gh1e$length), median(gh2e$length)),
           "campelen" = c(median(ac0c$length), median(ac1c$length),median(ac2c$length),
                          median(ap0c$length), median(ap1c$length),
                          median(gh0c$length), median(gh1c$length), median(gh2c$length)))

```

### 2025-05-20 SuppSections.Rmd
Added empty stomach sample size.

@@
 acs2 <- AC_stos %>% filter(length > 45)
-aps1 <- AP_stos %>% filter(length > 29)
 ghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
 ghs2 <- GH_stos %>% filter(length > 40)
+aps1 <- AP_stos %>% filter(length > 29)
 
 acs0 <- AC_stos %>% filter(length < 18)
+ghs0 <- GH_stos %>% filter(length < 20)
 aps0 <- AP_stos %>% filter(length < 30)
-ghs0 <- GH_stos %>% filter(length < 20)
-
-# table(acs0$pa, acs0$year)
-# table(acs1$pa, acs1$year)
-# table(acs2$pa, acs2$year)
-# table(aps0$pa, aps0$year)
-# table(aps1$pa, aps1$year)
-# table(ghs0$pa, ghs0$year)
-# table(ghs1$pa, ghs1$year)
-# table(ghs2$pa, ghs2$year)
+
+table(acs0$pa, acs0$year)
+table(acs1$pa, acs1$year)
+table(acs2$pa, acs2$year)
+table(ghs0$pa, ghs0$year)
+table(ghs1$pa, ghs1$year)
+table(ghs2$pa, ghs2$year)
+table(aps0$pa, aps0$year)
+table(aps1$pa, aps1$year)
 
@@
 Eacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 1995)
-Eaps1 <- AP_stos %>% filter(length > 29)
 Eghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
 Eghs2 <- GH_stos %>% filter(length > 40)
+Eaps1 <- AP_stos %>% filter(length > 29)
 
 Eacs0 <- AC_stos %>% filter(length < 18) %>% filter(year == 1982)
+Eghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 1984)
 Eaps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 1984)
-Eghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 1984)
 
@@
 acf2 <- AC_stof %>% filter(length > 45)
-apf1 <- AP_stof %>% filter(length > 29)
 ghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
 ghf2 <- GH_stof %>% filter(length > 40)
+apf1 <- AP_stof %>% filter(length > 29)
 
 acf0 <- AC_stof %>% filter(length < 18)
+ghf0 <- GH_stof %>% filter(length < 20)
 apf0 <- AP_stof %>% filter(length < 30)
-ghf0 <- GH_stof %>% filter(length < 20)
-
-# table(acf0$pa, acf0$year)
-# table(acf1$pa, acf1$year)
-# table(acf2$pa, acf2$year)
-# table(apf0$pa, apf0$year)
-# table(apf1$pa, apf1$year)
-# table(ghf0$pa, ghf0$year)
-# table(ghf1$pa, ghf1$year)
-# table(ghf2$pa, ghf2$year)
+
+table(acf0$pa, acf0$year)
+table(acf1$pa, acf1$year)
+table(acf2$pa, acf2$year)
+table(apf0$pa, apf0$year)
+table(apf1$pa, apf1$year)
+table(ghf0$pa, ghf0$year)
+table(ghf1$pa, ghf1$year)
+table(ghf2$pa, ghf2$year)
 
@@
 Eacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1994)
-Eapf1 <- AP_stof %>% filter(length > 29)
 Eghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
 Eghf2 <- GH_stof %>% filter(length > 40)
-
-Eacf0 <- AC_stof %>% filter(length < 18) %>% filter(year == 1982 & year == 1983 & year == 1988)
+Eapf1 <- AP_stof %>% filter(length > 29)
+
+Eacf0 <- AC_stof %>% filter(length < 18) %>% filter(year == 1988)
+Eghf0 <- GH_stof %>% filter(length < 20)
 Eapf0 <- AP_stof %>% filter(length < 30)
-Eghf0 <- GH_stof %>% filter(length < 20)
 
@@
 Cacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 2015)
-Caps1 <- AP_stos %>% filter(length > 29) %>% filter(year != 2017)
 Cghs1 <- GH_stos %>% filter(length > 19 & length <= 40) %>% filter(year != 2017)
 Cghs2 <- GH_stos %>% filter(length > 40)
+Caps1 <- AP_stos %>% filter(length > 29) %>% filter(year != 2017)
 
 Cacs0 <- AC_stos %>% filter(length < 18) %>% filter(year != 1996 & year != 1998 & year != 1999 & year != 2006 & year != 2011 & year != 2017)
+Cghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 2015 & year != 2017)
 Caps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 2017)
-Cghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 2015 & year != 2017)
 
@@
 Cacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1995)
-Capf1 <- AP_stof %>% filter(length > 29) %>% filter(year != 2014)
 Cghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
 Cghf2 <- GH_stof %>% filter(length > 40)
+Capf1 <- AP_stof %>% filter(length > 29) %>% filter(year != 2014)
 
 Cacf0 <- AC_stof %>% filter(length < 18) %>% filter(year != 2011 & year != 2020)
+Cghf0 <- GH_stof %>% filter(length < 20)
 Capf0 <- AP_stof %>% filter(length < 30) %>% filter(year != 2014)
-Cghf0 <- GH_stof %>% filter(length < 20)
 
@@
 
-                 ac0_fall = c(rep(0,11), dfac0$ac0_fall[1:16], 0, dfac0$ac0_fall[17:24], rep(0,1)),
+                 ac0_fall = c(rep(0,4), dfac0$ac0_fall[1], rep(0,6), dfac0$ac0_fall[1:16], 0, dfac0$ac0_fall[17:24], rep(0,1)),
                  ac1_fall = c(dfac1$ac1_fall),
@@
                nrow(filter(Tap1, geartype == "engel" & season == "fall" & content == "full"))),
-  E.pempty =  c(nrow(filter(Tac0, geartype == "engel" & pa == "0"))/nrow(filter(Tac0, geartype == "engel"))*100,
+  E.pcapelin =  c(nrow(filter(Tac0, geartype == "engel" & pa == "0"))/nrow(filter(Tac0, geartype == "engel"))*100,
                   nrow(filter(Tac1, geartype == "engel" & pa == "0"))/nrow(filter(Tac1, geartype == "engel"))*100,
@@
                   nrow(filter(Tap1, geartype == "engel" & pa == "0"))/nrow(filter(Tap1, geartype == "engel"))*100),
+  E.pempty =  c(nrow(filter(Tac0, geartype == "engel" & empty == TRUE))/nrow(filter(Tac0, geartype == "engel"))*100,
+                nrow(filter(Tac1, geartype == "engel" & empty == TRUE))/nrow(filter(Tac1, geartype == "engel"))*100,
+                nrow(filter(Tac2, geartype == "engel" & empty == TRUE))/nrow(filter(Tac2, geartype == "engel"))*100,
+                nrow(filter(Tgh0, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh0, geartype == "engel"))*100,
+                nrow(filter(Tgh1, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh1, geartype == "engel"))*100,
+                nrow(filter(Tgh2, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh2, geartype == "engel"))*100,
+                nrow(filter(Tap0, geartype == "engel" & empty == TRUE))/nrow(filter(Tap0, geartype == "engel"))*100,
+                nrow(filter(Tap1, geartype == "engel" & empty == TRUE))/nrow(filter(Tap1, geartype == "engel"))*100),
 
@@
                nrow(filter(Tap1, geartype == "campelen" & season == "fall" & content == "full"))),
-  C.pempty =  c(nrow(filter(Tac0, geartype == "campelen" & pa == "0"))/nrow(filter(Tac0, geartype == "campelen"))*100,
+  C.pcapelin =  c(nrow(filter(Tac0, geartype == "campelen" & pa == "0"))/nrow(filter(Tac0, geartype == "campelen"))*100,
                   nrow(filter(Tac1, geartype == "campelen" & pa == "0"))/nrow(filter(Tac1, geartype == "campelen"))*100,
@@
                   nrow(filter(Tap0, geartype == "campelen" & pa == "0"))/nrow(filter(Tap0, geartype == "campelen"))*100,
-                nrow(filter(Tap1, geartype == "campelen" & pa == "0"))/nrow(filter(Tap1, geartype == "campelen"))*100)
-
-)
-
-sample_size <- sample_size %>% mutate(E.pempty = format(E.pempty, digits = 4), C.pempty = format(C.pempty, digits = 4))
-
-write.csv(x = sample_size, file = "./Extra/samplesize.csv")
+                  nrow(filter(Tap1, geartype == "campelen" & pa == "0"))/nrow(filter(Tap1, geartype == "campelen"))*100),
+  C.pempty = c(nrow(filter(Tac0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac0, geartype == "campelen"))*100,
+                nrow(filter(Tac1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac1, geartype == "campelen"))*100,
+                nrow(filter(Tac2, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac2, geartype == "campelen"))*100,
+                nrow(filter(Tgh0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh0, geartype == "campelen"))*100,
+                nrow(filter(Tgh1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh1, geartype == "campelen"))*100,
+                nrow(filter(Tgh2, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh2, geartype == "campelen"))*100,
+                nrow(filter(Tap0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tap0, geartype == "campelen"))*100,
+                nrow(filter(Tap1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tap1, geartype == "campelen"))*100)
+
+)
+
+sample_size <- sample_size %>% mutate(E.pcapelin = format(E.pcapelin, digits = 4), C.pcapelin = format(C.pcapelin, digits = 4),
+                                      E.pempty = format(E.pempty, digits = 4), C.pempty = format(C.pempty, digits = 4))
+
+write.csv(x = sample_size, file = "./Extra/samplesize_16.05.25.csv")
 

### 2025-05-20 Functions/make_data.R
Associated model set up funcitons.

@@ -1,0 +1,141 @@
+#' Create basic data.frame for the model
+#'
+#'
+#' Combine presence/absence data from bottom trawl surveys, stomach contents, and an index for the different indices and different species/ ontogeny
+#'
+#' @param pa Vector of presence/absence data from all surveys (binary)
+#' @param year Vector of years associated with each observation (numeric)
+#' @param n Vector of the number of observations for each survey (integer)
+#' @param names Vector of names for each type of data, used for plotting (character)
+#' @param tempType Argument for the implementation of temperature: "noTemp", "monoTemp", "scaledTemp" (character) 
+#' @param onto Optional, Bollean whether to account for ontogenetic diet shifts (True/False), defaults to False
+#' @param temp Optional, Vector of individual temperature observations (vector)
+#' @param spp_id Optional, Vector of species identifiers, only needed for \code{tempType = "monoTemp"} when \code{onto = T} (integer)
+#' @param spp_n Optional, Vector of the number of observations for each survey and species, only needed for \code{tempType = "monoTemp"} when \code{onto = T} (integer)
+#'
+#' @return data.frame
+#' @export
+#'
+#' @examples
+#' make_data(pa=rbinom(n=20, size=1, prob=0.5), year=rep(seq(from=1, to=10, by=1),2), n=c(10,10), id =c(0,1,1), names=c("Trawl", "Call", "Full"))
+make_data <- function(n, pa, year, names, tempType, onto = F, temp = NULL, spp_id = NULL, spp_n = NULL){
+  
+  if(tempType == "noTemp" | tempType == "scaledTemp" | tempType == "monoTemp"){
+    
+    id <- c(seq(0,(length(names)-1)))
+    
+    #############################
+    # For no temperature effect #
+    #############################
+    
+    if(onto == T | onto == F){  
+      if(tempType == "noTemp"){
+        
+        fishy_dat <- data.frame(pa = pa, 
+                                year = year, 
+                                names = rep(names, n),
+                                idex = rep(id, n)
+        )
+      }
+    }
+    
+    
+    #############################
+    # For no ontogenetic effect #
+    #############################
+    
+    if(onto == F){
+      
+      # For monotonic temperature shape
+      if(tempType == "monoTemp"){
+        
+        if(is.null(spp_id) == T | is.null(spp_n) == T){
+          stop("Please ensure spp_id and spp_n are defined.")
+        } else{
+          if(is.null(temp == T)){
+            stop("Please ensure temp is defined.")
+          } else{
+            
[…]

### 2025-05-20 Functions/model_data.R

@@ -1,0 +1,100 @@
+#' Create data list for general functional response model
+#'
+#'
+#' @param fishy_dat Object output from the make_data() function
+#' @param n A vector the length of the number of datasets used where each number indicates the number of observations for that dataset
+#' @param modType A character identifying whether you are creating data for a linear or nonlinear functional response model. Input "linear" for a linear model and "nonlinear" for a nonlinear model
+#' @param tempType Argument for the implementation of temperature: "noTemp", "monoTemp", "scaledTemp" (character) 
+#'
+#'
+#'
+#' @return A list of data to be used when generating the TMB model. The list includes the total number of observations (n), the number of years (nyrs),
+#' the number of datasets (ndex), an index vector for the year of each observation (iyear), an index vector for the dataset associated with each observation (idex), and
+#' a vector for all presence/absence data (pa)
+#' @export
+#'
+#' @examples model_data(fishy_dat=fishy_dat, n=c(length(df$pa),length(df1$pa),length(df2$pa)), modType="nonlinear", tempType="noTemp")
+model_data <- function(fishy_dat, n, modType, tempType){
+  
+  if(modType == "linear"){
+    tmb_data <- list(n = length(fishy_dat$pa),
+                     nyrs = length(unique(fishy_dat$year)),
+                     ndex = length(unique(fishy_dat$idex)),
+                     iyear = fishy_dat$year-min(fishy_dat$year),
+                     idex = fishy_dat$idex,
+                     pa = fishy_dat$pa,
+                     modType = "linear"
+    )
+    
+  }
+  
+  
+  
+  if(modType == "nonlinear"){
+    
+    if(tempType == "noTemp"){
+      tmb_data <- list(n = length(fishy_dat$pa),
+                       nyrs = length(unique(fishy_dat$year)),
+                       ndex = length(unique(fishy_dat$idex)),
+                       iyear = fishy_dat$year-min(fishy_dat$year),
+                       idex = fishy_dat$idex,
+                       pa = fishy_dat$pa,
+                       k = 1, # maximum consumtion rate
+                       idmod = 0,
+                       tempType = "noTemp",
+                       modType = "nonlinear"
+      )
+      
+    }
+    
+    if(tempType == "scaledTemp"){
+      
+      # Generate theta values
+      theta <- data.frame(species = fishy_dat$names, value = rep(NA, length(fishy_dat$pa)))
[…]

### 2025-05-20 Functions/model_param.R

@@ -1,0 +1,136 @@
+#' Create parameter list for for general functional response model
+#'
+#'
+#' @param tmb_data TMB data object from the model_data() function
+#' @param lbeta A logged starting value for the beta parameter
+#' @param lchi A logged starting value for the chi parameter
+#' @param lk A placeholder parameter for the linear model that allows it to run, since otherwise there wouldn't be any fixed effects parameters. Don't change from default
+#' @param lscl  A logged starting value for the scl (temperature scaling) parameter
+#' @param lmink A logged starting value for the mink (minimum consumption rate) parameter
+#' @param lmidp A logged starting value for the midp (mid point) parameter
+#'
+#' @return A list of parameters for the functional response model, including a vector the length of the number of years (iye), 
+#' and a starting value for the beta, chi, and random walk variability parameters
+#' @export
+#'
+#' @examples model_param(tmb_data=tmb_data, lbeta=log(2), lchi=log(1), type="nonlinear")
+model_param <- function(tmb_data, lbeta, lchi, lscl = NULL, lmink = NULL, lmidp = NULL){
+  
+  if(tmb_data$modType == "linear"){
+    tmb_params <- list(
+      iye = seq(from=log(10), to=log(20), length.out=tmb_data$nyrs),
+      lk = 0
+    )
+  }
+  
+  if(tmb_data$modType == "nonlinear"){
+    
+    
+    if(tmb_data$tempType == "noTemp"){
+      tmb_params <- list(
+        iye = seq(from=log(10), to=log(20), length.out=tmb_data$nyrs),
+        logrw_var = log(1),
+        lbeta = c(rep(lbeta, tmb_data$ndex-1)),
+        lchi = c(rep(lchi, tmb_data$ndex-1))
+      )
+    }
+    
+    
+    
+    
+    if(tmb_data$tempType == "scaledTemp"){
+      if(is.null(lscl) == T){
+        warning("Automatic value lscl = log(1). Please assign lscl.")
+        
+        tmb_params <- list(
+          iye = seq(from=log(10), to=log(20), length.out=tmb_data$nyrs),
+          logrw_var = log(1),
+          lbeta = c(rep(lbeta, tmb_data$ndex-1)),
+          lchi = c(rep(lchi, tmb_data$ndex-1)),
[…]

### 2025-05-20 PaperSections.Rmd
Updated sample size table.

@@
 ```
-## - Figure 2
+## - Figure 1
 ```{r, fig.width=5, fig.height=5}
@@
         plot.title = element_text(size = 16, face = "bold"))
+```
+
+# Sample size
+
+## Engel
+
+### Spring
+```{r}
+load(file = "./ModelSaves/Set_Up/SE-1995.RData")
+
+Eacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1995)
+Eacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 1995)
+Eghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
+Eghs2 <- GH_stos %>% filter(length > 40)
+Eaps1 <- AP_stos %>% filter(length > 29)
+
+Eacs0 <- AC_stos %>% filter(length < 18) %>% filter(year == 1982)
+Eghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 1984)
+Eaps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 1984)
+
+```
+
+### Fall
+```{r}
+load(file = "./ModelSaves/Set_Up/FE-1994.RData")
+
+Eacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
+Eacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1994)
+Eghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
+Eghf2 <- GH_stof %>% filter(length > 40)
+Eapf1 <- AP_stof %>% filter(length > 29)
+
+Eacf0 <- AC_stof %>% filter(length < 18) %>% filter(year == 1988)
+Eghf0 <- GH_stof %>% filter(length < 20)
+Eapf0 <- AP_stof %>% filter(length < 30)
+
+```
+
+### Total
+```{r}
+Eac0 <- rbind(Eacs0, Eacf0) %>% mutate(alt.name = "Atlantic cod")
+Eac1 <- rbind(Eacs1, Eacf1) %>% mutate(alt.name = "Atlantic cod")
+Eac2 <- rbind(Eacs2, Eacf2) %>% mutate(alt.name = "Atlantic cod")
+Eap0 <- rbind(Eaps0, Eapf0) %>% mutate(alt.name = "American plaice")
+Eap1 <- rbind(Eaps1, Eapf1) %>% mutate(alt.name = "American plaice")
+Egh0 <- rbind(Eghs0, Eghf0) %>% mutate(alt.name = "Greenland halibut")
+Egh1 <- rbind(Eghs1, Eghf1) %>% mutate(alt.name = "Greenland halibut")
+Egh2 <- rbind(Eghs2, Eghf2) %>% mutate(alt.name = "Greenland halibut")
+
+```
+
+## Campelen
+
+### Spring
+```{r}
+load(file = "./ModelSaves/Set_Up/SC-2019.RData")
+
+Cacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1998 & year != 2017)
+Cacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 2015)
+Cghs1 <- GH_stos %>% filter(length > 19 & length <= 40) %>% filter(year != 2017)
+Cghs2 <- GH_stos %>% filter(length > 40)
+Caps1 <- AP_stos %>% filter(length > 29) %>% filter(year != 2017)
+
+Cacs0 <- AC_stos %>% filter(length < 18) %>% filter(year != 1996 & year != 1998 & year != 1999 & year != 2006 & year != 2011 & year != 2017)
+Cghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 2015 & year != 2017)
+Caps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 2017)
+
+```
+
+### Fall
+```{r}
+# load rstrap set data
+load(file = "./ModelSaves/Set_Up/FC-2020.RData")
+
+Cacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
+Cacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1995)
+Cghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
+Cghf2 <- GH_stof %>% filter(length > 40)
+Capf1 <- AP_stof %>% filter(length > 29) %>% filter(year != 2014)
+
+Cacf0 <- AC_stof %>% filter(length < 18) %>% filter(year != 2011 & year != 2020)
+Cghf0 <- GH_stof %>% filter(length < 20)
+Capf0 <- AP_stof %>% filter(length < 30) %>% filter(year != 2014)
+
+```
+
+### Total
+```{r}
+
+Cac0 <- rbind(Cacs0, Cacf0) %>% mutate(alt.name = "Atlantic cod")
+Cac1 <- rbind(Cacs1, Cacf1) %>% mutate(alt.name = "Atlantic cod")
+Cac2 <- rbind(Cacs2, Cacf2) %>% mutate(alt.name = "Atlantic cod")
+Cap0 <- rbind(Caps0, Capf0) %>% mutate(alt.name = "American plaice")
+Cap1 <- rbind(Caps1, Capf1) %>% mutate(alt.name = "American plaice")
+Cgh0 <- rbind(Cghs0, Cghf0) %>% mutate(alt.name = "Greenland halibut")
+Cgh1 <- rbind(Cghs1, Cghf1) %>% mutate(alt.name = "Greenland halibut")
+Cgh2 <- rbind(Cghs2, Cghf2) %>% mutate(alt.name = "Greenland halibut")
+
+```
+
+## All data
+```{r}
+# Combine seasonal data for
+## Engel
+Eac0 <- rbind(Eacs0, Eacf0) %>% mutate(alt.name = "Atlantic cod")
+Eac1 <- rbind(Eacs1, Eacf1) %>% mutate(alt.name = "Atlantic cod")
+Eac2 <- rbind(Eacs2, Eacf2) %>% mutate(alt.name = "Atlantic cod")
+
+Eap0 <- rbind(Eaps0, Eapf0) %>% mutate(alt.name = "American plaice")
+Eap1 <- rbind(Eaps1, Eapf1) %>% mutate(alt.name = "American plaice")
+
+Egh0 <- rbind(Eghs0, Eghf0) %>% mutate(alt.name = "Greenland halibut")
+Egh1 <- rbind(Eghs1, Eghf1) %>% mutate(alt.name = "Greenland halibut")
+Egh2 <- rbind(Eghs2, Eghf2) %>% mutate(alt.name = "Greenland halibut")
+
+## Campelen
+Cac0 <- rbind(Cacs0, Cacf0) %>% mutate(alt.name = "Atlantic cod")
+Cac1 <- rbind(Cacs1, Cacf1) %>% mutate(alt.name = "Atlantic cod")
+Cac2 <- rbind(Cacs2, Cacf2) %>% mutate(alt.name = "Atlantic cod")
+
+Cap0 <- rbind(Caps0, Capf0) %>% mutate(alt.name = "American plaice")
+Cap1 <- rbind(Caps1, Capf1) %>% mutate(alt.name = "American plaice")
+
+Cgh0 <- rbind(Cghs0, Cghf0) %>% mutate(alt.name = "Greenland halibut")
+Cgh1 <- rbind(Cghs1, Cghf1) %>% mutate(alt.name = "Greenland halibut")
+Cgh2 <- rbind(Cghs2, Cghf2) %>% mutate(alt.name = "Greenland halibut")
+
+# Combine species data from the Engel and Campelen timeseries
+Tac0 <- rbind(Eac0, Cac0)
+Tac1 <- rbind(Eac1, Cac1)
+Tac2 <- rbind(Eac2, Cac2)
+
+Tap0 <- rbind(Eap0, Cap0)
+Tap1 <- rbind(Eap1, Cap1)
+
+Tgh0 <- rbind(Egh0, Cgh0)
+Tgh1 <- rbind(Egh1, Cgh1)
+Tgh2 <- rbind(Egh2, Cgh2)
+
+```
+
+## - Table 1
+```{r}
+
+sample_size <- data.frame(
+  E.C.Spr = c(nrow(filter(Tac0, geartype == "engel" & season == "spring" & content == "called")),
+              nrow(filter(Tac1, geartype == "engel" & season == "spring" & content == "called")),
+              nrow(filter(Tac2, geartype == "engel" & season == "spring" & content == "called")),
+              nrow(filter(Tgh0, geartype == "engel" & season == "spring" & content == "called")),
+              nrow(filter(Tgh1, geartype == "engel" & season == "spring" & content == "called")),
+              nrow(filter(Tgh2, geartype == "engel" & season == "spring" & content == "called")),
+              nrow(filter(Tap0, geartype == "engel" & season == "spring" & content == "called")),
+              nrow(filter(Tap1, geartype == "engel" & season == "spring" & content == "called"))),
+  E.C.Fall = c(nrow(filter(Tac0, geartype == "engel" & season == "fall" & content == "called")),
+               nrow(filter(Tac1, geartype == "engel" & season == "fall" & content == "called")),
+               nrow(filter(Tac2, geartype == "engel" & season == "fall" & content == "called")),
+               nrow(filter(Tgh0, geartype == "engel" & season == "fall" & content == "called")),
+               nrow(filter(Tgh1, geartype == "engel" & season == "fall" & content == "called")),
+               nrow(filter(Tgh2, geartype == "engel" & season == "fall" & content == "called")),
+               nrow(filter(Tap0, geartype == "engel" & season == "fall" & content == "called")),
+               nrow(filter(Tap1, geartype == "engel" & season == "fall" & content == "called"))),
+  E.F.Spr = c(nrow(filter(Tac0, geartype == "engel" & season == "spring" & content == "full")),
+              nrow(filter(Tac1, geartype == "engel" & season == "spring" & content == "full")),
+              nrow(filter(Tac2, geartype == "engel" & season == "spring" & content == "full")),
+              nrow(filter(Tgh0, geartype == "engel" & season == "spring" & content == "full")),
+              nrow(filter(Tgh1, geartype == "engel" & season == "spring" & content == "full")),
+              nrow(filter(Tgh2, geartype == "engel" & season == "spring" & content == "full")),
+              nrow(filter(Tap0, geartype == "engel" & season == "spring" & content == "full")),
+              nrow(filter(Tap1, geartype == "engel" & season == "spring" & content == "full"))),
+  E.F.Fall = c(nrow(filter(Tac0, geartype == "engel" & season == "fall" & content == "full")),
+               nrow(filter(Tac1, geartype == "engel" & season == "fall" & content == "full")),
+               nrow(filter(Tac2, geartype == "engel" & season == "fall" & content == "full")),
+               nrow(filter(Tgh0, geartype == "engel" & season == "fall" & content == "full")),
+               nrow(filter(Tgh1, geartype == "engel" & season == "fall" & content == "full")),
+               nrow(filter(Tgh2, geartype == "engel" & season == "fall" & content == "full")),
+               nrow(filter(Tap0, geartype == "engel" & season == "fall" & content == "full")),
+               nrow(filter(Tap1, geartype == "engel" & season == "fall" & content == "full"))),
+  E.pcapelin =  c(nrow(filter(Tac0, geartype == "engel" & pa == "0"))/nrow(filter(Tac0, geartype == "engel"))*100,
+                  nrow(filter(Tac1, geartype == "engel" & pa == "0"))/nrow(filter(Tac1, geartype == "engel"))*100,
+                  nrow(filter(Tac2, geartype == "engel" & pa == "0"))/nrow(filter(Tac2, geartype == "engel"))*100,
+                  nrow(filter(Tgh0, geartype == "engel" & pa == "0"))/nrow(filter(Tgh0, geartype == "engel"))*100,
+                  nrow(filter(Tgh1, geartype == "engel" & pa == "0"))/nrow(filter(Tgh1, geartype == "engel"))*100,
+                  nrow(filter(Tgh2, geartype == "engel" & pa == "0"))/nrow(filter(Tgh2, geartype == "engel"))*100,
+                  nrow(filter(Tap0, geartype == "engel" & pa == "0"))/nrow(filter(Tap0, geartype == "engel"))*100,
+                  nrow(filter(Tap1, geartype == "engel" & pa == "0"))/nrow(filter(Tap1, geartype == "engel"))*100),
+  E.pempty =  c(nrow(filter(Tac0, geartype == "engel" & empty == TRUE))/nrow(filter(Tac0, geartype == "engel"))*100,
+                nrow(filter(Tac1, geartype == "engel" & empty == TRUE))/nrow(filter(Tac1, geartype == "engel"))*100,
+                nrow(filter(Tac2, geartype == "engel" & empty == TRUE))/nrow(filter(Tac2, geartype == "engel"))*100,
+                nrow(filter(Tgh0, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh0, geartype == "engel"))*100,
+                nrow(filter(Tgh1, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh1, geartype == "engel"))*100,
+                nrow(filter(Tgh2, geartype == "engel" & empty == TRUE))/nrow(filter(Tgh2, geartype == "engel"))*100,
+                nrow(filter(Tap0, geartype == "engel" & empty == TRUE))/nrow(filter(Tap0, geartype == "engel"))*100,
+                nrow(filter(Tap1, geartype == "engel" & empty == TRUE))/nrow(filter(Tap1, geartype == "engel"))*100),
+
+  C.C.Spr = c(nrow(filter(Tac0, geartype == "campelen" & season == "spring" & content == "called")),
+              nrow(filter(Tac1, geartype == "campelen" & season == "spring" & content == "called")),
+              nrow(filter(Tac2, geartype == "campelen" & season == "spring" & content == "called")),
+              nrow(filter(Tgh0, geartype == "campelen" & season == "spring" & content == "called")),
+              nrow(filter(Tgh1, geartype == "campelen" & season == "spring" & content == "called")),
+              nrow(filter(Tgh2, geartype == "campelen" & season == "spring" & content == "called")),
+              nrow(filter(Tap0, geartype == "campelen" & season == "spring" & content == "called")),
+              nrow(filter(Tap1, geartype == "campelen" & season == "spring" & content == "called"))),
+  C.C.Fall = c(nrow(filter(Tac0, geartype == "campelen" & season == "fall" & content == "called")),
+               nrow(filter(Tac1, geartype == "campelen" & season == "fall" & content == "called")),
+               nrow(filter(Tac2, geartype == "campelen" & season == "fall" & content == "called")),
+               nrow(filter(Tgh0, geartype == "campelen" & season == "fall" & content == "called")),
+               nrow(filter(Tgh1, geartype == "campelen" & season == "fall" & content == "called")),
+               nrow(filter(Tgh2, geartype == "campelen" & season == "fall" & content == "called")),
+               nrow(filter(Tap0, geartype == "campelen" & season == "fall" & content == "called")),
+               nrow(filter(Tap1, geartype == "campelen" & season == "fall" & content == "called"))),
+  C.F.Spr = c(nrow(filter(Tac0, geartype == "campelen" & season == "spring" & content == "full")),
+              nrow(filter(Tac1, geartype == "campelen" & season == "spring" & content == "full")),
+              nrow(filter(Tac2, geartype == "campelen" & season == "spring" & content == "full")),
+              nrow(filter(Tgh0, geartype == "campelen" & season == "spring" & content == "full")),
+              nrow(filter(Tgh1, geartype == "campelen" & season == "spring" & content == "full")),
+              nrow(filter(Tgh2, geartype == "campelen" & season == "spring" & content == "full")),
+              nrow(filter(Tap0, geartype == "campelen" & season == "spring" & content == "full")),
+              nrow(filter(Tap1, geartype == "campelen" & season == "spring" & content == "full"))),
+  C.F.Fall = c(nrow(filter(Tac0, geartype == "campelen" & season == "fall" & content == "full")),
+               nrow(filter(Tac1, geartype == "campelen" & season == "fall" & content == "full")),
+               nrow(filter(Tac2, geartype == "campelen" & season == "fall" & content == "full")),
+               nrow(filter(Tgh0, geartype == "campelen" & season == "fall" & content == "full")),
+               nrow(filter(Tgh1, geartype == "campelen" & season == "fall" & content == "full")),
+               nrow(filter(Tgh2, geartype == "campelen" & season == "fall" & content == "full")),
+               nrow(filter(Tap0, geartype == "campelen" & season == "fall" & content == "full")),
+               nrow(filter(Tap1, geartype == "campelen" & season == "fall" & content == "full"))),
+  C.pcapelin =  c(nrow(filter(Tac0, geartype == "campelen" & pa == "0"))/nrow(filter(Tac0, geartype == "campelen"))*100,
+                  nrow(filter(Tac1, geartype == "campelen" & pa == "0"))/nrow(filter(Tac1, geartype == "campelen"))*100,
+                  nrow(filter(Tac2, geartype == "campelen" & pa == "0"))/nrow(filter(Tac2, geartype == "campelen"))*100,
+                  nrow(filter(Tgh0, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh0, geartype == "campelen"))*100,
+                  nrow(filter(Tgh1, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh1, geartype == "campelen"))*100,
+                  nrow(filter(Tgh2, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh2, geartype == "campelen"))*100,
+                  nrow(filter(Tap0, geartype == "campelen" & pa == "0"))/nrow(filter(Tap0, geartype == "campelen"))*100,
+                  nrow(filter(Tap1, geartype == "campelen" & pa == "0"))/nrow(filter(Tap1, geartype == "campelen"))*100),
+  C.pempty = c(nrow(filter(Tac0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac0, geartype == "campelen"))*100,
+                nrow(filter(Tac1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac1, geartype == "campelen"))*100,
+                nrow(filter(Tac2, geartype == "campelen" & empty == TRUE))/nrow(filter(Tac2, geartype == "campelen"))*100,
+                nrow(filter(Tgh0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh0, geartype == "campelen"))*100,
+                nrow(filter(Tgh1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh1, geartype == "campelen"))*100,
+                nrow(filter(Tgh2, geartype == "campelen" & empty == TRUE))/nrow(filter(Tgh2, geartype == "campelen"))*100,
+                nrow(filter(Tap0, geartype == "campelen" & empty == TRUE))/nrow(filter(Tap0, geartype == "campelen"))*100,
+                nrow(filter(Tap1, geartype == "campelen" & empty == TRUE))/nrow(filter(Tap1, geartype == "campelen"))*100)
+
+)
+
+sample_size <- sample_size %>% mutate(E.pcapelin = format(E.pcapelin, digits = 4), C.pcapelin = format(C.pcapelin, digits = 4),
+                                      E.pempty = format(E.pempty, digits = 4), C.pempty = format(C.pempty, digits = 4))
+
+write.csv(x = sample_size, file = "./Figures/samplesize.csv")
+
 ```

### 2025-05-20 SuppSections.Rmd
Updated data by season by year section.

--- 2025-05-08 SuppSections.Rmd
@@
 
-acs1 <- AC_stos %>% filter(length > 17 & length <= 45)
-acs2 <- AC_stos %>% filter(length > 45)
-aps1 <- AP_stos %>% filter(length > 29)
-ghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
-ghs2 <- GH_stos %>% filter(length > 40)
-
-acs0 <- AC_stos %>% filter(length < 18)
-aps0 <- AP_stos %>% filter(length < 30)
-ghs0 <- GH_stos %>% filter(length < 20)
-
-# table(acs0$pa, acs0$year)
-# table(acs1$pa, acs1$year)
-# table(acs2$pa, acs2$year)
-# table(aps0$pa, aps0$year)
-# table(aps1$pa, aps1$year)
-# table(ghs0$pa, ghs0$year)
-# table(ghs1$pa, ghs1$year)
-# table(ghs2$pa, ghs2$year)
-
-Eacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1995)
-Eacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 1995)
-Eaps1 <- AP_stos %>% filter(length > 29)
+Eacs1 <- AC_stos %>% filter(length > 17 & length <= 45)
+Eacs2 <- AC_stos %>% filter(length > 45)
 Eghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
 Eghs2 <- GH_stos %>% filter(length > 40)
-
-Eacs0 <- AC_stos %>% filter(length < 18) %>% filter(year == 1982)
-Eaps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 1984)
-Eghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 1984)
+Eaps1 <- AP_stos %>% filter(length > 29)
+
+Eacs0 <- AC_stos %>% filter(length < 18)
+Eghs0 <- GH_stos %>% filter(length < 20)
+Eaps0 <- AP_stos %>% filter(length < 30)
+
+# table(Eacs0$pa, Eacs0$year)
+# table(Eacs1$pa, Eacs1$year)
+# table(Eacs2$pa, Eacs2$year)
+# table(Eghs0$pa, Eghs0$year)
+# table(Eghs1$pa, Eghs1$year)
+# table(Eghs2$pa, Eghs2$year)
+# table(Eaps0$pa, Eaps0$year)
+# table(Eaps1$pa, Eaps1$year)
 
@@
 
-acf1 <- AC_stof %>% filter(length > 17 & length <= 45)
-acf2 <- AC_stof %>% filter(length > 45)
-apf1 <- AP_stof %>% filter(length > 29)
-ghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
-ghf2 <- GH_stof %>% filter(length > 40)
-
-acf0 <- AC_stof %>% filter(length < 18)
-apf0 <- AP_stof %>% filter(length < 30)
-ghf0 <- GH_stof %>% filter(length < 20)
-
-# table(acf0$pa, acf0$year)
-# table(acf1$pa, acf1$year)
-# table(acf2$pa, acf2$year)
-# table(apf0$pa, apf0$year)
-# table(apf1$pa, apf1$year)
-# table(ghf0$pa, ghf0$year)
-# table(ghf1$pa, ghf1$year)
-# table(ghf2$pa, ghf2$year)
-
 Eacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
-Eacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1994)
-Eapf1 <- AP_stof %>% filter(length > 29)
+Eacf2 <- AC_stof %>% filter(length > 45)
 Eghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
 Eghf2 <- GH_stof %>% filter(length > 40)
-
-Eacf0 <- AC_stof %>% filter(length < 18) %>% filter(year == 1982 & year == 1983 & year == 1988)
+Eapf1 <- AP_stof %>% filter(length > 29)
+
+Eacf0 <- AC_stof %>% filter(length < 18)
+Eghf0 <- GH_stof %>% filter(length < 20)
 Eapf0 <- AP_stof %>% filter(length < 30)
-Eghf0 <- GH_stof %>% filter(length < 20)
+
+# table(Eacf0$pa, Eacf0$year)
+# table(Eacf1$pa, Eacf1$year)
+# table(Eacf2$pa, Eacf2$year)
+# table(Eapf0$pa, Eapf0$year)
+# table(Eapf1$pa, Eapf1$year)
+# table(Eghf0$pa, Eghf0$year)
+# table(Eghf1$pa, Eghf1$year)
+# table(Eghf2$pa, Eghf2$year)
 
@@
 ```{r}
-Eac0 <- rbind(acs0, acf0) %>% mutate(alt.name = "Atlantic cod")
-Eac1 <- rbind(acs1, acf1) %>% mutate(alt.name = "Atlantic cod")
-Eac2 <- rbind(acs2, acf2) %>% mutate(alt.name = "Atlantic cod")
-Eap0 <- rbind(aps0, apf0) %>% mutate(alt.name = "American plaice")
-Eap1 <- rbind(aps1, apf1) %>% mutate(alt.name = "American plaice")
-Egh0 <- rbind(ghs0, ghf0) %>% mutate(alt.name = "Greenland halibut")
-Egh1 <- rbind(ghs1, ghf1) %>% mutate(alt.name = "Greenland halibut")
-Egh2 <- rbind(ghs2, ghf2) %>% mutate(alt.name = "Greenland halibut")
+Eac0 <- rbind(Eacs0, Eacf0) %>% mutate(alt.name = "Atlantic cod")
+Eac1 <- rbind(Eacs1, Eacf1) %>% mutate(alt.name = "Atlantic cod")
+Eac2 <- rbind(Eacs2, Eacf2) %>% mutate(alt.name = "Atlantic cod")
+Eap0 <- rbind(Eaps0, Eapf0) %>% mutate(alt.name = "American plaice")
+Eap1 <- rbind(Eaps1, Eapf1) %>% mutate(alt.name = "American plaice")
+Egh0 <- rbind(Eghs0, Eghf0) %>% mutate(alt.name = "Greenland halibut")
+Egh1 <- rbind(Eghs1, Eghf1) %>% mutate(alt.name = "Greenland halibut")
+Egh2 <- rbind(Eghs2, Eghf2) %>% mutate(alt.name = "Greenland halibut")
 
@@
 
-acs1 <- AC_stos %>% filter(length > 17 & length <= 45)
-acs2 <- AC_stos %>% filter(length > 45)
-aps1 <- AP_stos %>% filter(length > 29)
-ghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
-ghs2 <- GH_stos %>% filter(length > 40)
-
-acs0 <- AC_stos %>% filter(length < 18)
-aps0 <- AP_stos %>% filter(length < 30)
-ghs0 <- GH_stos %>% filter(length < 20)
-
-# table(acs0$pa, acs0$year)
-# table(acs1$pa, acs1$year)
-# table(acs2$pa, acs2$year)
-# table(aps0$pa, aps0$year)
-# table(aps1$pa, aps1$year)
-# table(ghs0$pa, ghs0$year)
-# table(ghs1$pa, ghs1$year)
-# table(ghs2$pa, ghs2$year)
-
-Cacs1 <- AC_stos %>% filter(length > 17 & length <= 45) %>% filter(year != 1998 & year != 2017)
-Cacs2 <- AC_stos %>% filter(length > 45) %>% filter(year != 2015)
-Caps1 <- AP_stos %>% filter(length > 29) %>% filter(year != 2017)
-Cghs1 <- GH_stos %>% filter(length > 19 & length <= 40) %>% filter(year != 2017)
+Cacs1 <- AC_stos %>% filter(length > 17 & length <= 45)
+Cacs2 <- AC_stos %>% filter(length > 45)
+Cghs1 <- GH_stos %>% filter(length > 19 & length <= 40)
 Cghs2 <- GH_stos %>% filter(length > 40)
-
-Cacs0 <- AC_stos %>% filter(length < 18) %>% filter(year != 1996 & year != 1998 & year != 1999 & year != 2006 & year != 2011 & year != 2017)
-Caps0 <- AP_stos %>% filter(length < 30) %>% filter(year != 2017)
-Cghs0 <- GH_stos %>% filter(length < 20) %>% filter(year != 2015 & year != 2017)
+Caps1 <- AP_stos %>% filter(length > 29)
+
+Cacs0 <- AC_stos %>% filter(length < 18)
+Cghs0 <- GH_stos %>% filter(length < 20)
+Caps0 <- AP_stos %>% filter(length < 30)
+
+# table(Cacs0$pa, Cacs0$year)
+# table(Cacs1$pa, Cacs1$year)
+# table(Cacs2$pa, Cacs2$year)
+# table(Cghs0$pa, Cghs0$year)
+# table(Cghs1$pa, Cghs1$year)
+# table(Cghs2$pa, Cghs2$year)
+# table(Caps0$pa, Caps0$year)
+# table(Caps1$pa, Caps1$year)
 
@@
 
-acf1 <- AC_stof %>% filter(length > 17 & length <= 45)
-acf2 <- AC_stof %>% filter(length > 45)
-apf1 <- AP_stof %>% filter(length > 29)
-ghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
-ghf2 <- GH_stof %>% filter(length > 40)
-
-acf0 <- AC_stof %>% filter(length < 18)
-apf0 <- AP_stof %>% filter(length < 30)
-ghf0 <- GH_stof %>% filter(length < 20)
-
-# table(acf0$pa, acf0$year)
-# table(acf1$pa, acf1$year)
-# table(acf2$pa, acf2$year)
-# table(apf0$pa, apf0$year)
-# table(apf1$pa, apf1$year)
-# table(ghf0$pa, ghf0$year)
-# table(ghf1$pa, ghf1$year)
-# table(ghf2$pa, ghf2$year)
-
+# For supplemental
 Cacf1 <- AC_stof %>% filter(length > 17 & length <= 45)
-Cacf2 <- AC_stof %>% filter(length > 45) %>% filter(year != 1995)
-Capf1 <- AP_stof %>% filter(length > 29) %>% filter(year != 2014)
+Cacf2 <- AC_stof %>% filter(length > 45)
 Cghf1 <- GH_stof %>% filter(length > 19 & length <= 40)
 Cghf2 <- GH_stof %>% filter(length > 40)
-
-Cacf0 <- AC_stof %>% filter(length < 18) %>% filter(year != 2011 & year != 2020)
-Capf0 <- AP_stof %>% filter(length < 30) %>% filter(year != 2014)
+Capf1 <- AP_stof %>% filter(length > 29)
+
+Cacf0 <- AC_stof %>% filter(length < 18)
 Cghf0 <- GH_stof %>% filter(length < 20)
+Capf0 <- AP_stof %>% filter(length < 30)
+
+# table(Cacf0$pa, Cacf0$year)
+# table(Cacf1$pa, Cacf1$year)
+# table(Cacf2$pa, Cacf2$year)
+# table(Capf0$pa, Capf0$year)
+# table(Capf1$pa, Capf1$year)
+# table(Cghf0$pa, Cghf0$year)
+# table(Cghf1$pa, Cghf1$year)
+# table(Cghf2$pa, Cghf2$year)
 
@@
 ac <- data.frame(year = seq(1984,2020,1), 
-                 ac0_spring = c(rep(0,11), dfac0$ac0_spring[1:16], 0, dfac0$ac0_spring[17:24], rep(0,1)),
+                 ac0_spring = c(dfac0$ac0_spring[1:9], 0, 0, dfac0$ac0_spring[10:35]), # missing 1993, 1994
                  ac1_spring = c(dfac1$ac1_spring),
-                 ac2_spring = c(dfac2$ac2_spring[1:11], 0, dfac2$ac2_spring[12:36]),
-
-                 ac0_fall = c(rep(0,11), dfac0$ac0_fall[1:16], 0, dfac0$ac0_fall[17:24], rep(0,1)),
+                 ac2_spring = c(dfac2$ac2_spring),
+
+                 ac0_fall = c(dfac0$ac0_fall[1:9], 0, 0, dfac0$ac0_fall[10:35]), # missing 1993, 1994
                  ac1_fall = c(dfac1$ac1_fall),
-                 ac2_fall = c(dfac2$ac2_fall[1:11], 0, dfac2$ac2_fall[12:36]))
+                 ac2_fall = c(dfac2$ac2_fall))
 write.csv(ac, file = "./Extra/acseason.csv")
@@
 write.csv(ap, file = "./Extra/apseason.csv")
-
-```
-
-## - Table 1
-```{r}
-
-sample_size <- data.frame(
-  E.C.Spr = c(nrow(filter(Tac0, geartype == "engel" & season == "spring" & content == "called")),
-              nrow(filter(Tac1, geartype == "engel" & season == "spring" & content == "called")),
-              nrow(filter(Tac2, geartype == "engel" & season == "spring" & content == "called")),
-              nrow(filter(Tgh0, geartype == "engel" & season == "spring" & content == "called")),
-              nrow(filter(Tgh1, geartype == "engel" & season == "spring" & content == "called")),
-              nrow(filter(Tgh2, geartype == "engel" & season == "spring" & content == "called")),
-              nrow(filter(Tap0, geartype == "engel" & season == "spring" & content == "called")),
-              nrow(filter(Tap1, geartype == "engel" & season == "spring" & content == "called"))),
-  E.C.Fall = c(nrow(filter(Tac0, geartype == "engel" & season == "fall" & content == "called")),
-               nrow(filter(Tac1, geartype == "engel" & season == "fall" & content == "called")),
-               nrow(filter(Tac2, geartype == "engel" & season == "fall" & content == "called")),
-               nrow(filter(Tgh0, geartype == "engel" & season == "fall" & content == "called")),
-               nrow(filter(Tgh1, geartype == "engel" & season == "fall" & content == "called")),
-               nrow(filter(Tgh2, geartype == "engel" & season == "fall" & content == "called")),
-               nrow(filter(Tap0, geartype == "engel" & season == "fall" & content == "called")),
-               nrow(filter(Tap1, geartype == "engel" & season == "fall" & content == "called"))),
-  E.F.Spr = c(nrow(filter(Tac0, geartype == "engel" & season == "spring" & content == "full")),
-              nrow(filter(Tac1, geartype == "engel" & season == "spring" & content == "full")),
-              nrow(filter(Tac2, geartype == "engel" & season == "spring" & content == "full")),
-              nrow(filter(Tgh0, geartype == "engel" & season == "spring" & content == "full")),
-              nrow(filter(Tgh1, geartype == "engel" & season == "spring" & content == "full")),
-              nrow(filter(Tgh2, geartype == "engel" & season == "spring" & content == "full")),
-              nrow(filter(Tap0, geartype == "engel" & season == "spring" & content == "full")),
-              nrow(filter(Tap1, geartype == "engel" & season == "spring" & content == "full"))),
-  E.F.Fall = c(nrow(filter(Tac0, geartype == "engel" & season == "fall" & content == "full")),
-               nrow(filter(Tac1, geartype == "engel" & season == "fall" & content == "full")),
-               nrow(filter(Tac2, geartype == "engel" & season == "fall" & content == "full")),
-               nrow(filter(Tgh0, geartype == "engel" & season == "fall" & content == "full")),
-               nrow(filter(Tgh1, geartype == "engel" & season == "fall" & content == "full")),
-               nrow(filter(Tgh2, geartype == "engel" & season == "fall" & content == "full")),
-               nrow(filter(Tap0, geartype == "engel" & season == "fall" & content == "full")),
-               nrow(filter(Tap1, geartype == "engel" & season == "fall" & content == "full"))),
-  E.pempty =  c(nrow(filter(Tac0, geartype == "engel" & pa == "0"))/nrow(filter(Tac0, geartype == "engel"))*100,
-                nrow(filter(Tac1, geartype == "engel" & pa == "0"))/nrow(filter(Tac1, geartype == "engel"))*100,
-                nrow(filter(Tac2, geartype == "engel" & pa == "0"))/nrow(filter(Tac2, geartype == "engel"))*100,
-                nrow(filter(Tgh0, geartype == "engel" & pa == "0"))/nrow(filter(Tgh0, geartype == "engel"))*100,
-                nrow(filter(Tgh1, geartype == "engel" & pa == "0"))/nrow(filter(Tgh1, geartype == "engel"))*100,
-                nrow(filter(Tgh2, geartype == "engel" & pa == "0"))/nrow(filter(Tgh2, geartype == "engel"))*100,
-                nrow(filter(Tap0, geartype == "engel" & pa == "0"))/nrow(filter(Tap0, geartype == "engel"))*100,
-                nrow(filter(Tap1, geartype == "engel" & pa == "0"))/nrow(filter(Tap1, geartype == "engel"))*100),
-
-  C.C.Spr = c(nrow(filter(Tac0, geartype == "campelen" & season == "spring" & content == "called")),
-              nrow(filter(Tac1, geartype == "campelen" & season == "spring" & content == "called")),
-              nrow(filter(Tac2, geartype == "campelen" & season == "spring" & content == "called")),
-              nrow(filter(Tgh0, geartype == "campelen" & season == "spring" & content == "called")),
-              nrow(filter(Tgh1, geartype == "campelen" & season == "spring" & content == "called")),
-              nrow(filter(Tgh2, geartype == "campelen" & season == "spring" & content == "called")),
-              nrow(filter(Tap0, geartype == "campelen" & season == "spring" & content == "called")),
-              nrow(filter(Tap1, geartype == "campelen" & season == "spring" & content == "called"))),
-  C.C.Fall = c(nrow(filter(Tac0, geartype == "campelen" & season == "fall" & content == "called")),
-               nrow(filter(Tac1, geartype == "campelen" & season == "fall" & content == "called")),
-               nrow(filter(Tac2, geartype == "campelen" & season == "fall" & content == "called")),
-               nrow(filter(Tgh0, geartype == "campelen" & season == "fall" & content == "called")),
-               nrow(filter(Tgh1, geartype == "campelen" & season == "fall" & content == "called")),
-               nrow(filter(Tgh2, geartype == "campelen" & season == "fall" & content == "called")),
-               nrow(filter(Tap0, geartype == "campelen" & season == "fall" & content == "called")),
-               nrow(filter(Tap1, geartype == "campelen" & season == "fall" & content == "called"))),
-  C.F.Spr = c(nrow(filter(Tac0, geartype == "campelen" & season == "spring" & content == "full")),
-              nrow(filter(Tac1, geartype == "campelen" & season == "spring" & content == "full")),
-              nrow(filter(Tac2, geartype == "campelen" & season == "spring" & content == "full")),
-              nrow(filter(Tgh0, geartype == "campelen" & season == "spring" & content == "full")),
-              nrow(filter(Tgh1, geartype == "campelen" & season == "spring" & content == "full")),
-              nrow(filter(Tgh2, geartype == "campelen" & season == "spring" & content == "full")),
-              nrow(filter(Tap0, geartype == "campelen" & season == "spring" & content == "full")),
-              nrow(filter(Tap1, geartype == "campelen" & season == "spring" & content == "full"))),
-  C.F.Fall = c(nrow(filter(Tac0, geartype == "campelen" & season == "fall" & content == "full")),
-               nrow(filter(Tac1, geartype == "campelen" & season == "fall" & content == "full")),
-               nrow(filter(Tac2, geartype == "campelen" & season == "fall" & content == "full")),
-               nrow(filter(Tgh0, geartype == "campelen" & season == "fall" & content == "full")),
-               nrow(filter(Tgh1, geartype == "campelen" & season == "fall" & content == "full")),
-               nrow(filter(Tgh2, geartype == "campelen" & season == "fall" & content == "full")),
-               nrow(filter(Tap0, geartype == "campelen" & season == "fall" & content == "full")),
-               nrow(filter(Tap1, geartype == "campelen" & season == "fall" & content == "full"))),
-  C.pempty =  c(nrow(filter(Tac0, geartype == "campelen" & pa == "0"))/nrow(filter(Tac0, geartype == "campelen"))*100,
-                nrow(filter(Tac1, geartype == "campelen" & pa == "0"))/nrow(filter(Tac1, geartype == "campelen"))*100,
-                nrow(filter(Tac2, geartype == "campelen" & pa == "0"))/nrow(filter(Tac2, geartype == "campelen"))*100,
-                nrow(filter(Tgh0, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh0, geartype == "campelen"))*100,
-                nrow(filter(Tgh1, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh1, geartype == "campelen"))*100,
-                nrow(filter(Tgh2, geartype == "campelen" & pa == "0"))/nrow(filter(Tgh2, geartype == "campelen"))*100,
-                nrow(filter(Tap0, geartype == "campelen" & pa == "0"))/nrow(filter(Tap0, geartype == "campelen"))*100,
-                nrow(filter(Tap1, geartype == "campelen" & pa == "0"))/nrow(filter(Tap1, geartype == "campelen"))*100)
-
-)
-
-sample_size <- sample_size %>% mutate(E.pempty = format(E.pempty, digits = 4), C.pempty = format(C.pempty, digits = 4))
-
-write.csv(x = sample_size, file = "./Extra/samplesize.csv")
 
@@
 
-  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), size = 1.4) +
-  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), size = 1.4) +
-
-  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), size = 1.4) +
-  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), size = 1.4) +
-
-  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), size = 1.4) +
-
-  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
+  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), linewidth = 1.4) +
+  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), linewidth = 1.4) +
+
+  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), linewidth = 1.4) +
+  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), linewidth = 1.4) +
+
+  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), linewidth = 1.4) +
+
+  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.4), breaks = c(seq(1983,1995, 2))) + 
   scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.0,1.7)) +
@@
 
-  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), size = 1.4) +
-  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), size = 1.4) +
-
-  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), size = 1.4) +
-  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), size = 1.4) +
-
-  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), size = 1.4) +
-
-  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.2), breaks = c(seq(1983,1995, 2))) + 
+  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), linewidth = 1.4) +
+  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), linewidth = 1.4) +
+
+  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), linewidth = 1.4) +
+  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), linewidth = 1.4) +
+
+  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), linewidth = 1.4) +
+
+  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1983.9,1995.4), breaks = c(seq(1983,1995, 2))) + 
   scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0)) +
@@
 sc <- ggplot(data = plotdf) +  
-  geom_line(aes(x = time, y = ts, colour = "trawl"), size = 1.4, linetype = "dashed") +
-
-  geom_line( aes(x = time, y = ac1, colour = "ac"), size = 1.4, linetype = "solid") +
-
-  geom_line(aes(x = time, y = gh1, colour = "gh"), size = 1.4, linetype = "solid") +
-
-  geom_line(aes(x = time, y = ap1, colour = "ap"), size = 1.4, linetype = "solid") +
+  geom_line(aes(x = time, y = ts, colour = "trawl"), linetype = "dashed", linewidth = 1.4) +
+
+  geom_line(aes(x = time, y = ac1, colour = "ac"), linetype = "solid", linewidth = 1.4) +
+
+  geom_line(aes(x = time, y = gh1, colour = "gh"), linetype = "solid", linewidth = 1.4) +
+
+  geom_line(aes(x = time, y = ap1, colour = "ap"), linetype = "solid", linewidth = 1.4) +
 
@@
 
-  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), size = 1.4) +
-  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), size = 1.4) +
-
-  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), size = 1.4) +
-  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), size = 1.4) +
-
-  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), size = 1.4) +
+  geom_line( aes(x = time, y = ac1, colour = "ac", linetype = "medium"), linewidth = 1.4) +
+  geom_line(aes(x = time, y = ac2, colour = "ac", linetype = "large"), linewidth = 1.4) +
+
+  geom_line(aes(x = time, y = gh1, colour = "gh", linetype = "medium"), linewidth = 1.4) +
+  geom_line(aes(x = time, y = gh2, colour = "gh", linetype = "large"), linewidth = 1.4) +
+
+  geom_line(aes(x = time, y = ap1, colour = "ap", linetype = "medium"), linewidth = 1.4) +
 
@@
   theme_classic() + 
-  theme(legend.position = "none", 
-        axis.title.y = element_blank(),
+  theme(axis.title.y = element_blank(), legend.text = element_text(size = 16), 
         axis.text =  element_text(size = 15), axis.title = element_text(size = 16, face = "bold"), 
@@
 ## - Figure 2
-```{r, fig.height=10, fig.width=12}
-
-p1 <- ggarrange(se,
+```{r, fig.height=10, fig.width=14}
+
+p2 <- ggarrange(se,
           sc,
@@
           align = "v", common.legend = TRUE,
-          legend = "right", legend.grob = ggpubr::get_legend(fc+theme(legend.position = "right", lengend.text = element_text(size = 15))))
-
-ggsave(filename = "inputdata1.tiff", device = "tiff", plot = p1, path = "./Figures",
+          legend = "right", legend.grob = ggpubr::get_legend(fc))
+
+ggsave(filename = "inputdata2.tiff", device = "tiff", plot = p2, path = "./Figures",
        dpi = 300, width = 14, height = 10, units = "in")
